### 2020-11-02 slides.Rmd
slides proposal and such

---
title: "Measuring Political Freedom Around the World"
author: " Joe Despres, Joe Sigler, Jacob Haywood, Sabrina Ball"
institute: "MSU"
date: "Updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r}
data <- read_csv(here::here("sttproj", "merged", "df.csv"))
```

```{r}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan

### /ʃaː.'riŋ.ɡan/

---
class: inverse, center, middle

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](https://slides.yihui.org/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---
background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
class: center, bottom, inverse

# You only live once!

---

# Hello Ninja

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

# remark.js

You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to

- create a new slide (Markdown syntax<sup>*</sup> and slide properties);

- format a slide (e.g. text alignment);

- configure the slideshow;

- and use the presentation (keyboard shortcuts).

It is important to be familiar with remark.js before you can understand the options in **xaringan**.

.footnote[[*] It is different with Pandoc's Markdown! It is limited but should be enough for presentation purposes. Come on... You do not need a slide for the Table of Contents! Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]

---
background-image: url(`r xaringan:::karl`)
background-size: cover
class: center, bottom, inverse

# I was so happy to have discovered remark.js!

---
class: inverse, middle, center

# Using xaringan

---

# xaringan

Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```

See the help page `?xaringan::moon_reader` for all possible options that you can use.

---

# remark.js vs xaringan

Some differences between using remark.js (left) and using **xaringan** (right):

.pull-left[
1. Start with a boilerplate HTML file;

1. Plain Markdown;

1. Write JavaScript to autoplay slides;

1. Manually configure MathJax;

1. Highlight code with `*`;

1. Edit Markdown source and refresh browser to see updated slides;
]

.pull-right[
1. Start with an R Markdown document;

1. R Markdown (can embed R/other code chunks);

1. Provide an option `autoplay`;

1. MathJax just works;<sup>*</sup>

1. Highlight code with `{{}}`;

1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
]

.footnote[[*] Not really. See next page.]

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# R Code

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

---

# R Plots

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---

# HTML Widgets

I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.

Similarly, the Shiny mode (`runtime: shiny`) does not work. I might get these issues fixed in the future, but these are not of high priority to me. I never turn my presentation into a Shiny app. When I need to demonstrate more complicated examples, I just launch them separately. It is convenient to share slides with other people when they are plain HTML/JS applications.

See the next page for two HTML widgets.

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
```

---

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

---

# Some Tips

- Do not forget to try the `yolo` option of `xaringan::moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        yolo: true
    ```

---

# Some Tips

- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds in a lightning talk:

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          autoplay: 30000
    ```

- If you want to restart the play after it reaches the last slide, you may set the sub-option `loop` to TRUE, e.g.,

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          autoplay:
            interval: 30000
            loop: true
    ```

---

# Some Tips

- A countdown timer can be added to every page of the slides using the `countdown` option under `nature`, e.g. if you want to spend one minute on every page when you give the talk, you can set:

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          countdown: 60000
    ```

    Then you will see a timer counting down from `01:00`, to `00:59`, `00:58`, ... When the time is out, the timer will continue but the time turns red.

---

# Some Tips

- The title slide is created automatically by **xaringan**, but it is just another remark.js slide added before your other slides.

    The title slide is set to `class: center, middle, inverse, title-slide` by default. You can change the classes applied to the title slide with the `titleSlideClass` option of `nature` (`title-slide` is always applied).

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          titleSlideClass: [top, left, inverse]
    ```

--

- If you'd like to create your own title slide, disable **xaringan**'s title slide with the `seal = FALSE` option of `moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        seal: false
    ```

---

# Some Tips

- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.org/xaringan/incremental.html) for examples.

- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          highlightLines: true
    ```

    See examples on the next page.

---

# Some Tips

.pull-left[
An example using a leading `*`:

    ```r
    if (TRUE) {
    ** message("Very important!")
    }
    ```
Output:
```r
if (TRUE) {
* message("Very important!")
}
```

This is invalid R code, so it is a plain fenced code block that is not executed.
]

.pull-right[
An example using `{{}}`:

````
`r ''````{r tidy=FALSE}
if (TRUE) {
*{{ message("Very important!") }}
}
```
````
Output:
```{r tidy=FALSE}
if (TRUE) {
{{ message("Very important!") }}
}
```

It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
]

---

# Some Tips

An example of using the trailing comment `#<<` to highlight lines:

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````

Output:

```{r tidy=FALSE, eval=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---

# Some Tips

When you enable line-highlighting, you can also use the chunk option `highlight.output` to highlight specific lines of the text output from a code chunk. For example, `highlight.output = TRUE` means highlighting all lines, and `highlight.output = c(1, 3)` means highlighting the first and third line.

````md
`r ''````{r, highlight.output=c(1, 3)}
head(iris)
```
````

```{r, highlight.output=c(1, 3), echo=FALSE}
head(iris)
```

Question: what does `highlight.output = c(TRUE, FALSE)` mean? (Hint: think about R's recycling of vectors)

---

# Some Tips

- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).

- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.

- Then change the `chakra` option in YAML to point to this file, e.g.

    ```yaml
    output:
      xaringan::moon_reader:
        chakra: libs/remark-latest.min.js
    ```

- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally. The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.

---

# Macros

- remark.js [allows users to define custom macros](https://github.com/yihui/xaringan/issues/80) (JS functions) that can be applied to Markdown text using the syntax `![:macroName arg1, arg2, ...]` or `![:macroName arg1, arg2, ...](this)`. For example, before remark.js initializes the slides, you can define a macro named `scale`:

    ```js
    remark.macros.scale = function (percentage) {
      var url = this;
      return '<img src="' + url + '" style="width: ' + percentage + '" />';
    };
    ```

    Then the Markdown text

    ```markdown
    ![:scale 50%](image.jpg)
    ```

    will be translated to

    ```html
    <img src="image.jpg" style="width: 50%" />
    ```

---

# Macros (continued)

- To insert macros in **xaringan** slides, you can use the option `beforeInit` under the option `nature`, e.g.,

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          beforeInit: "macros.js"
    ```

    You save your remark.js macros in the file `macros.js`.

- The `beforeInit` option can be used to insert arbitrary JS code before `remark.create()`. Inserting macros is just one of its possible applications.

---

# CSS

Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.

You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css). You can completely replace it with your own CSS files, or define new rules to override the default. See the help page `?xaringan::moon_reader` for more information.

---

# CSS

For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:

```css
@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);

.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
```

Then set the `css` option in the YAML metadata:

```yaml
output:
  xaringan::moon_reader:
    css: ["default", "ubuntu-mono.css"]
```

Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.

See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.

---

# Themes

Don't want to learn CSS? Okay, you can use some user-contributed themes. A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name. Below are some existing themes:

```{r, R.options=list(width = 70)}
names(xaringan:::list_css())
```

---

# Themes

To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,

```yaml
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
```

If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.org/en/2017/10/xaringan-themes).

---
class: inverse, middle, center
background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
background-size: contain

# Naruto

---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

# Sharingan

The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:

- the "Eye of Insight"

- the "Eye of Hypnotism"

I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>

.footnote[
[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.

[2] By comparison, bad presentations only put the audience to sleep.

[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
]

---

# Naruto terminology

The **xaringan** package borrowed a few terms from Naruto, such as

- [Sharingan](https://naruto.fandom.com/wiki/Sharingan) (写輪眼; the package name)

- The [moon reader](https://naruto.fandom.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)

- [Chakra](https://naruto.fandom.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)

- [Nature transformation](https://naruto.fandom.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)

- The [infinite moon reader](https://naruto.fandom.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)

- The [summoning technique](https://naruto.fandom.com/wiki/Summoning_Technique) (download remark.js from the web)

You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.

---

class: center

# Hand seals (印)

Press `h` or `?` to see the possible ninjutsu you can use in remark.js.

![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)

---

class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

### 2020-11-03 R/best_subset_selection.R
organized files

@@ -1,0 +1,29 @@
+
+# best_subset_selection ---------------------------------------------------
+
+
+names(data)
+vars <- data %>% 
+  select(-country, -year, -ends_with("_fh")) %>%
+  names()
+
+outcome <- "polrights_fh"
+
+models <- list()
+for (i in 1:length(vars)) {
+  vc <- combn(vars,i)
+  for (j in 1:ncol(vc)) {
+    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
+    models <- c(models, model)
+  }
+}
+
+subsets <- map(models, function(x) lm(x, data)) %>% 
+  map(broom::glance) %>% 
+  setNames(models) %>% 
+  bind_rows(.id = "id") %>% 
+  distinct() %>% 
+  rename(model = id) 
+
+subsets %>% View()
+

### 2020-11-03 R/cleaningscript.R

@@ -1,0 +1,28 @@
+library(tidyverse)
+#hey we are editing
+# Read and Clean ----------------------------------------------------------
+files <- list.files(path = here::here("sttproj", "data"), pattern = ".csv")
+
+files
+
+cleaning <- function(df){
+  df <- pivot_longer(df, cols = -country, names_to = "year")
+}
+
+files %>% 
+  map(function(x) read_csv(paste0("sttproj/data/", x))) %>% 
+  setNames(gsub("\\.csv$", "", files)) %>% 
+  map(cleaning) %>% 
+  bind_rows(.id = "id") %>% 
+  pivot_wider(names_from = id) # %>% 
+write_csv(here::here("sttproj", "merged", "df.csv"))
+
+# Filtering ---------------------------------------------------------------
+
+data <- read_csv(here::here("sttproj", "merged", "df.csv"))
+vars <- paste0(colnames(data), sep = ", ", collapse = "" )
+data %>% select(-ends_with("_fh")) %>% names() %>% paste0(., sep = ", ", collapse = "" )
+
+
+
+

### 2020-11-03 R/visualization.R

@@ -1,0 +1,47 @@
+
+# Visuals -------------------------------------------------------------
+
+data %>% 
+  select(-year) %>% 
+  select_if(is.numeric) %>% 
+  cor(.,  use = "complete.obs") %>% 
+  View()
+
+data %>% 
+  filter(year > 2015) %>% 
+  ggplot(mapping = aes(x = freedix_fh)) + 
+  geom_histogram()
+
+data %>% 
+  filter(year > 2015) %>% 
+  ggplot(mapping = aes(x = polrights_fh)) + 
+  geom_histogram()
+
+data %>% 
+  filter(year > 2015) %>% 
+  ggplot(mapping = aes(x = cliberities_fh)) + 
+  geom_histogram()
+
+data %>% 
+  filter(year > 2015) %>% 
+  mutate(trans_civlib = exp(cliberities_fh)) %>% 
+  ggplot(mapping = aes(x = trans_civlib)) + 
+  geom_histogram()
+
+data %>% 
+  filter(year > 2015) %>% 
+  #  mutate(trans_civlib = gini) %>% 
+  ggplot(mapping = aes(x = gini)) + 
+  geom_histogram()
+
+data %>% 
+  select(country, gini) %>% 
+  group_by(country) %>%
+  summarise(mean = mean(gini, na.rm = TRUE)) %>% 
+  View()
+
+data %>% 
+  select(country, journakilled) %>% 
+  group_by(country) %>%
+  summarise(mean = mean(journakilled, na.rm = TRUE)) %>% 
+  View()

### 2020-11-03 cleaningscript.R

@@ -1,100 +1,0 @@
-library(tidyverse)
-#hey we are editing
-# Read and Clean ----------------------------------------------------------
-files <- list.files(path = here::here("sttproj", "data"), pattern = ".csv")
-
-files
-
-cleaning <- function(df){
-  df <- pivot_longer(df, cols = -country, names_to = "year")
-}
-
-files %>% 
-  map(function(x) read_csv(paste0("sttproj/data/", x))) %>% 
-  setNames(gsub("\\.csv$", "", files)) %>% 
-  map(cleaning) %>% 
-  bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id) # %>% 
-write_csv(here::here("sttproj", "merged", "df.csv"))
-
-# Filtering ---------------------------------------------------------------
-
-data <- read_csv(here::here("sttproj", "merged", "df.csv"))
-vars <- paste0(colnames(data), sep = ", ", collapse = "" )
-data %>% select(-ends_with("_fh")) %>% names() %>% paste0(., sep = ", ", collapse = "" )
-
-# Exploration -------------------------------------------------------------
-
-data %>% 
-  select(-year) %>% 
-  select_if(is.numeric) %>% 
-  cor(.,  use = "complete.obs") %>% 
-  View()
-
-data %>% 
-  filter(year > 2015) %>% 
-  ggplot(mapping = aes(x = freedix_fh)) + 
-  geom_histogram()
-
-data %>% 
-  filter(year > 2015) %>% 
-  ggplot(mapping = aes(x = polrights_fh)) + 
-  geom_histogram()
-
-data %>% 
-  filter(year > 2015) %>% 
-  ggplot(mapping = aes(x = cliberities_fh)) + 
-  geom_histogram()
-
-data %>% 
-  filter(year > 2015) %>% 
-  mutate(trans_civlib = exp(cliberities_fh)) %>% 
-  ggplot(mapping = aes(x = trans_civlib)) + 
-  geom_histogram()
-
-data %>% 
-  filter(year > 2015) %>% 
-#  mutate(trans_civlib = gini) %>% 
-  ggplot(mapping = aes(x = gini)) + 
-  geom_histogram()
-
-data %>% 
-  select(country, gini) %>% 
-  group_by(country) %>%
-  summarise(mean = mean(gini, na.rm = TRUE)) %>% 
-  View()
-
-data %>% 
-  select(country, journakilled) %>% 
-  group_by(country) %>%
[…]

### 2020-11-03 R/best_subset_selection.R
adjusted paths

@@ -1,6 +1,8 @@
+library(tidyverse)
 
 # best_subset_selection ---------------------------------------------------
 
+data <- read_csv(here::here("data", "df.csv"))
 
 names(data)
 vars <- data %>% 
@@ -24,6 +26,7 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   bind_rows(.id = "id") %>% 
   distinct() %>% 
   rename(model = id) 
+
 
 subsets %>% View()
 

### 2020-11-03 R/cleaningscript.R

@@ -1,8 +1,7 @@
 library(tidyverse)
-#hey we are editing
-# Read and Clean ----------------------------------------------------------
-files <- list.files(path = here::here("sttproj", "data"), pattern = ".csv")
 
+# Read and Clean ----------------------------------------------------------
+files <- list.files(path = here::here("data"), pattern = ".csv")
 files
 
 cleaning <- function(df){
@@ -10,19 +9,16 @@ cleaning <- function(df){
 }
 
 files %>% 
-  map(function(x) read_csv(paste0("sttproj/data/", x))) %>% 
+  map(function(x) read_csv(paste0("data/", x))) %>% 
   setNames(gsub("\\.csv$", "", files)) %>% 
   map(cleaning) %>% 
   bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id) # %>% 
-write_csv(here::here("sttproj", "merged", "df.csv"))
+  pivot_wider(names_from = id)# %>% 
+write_csv(here::here("merged", "df.csv"))
 
 # Filtering ---------------------------------------------------------------
-
-data <- read_csv(here::here("sttproj", "merged", "df.csv"))
-vars <- paste0(colnames(data), sep = ", ", collapse = "" )
-data %>% select(-ends_with("_fh")) %>% names() %>% paste0(., sep = ", ", collapse = "" )
-
+data <- read_csv(here::here("merged", "df.csv"))
+data %>% View()
 
 
 

### 2020-11-03 R/visualization.R

@@ -1,5 +1,8 @@
+library(tidyverse)
 
 # Visuals -------------------------------------------------------------
+
+data <- read_csv(here::here("data", "df.csv"))
 
 data %>% 
   select(-year) %>% 

### 2020-11-03 R/cleaningscript.R
adjusted paths

@@ -1,7 +1,7 @@
 library(tidyverse)
 
 # Read and Clean ----------------------------------------------------------
-files <- list.files(path = here::here("data"), pattern = ".csv")
+files <- list.files(path = here::here("raw_data"), pattern = ".csv")
 files
 
 cleaning <- function(df){
@@ -9,7 +9,7 @@ cleaning <- function(df){
 }
 
 files %>% 
-  map(function(x) read_csv(paste0("data/", x))) %>% 
+  map(function(x) read_csv(paste0("raw_data/", x))) %>% 
   setNames(gsub("\\.csv$", "", files)) %>% 
   map(cleaning) %>% 
   bind_rows(.id = "id") %>% 
@@ -17,7 +17,7 @@ files %>%
 write_csv(here::here("merged", "df.csv"))
 
 # Filtering ---------------------------------------------------------------
-data <- read_csv(here::here("merged", "df.csv"))
+data <- read_csv(here::here("data", "df.csv"))
 data %>% View()
 
 

### 2020-11-03 paper.tex
.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{The title}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 4.0.2; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
\end{cslreferences}

\endgroup

\end{document}

### 2020-11-03 slides.Rmd
added rmd template for slideshow

@@
 title: "Measuring Political Freedom Around the World"
-author: " Joe Despres, Joe Sigler, Jacob Haywood, Sabrina Ball"
+subtitle: " Joe Despres, Joe Sigler, Jacob Haywood"
 institute: "MSU"
-date: "Updated: `r Sys.Date()`"
+date: "updated: `r Sys.Date()`"
 output:
@@
 ---
+
 background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
@@
 
-```{r}
-data <- read_csv(here::here("sttproj", "merged", "df.csv"))
-```
-
-```{r}
-DT::datatable(
-  head(iris, 10),
-  fillContainer = FALSE, options = list(pageLength = 8)
-)
-```
+???
 

### 2020-11-03 R/best_subset_selection.R
added best subsets

@@ -27,6 +27,6 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   distinct() %>% 
   rename(model = id) 
 
-
+write_csv(subsets, here::here("data", "bestsebsets.csv"))
 subsets %>% View()
 

### 2020-11-03 R/best_subset_selection.R
.

@@ -27,6 +27,6 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   distinct() %>% 
   rename(model = id) 
 
-write_csv(subsets, here::here("data", "bestsebsets.csv"))
 subsets %>% View()
 
+write_csv(subsets, here::here("data", "bestsebsets.csv"))

### 2020-11-04 R/cleaningscript.R
removed data from years < 2010

@@ -13,12 +13,14 @@ files %>%
   setNames(gsub("\\.csv$", "", files)) %>% 
   map(cleaning) %>% 
   bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id)# %>% 
-write_csv(here::here("merged", "df.csv"))
+  pivot_wider(names_from = id) # %>% 
+write_csv(here::here("data", "df.csv"))
 
 # Filtering ---------------------------------------------------------------
-data <- read_csv(here::here("data", "df.csv"))
+data <- read_csv(here::here("data", "df.csv")) %>% 
+  filter(year > 2009) 
+
 data %>% View()
 
-
+dim(data)
 

### 2020-11-04 R/best_subset_selection.R
fixed spelling

@@ -29,4 +29,4 @@ subsets <- map(models, function(x) lm(x, data)) %>%
 
 subsets %>% View()
 
-write_csv(subsets, here::here("data", "bestsebsets.csv"))
+write_csv(subsets, here::here("data", "best_subsets.csv"))

### 2020-11-04 R/visualization.R
ran some plots

@@ -1,19 +1,20 @@
 library(tidyverse)
-
 # Visuals -------------------------------------------------------------
+theme_set(theme_light())
 
 data <- read_csv(here::here("data", "df.csv"))
+best_subsets <- read_csv(here::here("data", "best_subsets.csv"))
 
-data %>% 
+corr_matrix <- data %>% 
   select(-year) %>% 
   select_if(is.numeric) %>% 
-  cor(.,  use = "complete.obs") %>% 
-  View()
+  cor(.,  use = "complete.obs")
+
 
 data %>% 
   filter(year > 2015) %>% 
   ggplot(mapping = aes(x = freedix_fh)) + 
-  geom_histogram()
+  geom_histogram(bins = 10)
 
 data %>% 
   filter(year > 2015) %>% 
@@ -33,18 +34,52 @@ data %>%
 
 data %>% 
   filter(year > 2015) %>% 
-  #  mutate(trans_civlib = gini) %>% 
   ggplot(mapping = aes(x = gini)) + 
   geom_histogram()
 
 data %>% 
-  select(country, gini) %>% 
-  group_by(country) %>%
-  summarise(mean = mean(gini, na.rm = TRUE)) %>% 
-  View()
+  ggplot(aes(x = gini, y = polrights_fh)) +
+  geom_hex(binwidth = c(3, .6)) + 
+  scale_fill_gradient(low = "#7FFFD4", high = "#8B8378") + 
+  geom_smooth(method = "lm", se = TRUE, color = "red") +
+  geom_point(data = data %>% 
+               filter(country == "United States", 
+                         year == 2018), 
+      aes(x = gini, y = polrights_fh), size = 5, color = "red") +
+  labs(x = "GINI Coeffeceint", y = "Political Rights")
+
 
 data %>% 
-  select(country, journakilled) %>% 
-  group_by(country) %>%
-  summarise(mean = mean(journakilled, na.rm = TRUE)) %>% 
-  View()
+  ggplot(aes(x = gini, y = polrights_fh)) + 
+  geom_smooth(se = false)
+
+r <- best_subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+
+best_subsets %>% 
+  ggplot(aes(x = df, y = adj.r.squared)) + 
+  geom_point() + 
[…]

### 2020-11-04 slides.Rmd
added table to slide

@@
 title: "Measuring Political Freedom Around the World"
-subtitle: " Joe Despres, Joe Sigler, Jacob Haywood"
-institute: "MSU"
-date: "updated: `r Sys.Date()`"
+subtitle: "Sabrina Ball, Joe Despres, Joe Sigler, Jacob Haywood"
+date: "Last compiled `r format(Sys.time(), '%H:%M')`"
 output:
@@
 ```{r setup, include=FALSE}
-options(htmltools.dir.version = FALSE)
+options(htmltools.dir.version = FALSE, echo = FALSE)
+library(gtsummary)
+source(here::here("R", "visualization.R"))
+options(digits = 3)
 ```
+
+---
+```{r echo=FALSE}
+best_subsets %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  select(model, adj.r.squared) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 6))
+```
+---
+
+---
+
+---
 

### 2020-11-04 R/visualization.R
fixed error

@@ -51,7 +51,7 @@ data %>%
 
 data %>% 
   ggplot(aes(x = gini, y = polrights_fh)) + 
-  geom_smooth(se = false)
+  geom_smooth(se = FALSE)
 
 r <- best_subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
 

### 2020-11-04 R/best_subset_selection.R
added model

@@ -5,11 +5,16 @@ library(tidyverse)
 data <- read_csv(here::here("data", "df.csv"))
 
 names(data)
+
 vars <- data %>% 
   select(-country, -year, -ends_with("_fh")) %>%
   names()
 
+# make it continuous
+data$garbage <- data$polrights_fh + rnorm(length(data$polrights_fh),3.68,1.94)
+
 outcome <- "polrights_fh"
+outcome <- "garbage"
 
 models <- list()
 for (i in 1:length(vars)) {
@@ -29,4 +34,4 @@ subsets <- map(models, function(x) lm(x, data)) %>%
 
 subsets %>% View()
 
-write_csv(subsets, here::here("data", "best_subsets.csv"))
+# write_csv(subsets, here::here("data", "best_subsets.csv"))

### 2020-11-04 R/cleaningscript.R

@@ -8,19 +8,18 @@ cleaning <- function(df){
   df <- pivot_longer(df, cols = -country, names_to = "year")
 }
 
-files %>% 
+data <- files %>% 
   map(function(x) read_csv(paste0("raw_data/", x))) %>% 
   setNames(gsub("\\.csv$", "", files)) %>% 
   map(cleaning) %>% 
   bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id) # %>% 
-write_csv(here::here("data", "df.csv"))
+  pivot_wider(names_from = id) 
+
+
 
 # Filtering ---------------------------------------------------------------
-data <- read_csv(here::here("data", "df.csv")) %>% 
-  filter(year > 2009) 
+data %>% filter(year > 2000) %>% 
+write_csv(here::here("data", "df.csv"))
 
-data %>% View()
-
-dim(data)
+data <- read_csv(here::here("data", "df.csv")) 
 

### 2020-11-04 R/visualization.R

@@ -3,7 +3,7 @@ library(tidyverse)
 theme_set(theme_light())
 
 data <- read_csv(here::here("data", "df.csv"))
-best_subsets <- read_csv(here::here("data", "best_subsets.csv"))
+subsets <- read_csv(here::here("data", "subsets.csv"))
 
 corr_matrix <- data %>% 
   select(-year) %>% 
@@ -11,23 +11,20 @@ corr_matrix <- data %>%
   cor(.,  use = "complete.obs")
 
 
+
 data %>% 
-  filter(year > 2015) %>% 
   ggplot(mapping = aes(x = freedix_fh)) + 
   geom_histogram(bins = 10)
 
 data %>% 
-  filter(year > 2015) %>% 
   ggplot(mapping = aes(x = polrights_fh)) + 
   geom_histogram()
 
 data %>% 
-  filter(year > 2015) %>% 
   ggplot(mapping = aes(x = cliberities_fh)) + 
   geom_histogram()
 
 data %>% 
-  filter(year > 2015) %>% 
   mutate(trans_civlib = exp(cliberities_fh)) %>% 
   ggplot(mapping = aes(x = trans_civlib)) + 
   geom_histogram()
@@ -48,38 +45,52 @@ data %>%
       aes(x = gini, y = polrights_fh), size = 5, color = "red") +
   labs(x = "GINI Coeffeceint", y = "Political Rights")
 
-
 data %>% 
   ggplot(aes(x = gini, y = polrights_fh)) + 
   geom_smooth(se = FALSE)
 
-r <- best_subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
 
-best_subsets %>% 
+subsets %>% 
   ggplot(aes(x = df, y = adj.r.squared)) + 
   geom_point() + 
   geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
   labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
 
-AIC <- best_subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+AIC <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
 
-best_subsets %>% 
+subsets %>% 
   ggplot(aes(x = df, y = AIC)) + 
[…]

### 2020-11-04 R/best_subset_selection.R
.catchup

@@ -5,16 +5,11 @@ library(tidyverse)
 data <- read_csv(here::here("data", "df.csv"))
 
 names(data)
-
 vars <- data %>% 
   select(-country, -year, -ends_with("_fh")) %>%
   names()
 
-# make it continuous
-data$garbage <- data$polrights_fh + rnorm(length(data$polrights_fh),3.68,1.94)
-
 outcome <- "polrights_fh"
-outcome <- "garbage"
 
 models <- list()
 for (i in 1:length(vars)) {
@@ -34,4 +29,4 @@ subsets <- map(models, function(x) lm(x, data)) %>%
 
 subsets %>% View()
 
-# write_csv(subsets, here::here("data", "best_subsets.csv"))
+write_csv(subsets, here::here("data", "best_subsets.csv"))

### 2020-11-04 R/cleaningscript.R

@@ -8,18 +8,19 @@ cleaning <- function(df){
   df <- pivot_longer(df, cols = -country, names_to = "year")
 }
 
-data <- files %>% 
+files %>% 
   map(function(x) read_csv(paste0("raw_data/", x))) %>% 
   setNames(gsub("\\.csv$", "", files)) %>% 
   map(cleaning) %>% 
   bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id) 
-
-
-
-# Filtering ---------------------------------------------------------------
-data %>% filter(year > 2000) %>% 
+  pivot_wider(names_from = id) # %>% 
 write_csv(here::here("data", "df.csv"))
 
-data <- read_csv(here::here("data", "df.csv")) 
+# Filtering ---------------------------------------------------------------
+data <- read_csv(here::here("data", "df.csv")) %>% 
+  filter(year > 2009) 
+
+data %>% View()
+
+dim(data)
 

### 2020-11-04 R/visualization.R

@@ -3,7 +3,7 @@ library(tidyverse)
 theme_set(theme_light())
 
 data <- read_csv(here::here("data", "df.csv"))
-subsets <- read_csv(here::here("data", "subsets.csv"))
+best_subsets <- read_csv(here::here("data", "best_subsets.csv"))
 
 corr_matrix <- data %>% 
   select(-year) %>% 
@@ -11,20 +11,23 @@ corr_matrix <- data %>%
   cor(.,  use = "complete.obs")
 
 
-
 data %>% 
+  filter(year > 2015) %>% 
   ggplot(mapping = aes(x = freedix_fh)) + 
   geom_histogram(bins = 10)
 
 data %>% 
+  filter(year > 2015) %>% 
   ggplot(mapping = aes(x = polrights_fh)) + 
   geom_histogram()
 
 data %>% 
+  filter(year > 2015) %>% 
   ggplot(mapping = aes(x = cliberities_fh)) + 
   geom_histogram()
 
 data %>% 
+  filter(year > 2015) %>% 
   mutate(trans_civlib = exp(cliberities_fh)) %>% 
   ggplot(mapping = aes(x = trans_civlib)) + 
   geom_histogram()
@@ -45,52 +48,38 @@ data %>%
       aes(x = gini, y = polrights_fh), size = 5, color = "red") +
   labs(x = "GINI Coeffeceint", y = "Political Rights")
 
+
 data %>% 
   ggplot(aes(x = gini, y = polrights_fh)) + 
   geom_smooth(se = FALSE)
 
-r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+r <- best_subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
 
-subsets %>% 
+best_subsets %>% 
   ggplot(aes(x = df, y = adj.r.squared)) + 
   geom_point() + 
   geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
   labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
 
-AIC <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+AIC <- best_subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
 
-subsets %>% 
+best_subsets %>% 
   ggplot(aes(x = df, y = AIC)) + 
[…]

### 2020-11-05 R/cleaningscript.R
removed projections

@@ -18,8 +18,9 @@ data <- files %>%
 
 
 # Filtering ---------------------------------------------------------------
-data %>% filter(year > 2000) %>% 
-write_csv(here::here("data", "df.csv"))
 
-data <- read_csv(here::here("data", "df.csv")) 
+data %>%
+  filter(year > 2000, year > 2019) %>% 
+  write_csv(here::here("data", "df.csv"))
 
+# data <- read_csv(here::here("data", "df.csv")) 

### 2020-11-05 R/best_subset_selection.R
there is no way that transformation is appropriate

@@ -10,11 +10,7 @@ vars <- data %>%
   select(-country, -year, -ends_with("_fh")) %>%
   names()
 
-# make it continuous
-data$garbage <- data$polrights_fh + rnorm(length(data$polrights_fh),3.68,1.94)
-
 outcome <- "polrights_fh"
-outcome <- "garbage"
 
 models <- list()
 for (i in 1:length(vars)) {
@@ -32,6 +28,15 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   distinct() %>% 
   rename(model = id) 
 
-subsets %>% View()
+subsets %>% 
+  write_csv(here::here("data", "best_subsets.csv"))
 
-# write_csv(subsets, here::here("data", "best_subsets.csv"))
+
+
+
+
+# this cannot be right ---------------------------------------------------
+
+
+data$garbage <- data$polrights_fh + rnorm(length(data$polrights_fh),3.68,1.94)
+outcome <- "garbage"

### 2020-11-05 R/cleaningscript.R
removed projections

@@ -20,7 +20,7 @@ data <- files %>%
 # Filtering ---------------------------------------------------------------
 
 data %>%
-  filter(year > 2000, year > 2019) %>% 
+  filter(year > 2000, year < 2019) %>% 
   write_csv(here::here("data", "df.csv"))
 
 # data <- read_csv(here::here("data", "df.csv")) 

### 2020-11-05 meetingquestions.Rmd
added meeting q's

---
title: "meeting q"
author: "Joe Despres"
date: "11/5/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(patchwork)
theme_set(theme_light())
data <- read_csv(here::here("data", "df.csv"))
```

```{r}
dep_vars <- select(data, ends_with("_fh")) %>% names()
resp_vars <- select(data, -ends_with("_fh")) %>% names()
dep_vars
resp_vars
```

Our dependent variables are indexes measured in increments of 0.5, can we use regression methods without making extreme transformations?

```{r}
p1 <- data %>% 
  ggplot(mapping = aes(x = -freedix_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Freedom Index", subtitle = 'Further Right More "Free"')

p2 <- data %>% 
  ggplot(mapping = aes(x = -polrights_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Political Rights Index")

p3 <- data %>% 
  ggplot(mapping = aes(x = -cliberities_fh)) + 
  geom_histogram(bins = 15) + labs(title = "Civil Liberties Index")

p1 + p2 + p3

```

Missing values

```{r}
skimr::skim(data)
str(data)
data %>% view()
```

Best subsets resuls show most vars are insignificant. Can we procede with the project?

```{r}
models <- list()
for (i in 1:length(vars)) {
  vc <- combn(vars,i)
  for (j in 1:ncol(vc)) {
    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
    models <- c(models, model)
  }
}

subsets <- map(models, function(x) lm(x, data)) %>% 
  map(broom::glance) %>% 
  setNames(models) %>% 
  bind_rows(.id = "id") %>% 
  distinct() %>% 
  rename(model = id)

```

```{r}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
```
at 5 degrees of freedom
```{r}
model_df5 <- subsets %>% filter(df == 5) %>% 
  arrange(desc(adj.r.squared)) %>% 
  select(model) %>% head(1) %>% as.character()

model_df5
fit <- lm(model_df5, data = data)
summary(fit)
```

```{r}
hist(resid(fit))
```

at 4 degrees of freedom
```{r}
model_df4 <- subsets %>% filter(df == 4) %>% 
  arrange(desc(adj.r.squared)) %>% 
  select(model) %>% head(1) %>% as.character()

fit <- lm(model_df4, data = data)
summary(fit)
```

### 2020-11-05 meetingquestions.Rmd
removed journalist killed and everything but oecd and latin america

@@
 resp_vars <- select(data, -ends_with("_fh")) %>% names()
+# note all.equal(data$cliberities_fh, data$freedix_fh)
 dep_vars
@@
 ```{r}
+
 p1 <- data %>% 
-  ggplot(mapping = aes(x = -freedix_fh)) + 
-  geom_histogram(bins = 15) + labs(title = "Freedom Index", subtitle = 'Further Right More "Free"')
+  ggplot(mapping = aes(x = -polrights_fh)) + 
+  geom_histogram(bins = 15) + labs(title = "Political Rights Index", subtitle = 'Further Right More "Free"')
 
 p2 <- data %>% 
-  ggplot(mapping = aes(x = -polrights_fh)) + 
-  geom_histogram(bins = 15) + labs(title = "Political Rights Index")
+  ggplot(mapping = aes(x = -cliberities_fh)) + 
+  geom_histogram(bins = 15) + labs(title = "Civil Liberties Index", subtitle = 'Further Right More Civli Liberties')
 
-p3 <- data %>% 
-  ggplot(mapping = aes(x = -cliberities_fh)) + 
-  geom_histogram(bins = 15) + labs(title = "Civil Liberties Index")
-
-p1 + p2 + p3
+p1 + p2
 
@@
 
-Missing values
+Missing values we are running into a lot of incomplete rows. If we drop all the NA we lose more than 90% of our data.
 
@@
 
-Best subsets resuls show most vars are insignificant. Can we procede with the project?
+Best subsets results show most vars are insignificant. Can we proceed with the project?
 
@@
 ```
+
 at 5 degrees of freedom
@@
 summary(fit)
+
 ```

### 2020-11-05 R/cleaningscript.R

@@ -13,14 +13,64 @@ data <- files %>%
   setNames(gsub("\\.csv$", "", files)) %>% 
   map(cleaning) %>% 
   bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id) 
+  pivot_wider(names_from = id)
 
 
 
 # Filtering ---------------------------------------------------------------
 
-data %>%
-  filter(year > 2000, year < 2019) %>% 
-  write_csv(here::here("data", "df.csv"))
 
 # data <- read_csv(here::here("data", "df.csv")) 
+OECD <- tibble::tribble(
+          ~Country,            ~Application,      ~Negotiations,            ~Invitation,    ~`Membership[1]`, ~Geographic.location,                                                                                                                                                                           ~Notes,
+       "Australia",                      NA,                 NA,                     NA,       "7 June 1971",            "Oceania",                                                                                                                                                                               NA,
+         "Austria",                      NA,                 NA,                     NA, "29 September 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
+         "Belgium",                      NA,                 NA,                     NA, "13 September 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
+          "Canada",                      NA,                 NA,                     NA,     "10 April 1961",      "North America",                                                                                                                                                                               NA,
+           "Chile", "November 2003[57][58]",  "16 May 2007[26]", "15 December 2009[59]",        "7 May 2010",      "South America",                                                                                                                                                                               NA,
+        "Colombia",   "24 January 2011[60]",  "30 May 2013[30]",      "25 May 2018[61]",     "28 April 2020",      "South America",                                                                                                                                                                               NA,
+  "Czech Republic",      "January 1994[62]",  "8 June 1994[63]", "24 November 1995[62]",  "21 December 1995",             "Europe",                                                                                                 "Was a member of the rival Comecon from 1949 to 1991 as part of Czechoslovakia.",
+         "Denmark",                      NA,                 NA,                     NA,       "30 May 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
+         "Estonia",                      NA,  "16 May 2007[26]",      "10 May 2010[64]",   "9 December 2010",             "Europe",                                                                                                                                                                               NA,
+         "Finland",                      NA,                 NA,                     NA,   "28 January 1969",             "Europe",                                                                                                                                                                               NA,
[…]

### 2020-11-05 R/visualization.R

@@ -6,9 +6,11 @@ data <- read_csv(here::here("data", "df.csv"))
 subsets <- read_csv(here::here("data", "subsets.csv"))
 
 corr_matrix <- data %>% 
-  select(-year) %>% 
+  select(-year, -ends_with("_fh")) %>% 
   select_if(is.numeric) %>% 
   cor(.,  use = "complete.obs")
+View(corr_matrix)
+
 
 
 
@@ -79,6 +81,8 @@ model_df4 <- subsets %>% filter(df == 4) %>%
 
 fit <- lm(model_df4, data = data)
 fit %>% broom::tidy()
+
+summary(fit)
 
 fit <- lm(model_df3, data = data)
 fit %>% broom::tidy()

### 2020-11-05 R/best_subset_selection.R
.

@@ -29,7 +29,7 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   rename(model = id) 
 
 subsets %>% 
-  write_csv(here::here("data", "best_subsets.csv"))
+  write_csv(here::here("data", "subsets.csv"))
 
 
 

### 2020-11-05 meetingquestions.Rmd
.

@@
 
-Our dependent variables are indexes measured in increments of 0.5, can we use regression methods without making extreme transformations?
+Our dependent variables are indexes measured from 1 to 7. With one being the highest degree of freedom and rights and , can we use regression methods without making extreme transformations?
+
+*subtract mean and divide by sd.*
 
@@
 
+```{r}
+
+```
+
 at 5 degrees of freedom
@@
 summary(fit)
+df = matrix(c(predict(fit), data$polrights_fh), ncol = 2)
+
+matplot(df)
+
+plot(predict(fit), data$polrights_fh)
 

### 2020-11-07 R/cleaningscript.R
imputed values

@@ -18,59 +18,24 @@ data <- files %>%
 
 
 # Filtering ---------------------------------------------------------------
-
-
-# data <- read_csv(here::here("data", "df.csv")) 
-OECD <- tibble::tribble(
-          ~Country,            ~Application,      ~Negotiations,            ~Invitation,    ~`Membership[1]`, ~Geographic.location,                                                                                                                                                                           ~Notes,
-       "Australia",                      NA,                 NA,                     NA,       "7 June 1971",            "Oceania",                                                                                                                                                                               NA,
-         "Austria",                      NA,                 NA,                     NA, "29 September 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
-         "Belgium",                      NA,                 NA,                     NA, "13 September 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
-          "Canada",                      NA,                 NA,                     NA,     "10 April 1961",      "North America",                                                                                                                                                                               NA,
-           "Chile", "November 2003[57][58]",  "16 May 2007[26]", "15 December 2009[59]",        "7 May 2010",      "South America",                                                                                                                                                                               NA,
-        "Colombia",   "24 January 2011[60]",  "30 May 2013[30]",      "25 May 2018[61]",     "28 April 2020",      "South America",                                                                                                                                                                               NA,
-  "Czech Republic",      "January 1994[62]",  "8 June 1994[63]", "24 November 1995[62]",  "21 December 1995",             "Europe",                                                                                                 "Was a member of the rival Comecon from 1949 to 1991 as part of Czechoslovakia.",
-         "Denmark",                      NA,                 NA,                     NA,       "30 May 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
-         "Estonia",                      NA,  "16 May 2007[26]",      "10 May 2010[64]",   "9 December 2010",             "Europe",                                                                                                                                                                               NA,
-         "Finland",                      NA,                 NA,                     NA,   "28 January 1969",             "Europe",                                                                                                                                                                               NA,
-          "France",                      NA,                 NA,                     NA,     "7 August 1961",             "Europe",                                                                                                                                                                "OEEC member.[6]",
-         "Germany",                      NA,                 NA,                     NA, "27 September 1961",             "Europe", "Joined OEEC in 1949 (West Germany).[65] Previously represented by the Trizone.[6] East Germany was a member of the rival Comecon from 1950 until German reunification in 1990.",
[…]

### 2020-11-07 R/cleaningscript.R
imputed country median as na

@@ -2,7 +2,7 @@ library(tidyverse)
 
 # Read and Clean ----------------------------------------------------------
 files <- list.files(path = here::here("raw_data"), pattern = ".csv")
-files
+
 
 cleaning <- function(df){
   df <- pivot_longer(df, cols = -country, names_to = "year")
@@ -23,8 +23,8 @@ countries <- readRDS(here::here("data", "countries.RDS"))
 data <- data %>%
   filter(year > 2000, year < 2019, country %in% countries) %>% 
   group_by(country) %>%
-  mutate_all(list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
-  # Iceland spent 0 so I needed to manually recode that
+  mutate_at(vars(-country),list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
+# Iceland spent 0 so I needed to manually recode that
   mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
   mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
          # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
@@ -38,4 +38,4 @@ data <- data %>%
 
 # writing -----------------------------------------------------------------
 write_csv(data, here::here("data", "df.csv"))
-
+skimr::skim(ungroup(data))

### 2020-11-07 R/best_subset_selection.R
re-ran with new data

@@ -28,15 +28,7 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   distinct() %>% 
   rename(model = id) 
 
-subsets %>% 
-  write_csv(here::here("data", "subsets.csv"))
+# writing -----------------------------------------------------------------
 
+write_csv(subsets, here::here("data", "subsets.csv"))
 
-
-
-
-# this cannot be right ---------------------------------------------------
-
-
-data$garbage <- data$polrights_fh + rnorm(length(data$polrights_fh),3.68,1.94)
-outcome <- "garbage"

### 2020-11-07 R/cleaningscript.R
.

@@ -33,9 +33,7 @@ data <- data %>%
          murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
          murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34))
 
-
-
-
 # writing -----------------------------------------------------------------
+
 write_csv(data, here::here("data", "df.csv"))
 skimr::skim(ungroup(data))

### 2020-11-07 R/cleaningscript.R
moved y var to first position in df

@@ -31,7 +31,8 @@ data <- data %>%
          # these murder rates were not included in the gapminder but i didnt want to 
          # lose 3 important countries in LA
          murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
-         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34))
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
+  relocate(polrights_fh)
 
 # writing -----------------------------------------------------------------
 

### 2020-11-07 R/visualization.R
.

@@ -4,31 +4,22 @@ theme_set(theme_light())
 
 data <- read_csv(here::here("data", "df.csv"))
 subsets <- read_csv(here::here("data", "subsets.csv"))
+names(data)
 
 corr_matrix <- data %>% 
-  select(-year, -ends_with("_fh")) %>% 
-  select_if(is.numeric) %>% 
+  select(-year, -country) %>% 
   cor(.,  use = "complete.obs")
+
 View(corr_matrix)
 
-
-
+names(data)
 
 data %>% 
-  ggplot(mapping = aes(x = freedix_fh)) + 
+  ggplot(mapping = aes(x = polrights_fh)) + 
   geom_histogram(bins = 10)
 
 data %>% 
   ggplot(mapping = aes(x = polrights_fh)) + 
-  geom_histogram()
-
-data %>% 
-  ggplot(mapping = aes(x = cliberities_fh)) + 
-  geom_histogram()
-
-data %>% 
-  mutate(trans_civlib = exp(cliberities_fh)) %>% 
-  ggplot(mapping = aes(x = trans_civlib)) + 
   geom_histogram()
 
 data %>% 
@@ -74,6 +65,7 @@ model_df5 <- subsets %>% filter(df == 5) %>%
 model_df5
 fit <- lm(model_df5, data = data)
 fit %>% broom::tidy()
+summary(fit)
 
 model_df4 <- subsets %>% filter(df == 4) %>% 
   arrange(desc(adj.r.squared)) %>% 

### 2020-11-07 R/cleaningscript.R
reformat

@@ -15,9 +15,8 @@ data <- files %>%
   bind_rows(.id = "id") %>% 
   pivot_wider(names_from = id)
 
-
-
 # Filtering ---------------------------------------------------------------
+
 countries <- readRDS(here::here("data", "countries.RDS"))
 
 data <- data %>%
@@ -37,4 +36,5 @@ data <- data %>%
 # writing -----------------------------------------------------------------
 
 write_csv(data, here::here("data", "df.csv"))
+
 skimr::skim(ungroup(data))

### 2020-11-09 R/cleaningscript.R
reversed order

@@ -3,7 +3,6 @@ library(tidyverse)
 # Read and Clean ----------------------------------------------------------
 files <- list.files(path = here::here("raw_data"), pattern = ".csv")
 
-
 cleaning <- function(df){
   df <- pivot_longer(df, cols = -country, names_to = "year")
 }

### 2020-11-09 R/cleaningscript.R
.

@@ -30,7 +30,7 @@ data <- data %>%
          # lose 3 important countries in LA
          murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
          murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
-  relocate(polrights_fh)
+  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh))
 
 # writing -----------------------------------------------------------------
 

### 2020-11-10 slides.Rmd
.

@@
 
-background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
-
 ```{r setup, include=FALSE}
 options(htmltools.dir.version = FALSE, echo = FALSE)
-library(gtsummary)
-source(here::here("R", "visualization.R"))
+source(here::here("R", "regression.R"))
 options(digits = 3)
@@
 ```{r echo=FALSE}
-best_subsets %>% 
+subsets %>% 
   mutate_if(is.numeric, round, 3) %>% 
@@
 
----
+# Introduction
 
-???
+# Model
 
-Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)
+# Findings
 
----
+# Conclusions
+
 class: center, middle

### 2020-11-10 R/best_subset_selection.R

@@ -32,3 +32,4 @@ subsets <- map(models, function(x) lm(x, data)) %>%
 
 write_csv(subsets, here::here("data", "subsets.csv"))
 
+subsets %>% select(model) %>% tail(1) %>% as.character()

### 2020-11-10 R/cleaningscript.R

@@ -30,10 +30,12 @@ data <- data %>%
          # lose 3 important countries in LA
          murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
          murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
-  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh))
+  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
+                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)
 
 # writing -----------------------------------------------------------------
 
 write_csv(data, here::here("data", "df.csv"))
 
+View(data)
 skimr::skim(ungroup(data))

### 2020-11-10 R/regression.R

@@ -1,0 +1,70 @@
+library(tidyverse)
+
+data <- readr::read_csv(here::here("data", "df.csv"))
+subsets <- readr::read_csv(here::here("data", "subsets.csv"))
+
+# First model -------------------------------------------------------------
+
+model_df5_formula <- subsets %>% filter(df == 5) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+model_df5 <- lm(polrights_fh ~ corruption_perception_index_cpi + 
+            edu_exp_gdp_per_person + 
+            life_expectancy_years + 
+            military_spending_pct_of_gdp + 
+            murder_per_mil_people, data)
+
+subsets %>% filter(df == 9) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+summary(model_df5)
+
+hist(resid(model_df5), breaks = 100)
+qqnorm(resid(model_df5))
+boxplot(resid(model_df5))
+
+plot(data$edu_exp_gdp_per_person, resid(model_df5))
+plot(data$corruption_perception_index_cpi, resid(model_df5))
+plot(data$polrights_fh, resid(model_df5))
+plot(data$electricity_use_per_person, resid(model_df5))
+plot(data$gini, resid(model_df5))
+plot(data$internet_users, resid(model_df5))
+plot(data$labour_force_participation_rate_percent, resid(model_df5))
+plot(data$life_expectancy_years, resid(model_df5))
+plot(data$military_spending_pct_of_gdp, resid(model_df5))
+plot(data$murder_per_mil_people, resid(model_df5))
+
+
+sort(resid(model_df5))
+data$resid <- resid(model_df5)
+
+# Second model ------------------------------------------------------------
+
+subsets %>% filter(df == 4) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  View()
+
+model_df4_formula <- subsets %>% filter(df == 4) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character() 
+
+fit_df4 <- lm(model_df4_formula, data)
+
+summary(fit_df4)
+
+# third -------------------------------------------------------------------
+
+subsets %>% filter(df == 6) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  View()
+
[…]

### 2020-11-10 slides.Rmd
update

--- 2020-11-03 slides.Rmd
@@
     lib_dir: libs
+    mathjax: null
     nature:
@@
 
-background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
-
 ```{r setup, include=FALSE}
-options(htmltools.dir.version = FALSE)
+source(here::here("R", "regression.R"))
+options(htmltools.dir.version = FALSE, echo = FALSE)
 ```
 
-???
-
-Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)
+# Introduction
+- political freedom as a function of 
+- variables
 
 ---
-class: center, middle
-
-# xaringan
-
-### /ʃaː.'riŋ.ɡan/
+```{r echo=FALSE}
+subsets %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  rename(a_rsq = adj.r.squared) %>% 
+  select(df, a_rsq, model) %>% 
+  arrange(desc(a_rsq)) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
+```
 
 ---
-class: inverse, center, middle
+# Model
 
-# Get Started
+```{r}
+# equatiomatic::extract_eq(model = model_df5, intercept = "beta", terms_per_line = 1)
+```
+<script src="https://cdnjs.cloudflare.com/ajax/libs/mathjax/2.7.1/MathJax.js?config=TeX-AMS_HTML"></script>
+$$
+
+\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) + \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+
+$$
 
@@
 
-# Hello World
-
-Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):
-
-```{r eval=FALSE, tidy=FALSE}
-devtools::install_github("yihui/xaringan")
-```
-
---
-
-You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.
-
-- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>
-
---
-
-- Click the `Knit` button to compile it;
-
---
-
-- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.
-
-.footnote[
-[1] 中文用户请看[这份教程](https://slides.yihui.org/xaringan/zh-CN.html)
-
-[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
-]
+# Model
 
 ---
-background-image: url(`r xaringan:::karl`)
-background-position: 50% 50%
-class: center, bottom, inverse
-
-# You only live once!
-
----
-
-# Hello Ninja
-
-As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:
-
-1. The [remark.js](https://remarkjs.com) library;
-
-1. The **xaringan** package;
-
-Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**.
-The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).
-
----
-
-# remark.js
-
-You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to
-
-- create a new slide (Markdown syntax<sup>*</sup> and slide properties);
-
-- format a slide (e.g. text alignment);
-
-- configure the slideshow;
-
-- and use the presentation (keyboard shortcuts).
-
-It is important to be familiar with remark.js before you can understand the options in **xaringan**.
-
-.footnote[[*] It is different with Pandoc's Markdown!
-It is limited but should be enough for presentation purposes.
-Come on...
-You do not need a slide for the Table of Contents!
-Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]
-
----
-background-image: url(`r xaringan:::karl`)
-background-size: cover
-class: center, bottom, inverse
-
-# I was so happy to have discovered remark.js!
-
----
-class: inverse, middle, center
-
-# Using xaringan
-
----
-
-# xaringan
-
-Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.
-
-```yaml
----
-title: "A Cool Presentation"
-output:
-  xaringan::moon_reader:
-    yolo: true
-    nature:
-      autoplay: 30000
----
-```
-
-See the help page `?xaringan::moon_reader` for all possible options that you can use.
-
----
-
-# remark.js vs xaringan
-
-Some differences between using remark.js (left) and using **xaringan** (right):
-
-.pull-left[
-1. Start with a boilerplate HTML file;
-
-1. Plain Markdown;
-
-1. Write JavaScript to autoplay slides;
-
-1. Manually configure MathJax;
-
-1. Highlight code with `*`;
-
-1. Edit Markdown source and refresh browser to see updated slides;
-]
-
-.pull-right[
-1. Start with an R Markdown document;
-
-1. R Markdown (can embed R/other code chunks);
-
-1. Provide an option `autoplay`;
-
-1. MathJax just works;<sup>*</sup>
-
-1. Highlight code with `{{}}`;
-
-1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
-]
-
-.footnote[[*] Not really. See next page.]
-
----
-
-# Math Expressions
-
-You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:
-
-```
-$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
-```
-
-$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
-
-Limitations:
-
-1.
-The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;
-
-1. There should not be spaces after the opening `$` or before the closing `$`.
-
-1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).
-
----
-
-# R Code
-
-```{r comment='#'}
-# a boring regression
-fit = lm(dist ~ 1 + speed, data = cars)
-coef(summary(fit))
-dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
-grep('天', dojutsu, value = TRUE)
-```
-
----
-
-# R Plots
-
-```{r cars, fig.height=4, dev='svg'}
-par(mar = c(4, 4, 1, .1))
-plot(cars, pch = 19, col = 'darkgray', las = 1)
-abline(fit, lwd = 2)
-```
-
----
-
-# Tables
-
-If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,
-
-```{r}
-knitr::kable(head(iris), format = 'html')
-```
-
----
-
-# HTML Widgets
-
-I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.
-
-Similarly, the Shiny mode (`runtime: shiny`) does not work.
-I might get these issues fixed in the future, but these are not of high priority to me.
-I never turn my presentation into a Shiny app.
-When I need to demonstrate more complicated examples, I just launch them separately.
-It is convenient to share slides with other people when they are plain HTML/JS applications.
-
-See the next page for two HTML widgets.
-
----
-
-```{r out.width='100%', fig.height=6, eval=require('leaflet')}
-library(leaflet)
-leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
-```
-
----
-
-```{r eval=require('DT'), tidy=FALSE}
-DT::datatable(
-  head(iris, 10),
-  fillContainer = FALSE, options = list(pageLength = 8)
-)
-```
-
----
-
-# Some Tips
-
-- Do not forget to try the `yolo` option of `xaringan::moon_reader`.
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        yolo: true
-    ```
-
----
-
-# Some Tips
-
-- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds in a lightning talk:
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          autoplay: 30000
-    ```
-
-- If you want to restart the play after it reaches the last slide, you may set the sub-option `loop` to TRUE, e.g.,
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          autoplay:
-            interval: 30000
-            loop: true
-    ```
-
----
-
-# Some Tips
-
-- A countdown timer can be added to every page of the slides using the `countdown` option under `nature`, e.g. if you want to spend one minute on every page when you give the talk, you can set:
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          countdown: 60000
-    ```
-
-    Then you will see a timer counting down from `01:00`, to `00:59`, `00:58`, ... When the time is out, the timer will continue but the time turns red.
-
----
-
-# Some Tips
-
-- The title slide is created automatically by **xaringan**, but it is just another remark.js slide added before your other slides.
-
-    The title slide is set to `class: center, middle, inverse, title-slide` by default.
-You can change the classes applied to the title slide with the `titleSlideClass` option of `nature` (`title-slide` is always applied).
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          titleSlideClass: [top, left, inverse]
-    ```
-
---
-
-- If you'd like to create your own title slide, disable **xaringan**'s title slide with the `seal = FALSE` option of `moon_reader`.
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        seal: false
-    ```
-
----
-
-# Some Tips
-
-- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.org/xaringan/incremental.html) for examples.
-
-- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          highlightLines: true
-    ```
-
-    See examples on the next page.
-
----
-
-# Some Tips
-
-.pull-left[
-An example using a leading `*`:
-
-    ```r
-    if (TRUE) {
-    ** message("Very important!")
-    }
-    ```
-Output:
-```r
-if (TRUE) {
-* message("Very important!")
-}
-```
-
-This is invalid R code, so it is a plain fenced code block that is not executed.
-]
-
-.pull-right[
-An example using `{{}}`:
-
-````
-`r ''````{r tidy=FALSE}
-if (TRUE) {
-*{{ message("Very important!") }}
-}
-```
-````
-Output:
-```{r tidy=FALSE}
-if (TRUE) {
-{{ message("Very important!") }}
-}
-```
-
-It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
-]
-
----
-
-# Some Tips
-
-An example of using the trailing comment `#<<` to highlight lines:
-
-````markdown
-`r ''````{r tidy=FALSE}
-library(ggplot2)
-ggplot(mtcars) + 
-  aes(mpg, disp) + 
-  geom_point() +   #<<
-  geom_smooth()    #<<
-```
-````
-
-Output:
-
-```{r tidy=FALSE, eval=FALSE}
-library(ggplot2)
-ggplot(mtcars) + 
-  aes(mpg, disp) + 
-  geom_point() +   #<<
-  geom_smooth()    #<<
-```
-
----
-
-# Some Tips
-
-When you enable line-highlighting, you can also use the chunk option `highlight.output` to highlight specific lines of the text output from a code chunk.
-For example, `highlight.output = TRUE` means highlighting all lines, and `highlight.output = c(1, 3)` means highlighting the first and third line.
-
-````md
-`r ''````{r, highlight.output=c(1, 3)}
-head(iris)
-```
-````
-
-```{r, highlight.output=c(1, 3), echo=FALSE}
-head(iris)
-```
-
-Question: what does `highlight.output = c(TRUE, FALSE)` mean? (Hint: think about R's recycling of vectors)
-
----
-
-# Some Tips
-
-- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).
-
-- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.
-
-- Then change the `chakra` option in YAML to point to this file, e.g.
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        chakra: libs/remark-latest.min.js
-    ```
-
-- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally.
-The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.
-
----
-
-# Macros
-
-- remark.js [allows users to define custom macros](https://github.com/yihui/xaringan/issues/80) (JS functions) that can be applied to Markdown text using the syntax `![:macroName arg1, arg2, ...]` or `![:macroName arg1, arg2, ...](this)`.
-For example, before remark.js initializes the slides, you can define a macro named `scale`:
-
-    ```js
-    remark.macros.scale = function (percentage) {
-      var url = this;
-      return '<img src="' + url + '" style="width: ' + percentage + '" />';
-    };
-    ```
-
-    Then the Markdown text
-
-    ```markdown
-    ![:scale 50%](image.jpg)
-    ```
-
-    will be translated to
-
-    ```html
-    <img src="image.jpg" style="width: 50%" />
-    ```
-
----
-
-# Macros (continued)
-
-- To insert macros in **xaringan** slides, you can use the option `beforeInit` under the option `nature`, e.g.,
-
-    ```yaml
-    output:
-      xaringan::moon_reader:
-        nature:
-          beforeInit: "macros.js"
-    ```
-
-    You save your remark.js macros in the file `macros.js`.
-
-- The `beforeInit` option can be used to insert arbitrary JS code before `remark.create()`. Inserting macros is just one of its possible applications.
-
----
-
-# CSS
-
-Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.
-
-You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css).
-You can completely replace it with your own CSS files, or define new rules to override the default.
-See the help page `?xaringan::moon_reader` for more information.
-
----
-
-# CSS
-
-For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:
-
-```css
-@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);
-
-.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
-```
-
-Then set the `css` option in the YAML metadata:
-
-```yaml
-output:
-  xaringan::moon_reader:
-    css: ["default", "ubuntu-mono.css"]
-```
-
-Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.
-
-See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.
-
----
-
-# Themes
-
-Don't want to learn CSS?
-Okay, you can use some user-contributed themes.
-A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name.
-Below are some existing themes:
-
-```{r, R.options=list(width = 70)}
-names(xaringan:::list_css())
-```
-
----
-
-# Themes
-
-To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,
-
-```yaml
-output:
-  xaringan::moon_reader:
-    css: [default, metropolis, metropolis-fonts]
-```
-
-If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.org/en/2017/10/xaringan-themes).
-
----
-class: inverse, middle, center
-background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
-background-size: contain
-
-# Naruto
-
----
-background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
-background-size: 100px
-background-position: 90% 8%
-
-# Sharingan
-
-The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:
-
-- the "Eye of Insight"
-
-- the "Eye of Hypnotism"
-
-I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>
-
-.footnote[
-[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.
-
-[2] By comparison, bad presentations only put the audience to sleep.
-
-[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
-]
-
----
-
-# Naruto terminology
-
-The **xaringan** package borrowed a few terms from Naruto, such as
-
-- [Sharingan](https://naruto.fandom.com/wiki/Sharingan) (写輪眼; the package name)
-
-- The [moon reader](https://naruto.fandom.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)
-
-- [Chakra](https://naruto.fandom.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)
-
-- [Nature transformation](https://naruto.fandom.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)
-
-- The [infinite moon reader](https://naruto.fandom.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)
-
-- The [summoning technique](https://naruto.fandom.com/wiki/Summoning_Technique) (download remark.js from the web)
-
-You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.
-
----
-
-class: center
-
-# Hand seals (印)
-
-Press `h` or `?` to see the possible ninjutsu you can use in remark.js.
-
-![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)
-
----
-
-class: center, middle
-
-# Thanks!
-
-Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
-
-The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
+# Conclusions

### 2020-11-10 R/regression.R

@@ -43,8 +43,7 @@ data$resid <- resid(model_df5)
 # Second model ------------------------------------------------------------
 
 subsets %>% filter(df == 4) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  View()
+  arrange(desc(adj.r.squared)) 
 
 model_df4_formula <- subsets %>% filter(df == 4) %>% 
   arrange(desc(adj.r.squared)) %>% 
@@ -57,8 +56,7 @@ summary(fit_df4)
 # third -------------------------------------------------------------------
 
 subsets %>% filter(df == 6) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  View()
+  arrange(desc(adj.r.squared)) 
 
 model_df6_formula <- subsets %>% filter(df == 6) %>% 
   arrange(desc(adj.r.squared)) %>% 

### 2020-11-10 slides.Rmd
started slides

@@
     lib_dir: libs
-    mathjax: null
     nature:
@@
 options(htmltools.dir.version = FALSE, echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 # Introduction
-- political freedom as a function of 
-- variables
+- study political freedom as a function of social, economic, political factors
+- gapminder data
+- filtered to only include OECD
 
 ---
-```{r echo=FALSE}
+
+# Define political freedom
+summarsze fh index
+
+---
+
+```{r message=FALSE}
 subsets %>% 
+  group_by(df) %>% 
+  filter(adj.r.squared == max(adj.r.squared)) %>% 
   mutate_if(is.numeric, round, 3) %>% 
@@
 
+```{r, message=FALSE, warning=FALSE, fig.dim=3}
+r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+
+subsets %>% 
+  ggplot(aes(x = df, y = adj.r.squared)) + 
+  geom_point() + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
+  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
+```
+
 ---
@@
 
-```{r}
-# equatiomatic::extract_eq(model = model_df5, intercept = "beta", terms_per_line = 1)
+```{r include=FALSE}
+equatiomatic::extract_eq(model = model_df5, intercept = "beta", terms_per_line = 1)
 ```
-<script src="https://cdnjs.cloudflare.com/ajax/libs/mathjax/2.7.1/MathJax.js?config=TeX-AMS_HTML"></script>
-$$
 
-\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) + \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
-
-$$
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
 
@@
 
-# Model
+```{r}
+broom::tidy(model_df5) %>% 
+  kableExtra::kable()
+```
+---
 
----
-# Conclusions
+```{r}
+broom::tidy(model_df5) %>% 
+  kableExtra::kable() %>% 
+  kableExtra::row_spec(4, bold = T, color = "white", background = "#D7261E")
+```

### 2020-11-10 R/regression.R

@@ -19,26 +19,6 @@ subsets %>% filter(df == 9) %>%
   arrange(desc(adj.r.squared)) %>% 
   select(model) %>% head(1) %>% as.character()
 
-summary(model_df5)
-
-hist(resid(model_df5), breaks = 100)
-qqnorm(resid(model_df5))
-boxplot(resid(model_df5))
-
-plot(data$edu_exp_gdp_per_person, resid(model_df5))
-plot(data$corruption_perception_index_cpi, resid(model_df5))
-plot(data$polrights_fh, resid(model_df5))
-plot(data$electricity_use_per_person, resid(model_df5))
-plot(data$gini, resid(model_df5))
-plot(data$internet_users, resid(model_df5))
-plot(data$labour_force_participation_rate_percent, resid(model_df5))
-plot(data$life_expectancy_years, resid(model_df5))
-plot(data$military_spending_pct_of_gdp, resid(model_df5))
-plot(data$murder_per_mil_people, resid(model_df5))
-
-
-sort(resid(model_df5))
-data$resid <- resid(model_df5)
 
 # Second model ------------------------------------------------------------
 

### 2020-11-10 R/visualization.R

@@ -44,6 +44,7 @@ data %>%
 
 r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
 
+
 subsets %>% 
   ggplot(aes(x = df, y = adj.r.squared)) + 
   geom_point() + 
@@ -90,3 +91,23 @@ model_df2 <- subsets %>% filter(df == 2) %>%
 fit <- lm(model_df2, data = data)
 fit %>% broom::tidy()
 
+summary(model_df5)
+
+hist(resid(model_df5), breaks = 100)
+qqnorm(resid(model_df5))
+boxplot(resid(model_df5))
+
+plot(data$edu_exp_gdp_per_person, resid(model_df5))
+plot(data$corruption_perception_index_cpi, resid(model_df5))
+plot(data$polrights_fh, resid(model_df5))
+plot(data$electricity_use_per_person, resid(model_df5))
+plot(data$gini, resid(model_df5))
+plot(data$internet_users, resid(model_df5))
+plot(data$labour_force_participation_rate_percent, resid(model_df5))
+plot(data$life_expectancy_years, resid(model_df5))
+plot(data$military_spending_pct_of_gdp, resid(model_df5))
+plot(data$murder_per_mil_people, resid(model_df5))
+
+
+sort(resid(model_df5))
+data$resid <- resid(model_df5)

### 2020-11-10 slides.Rmd
slides

@@
 ---
-
+# Best Subsets
 ```{r message=FALSE}
@@
 ```
-
-```{r, message=FALSE, warning=FALSE, fig.dim=3}
+---
+# Best Subsets
+```{r, message=FALSE, warning=FALSE}
 r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
@@
   geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
-  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
+  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared") + 
+  scale_x_continuous(breaks = 1:9) + 
+  theme_light(base_size = 12)
 ```
@@
 ---
+# show charts
+
+---
+
+# Some model test
+
+---
 

### 2020-11-10 slides.Rmd
outline of slideshow

@@
 
-# Introduction
-- study political freedom as a function of social, economic, political factors
-- gapminder data
-- filtered to only include OECD
+# Outline
+
+* What factors are associated with an increase in political freedom?
+
+--
+
+* study political freedom as a function of social, economic, political factors
+
+--
+
+* From Data provided by the Gapminder Foundation.
+
+---
+class: inverse, middle, center
+
+# Data
+
+---
+
+# Data
+
+* filtered to only include OECD Countries from year 2000 to 2018
 
@@
 # Define political freedom
-summarsze fh index
+
+--
+
+* Freedomhouse index
+
+--
+
+* summarsze fh index
 
@@
 ---
+
+class: inverse, middle, center
+
 # Model
+---
+
+class: center, middle
 
@@
 
+$$
+\large
 \begin{align}
@@
 \end{align}
+$$
 
 ---
-# show charts
+class: center
 
----
-
-# Some model test
-
----
+$$
+\tiny
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
 
@@
 ---
-
+class: center
+$$
+\tiny
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
 ```{r}
@@
 ```
+
+---
+
+class: center, middle
+
+# Thanks You and We are Happy to Take Questions
+
+Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

### 2020-11-11 slides.Rmd
.

@@
 source(here::here("R", "regression.R"))
+library(kableExtra)
 options(htmltools.dir.version = FALSE, echo = FALSE)
@@
 ---
-# Best Subsets
-```{r, message=FALSE, warning=FALSE}
+
+class: center
+### Best Subsets
+```{r, message=FALSE, warning=FALSE, fig.align='center', fig.width=12, fig.height=8}
 r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
@@
   geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
-  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared") + 
+  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
   scale_x_continuous(breaks = 1:9) + 
-  theme_light(base_size = 12)
+  theme_light(base_size = 30)
+
 ```
@@
 broom::tidy(model_df5) %>% 
-  kableExtra::kable()
+  kable()
 ```
 ---
-class: center
+class: animated, fadeIn, center
 $$
@@
 broom::tidy(model_df5) %>% 
-  kableExtra::kable() %>% 
-  kableExtra::row_spec(4, bold = T, color = "white", background = "#D7261E")
+  kable() %>% 
+  row_spec(4, bold = T, color = "white", background = "#D7261E")
 ```
@@
 
+class: center, top
+<font size="1">
+```{r results='asis',out.width='25%', fig.align='center'}
+stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
+                     title = "Regression Results", 
+                     covariate.labels = c(),header = FALSE,
+single.row=FALSE,column.sep.width = "-15pt", column.separate = 1)
+```
+
+---
 class: center, middle

### 2020-11-11 R/best_subset_selection.R
.

@@ -1,35 +1,0 @@
-library(tidyverse)
-
-# best_subset_selection ---------------------------------------------------
-
-data <- read_csv(here::here("data", "df.csv"))
-
-names(data)
-
-vars <- data %>% 
-  select(-country, -year, -ends_with("_fh")) %>%
-  names()
-
-outcome <- "polrights_fh"
-
-models <- list()
-for (i in 1:length(vars)) {
-  vc <- combn(vars,i)
-  for (j in 1:ncol(vc)) {
-    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
-    models <- c(models, model)
-  }
-}
-
-subsets <- map(models, function(x) lm(x, data)) %>% 
-  map(broom::glance) %>% 
-  setNames(models) %>% 
-  bind_rows(.id = "id") %>% 
-  distinct() %>% 
-  rename(model = id) 
-
-# writing -----------------------------------------------------------------
-
-write_csv(subsets, here::here("data", "subsets.csv"))
-
-subsets %>% select(model) %>% tail(1) %>% as.character()

### 2020-11-11 R/cleaningscript.R

@@ -1,41 +1,0 @@
-library(tidyverse)
-
-# Read and Clean ----------------------------------------------------------
-files <- list.files(path = here::here("raw_data"), pattern = ".csv")
-
-cleaning <- function(df){
-  df <- pivot_longer(df, cols = -country, names_to = "year")
-}
-
-data <- files %>% 
-  map(function(x) read_csv(paste0("raw_data/", x))) %>% 
-  setNames(gsub("\\.csv$", "", files)) %>% 
-  map(cleaning) %>% 
-  bind_rows(.id = "id") %>% 
-  pivot_wider(names_from = id)
-
-# Filtering ---------------------------------------------------------------
-
-countries <- readRDS(here::here("data", "countries.RDS"))
-
-data <- data %>%
-  filter(year > 2000, year < 2019, country %in% countries) %>% 
-  group_by(country) %>%
-  mutate_at(vars(-country),list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
-# Iceland spent 0 so I needed to manually recode that
-  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
-  mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
-         # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
-         # these murder rates were not included in the gapminder but i didnt want to 
-         # lose 3 important countries in LA
-         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
-         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
-  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
-                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)
-
-# writing -----------------------------------------------------------------
-
-write_csv(data, here::here("data", "df.csv"))
-
-View(data)
-skimr::skim(ungroup(data))

### 2020-11-11 R/readinghwdata.R

@@ -1,14 +1,0 @@
-
-# reading in hw data ------------------------------------------------------
-
-
-devtools::install_github("bryangoodrich/ALSM")
-library(ALSM)
-
-
-set_names <- function(data){
-  colnames(data) <- setNames(nm = c(paste0("x", seq_along(data) - 1)))
-  colnames(data)[1] <- "y"
-  data
-}
-df <- set_names(CH06PR05)

### 2020-11-11 R/regression.R

@@ -1,48 +1,0 @@
-library(tidyverse)
-
-data <- readr::read_csv(here::here("data", "df.csv"))
-subsets <- readr::read_csv(here::here("data", "subsets.csv"))
-
-# First model -------------------------------------------------------------
-
-model_df5_formula <- subsets %>% filter(df == 5) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character()
-
-model_df5 <- lm(polrights_fh ~ corruption_perception_index_cpi + 
-            edu_exp_gdp_per_person + 
-            life_expectancy_years + 
-            military_spending_pct_of_gdp + 
-            murder_per_mil_people, data)
-
-subsets %>% filter(df == 9) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character()
-
-
-# Second model ------------------------------------------------------------
-
-subsets %>% filter(df == 4) %>% 
-  arrange(desc(adj.r.squared)) 
-
-model_df4_formula <- subsets %>% filter(df == 4) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character() 
-
-fit_df4 <- lm(model_df4_formula, data)
-
-summary(fit_df4)
-
-# third -------------------------------------------------------------------
-
-subsets %>% filter(df == 6) %>% 
-  arrange(desc(adj.r.squared)) 
-
-model_df6_formula <- subsets %>% filter(df == 6) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character() 
-
-fit_df6 <- lm(model_df6_formula, data)
-
-summary(fit_df6)
-

### 2020-11-11 R/visualization.R

@@ -1,113 +1,0 @@
-library(tidyverse)
-# Visuals -------------------------------------------------------------
-theme_set(theme_light())
-
-data <- read_csv(here::here("data", "df.csv"))
-subsets <- read_csv(here::here("data", "subsets.csv"))
-names(data)
-
-corr_matrix <- data %>% 
-  select(-year, -country) %>% 
-  cor(.,  use = "complete.obs")
-
-View(corr_matrix)
-
-names(data)
-
-data %>% 
-  ggplot(mapping = aes(x = polrights_fh)) + 
-  geom_histogram(bins = 10)
-
-data %>% 
-  ggplot(mapping = aes(x = polrights_fh)) + 
-  geom_histogram()
-
-data %>% 
-  filter(year > 2015) %>% 
-  ggplot(mapping = aes(x = gini)) + 
-  geom_histogram()
-
-data %>% 
-  ggplot(aes(x = gini, y = polrights_fh)) +
-  geom_hex(binwidth = c(3, .6)) + 
-  scale_fill_gradient(low = "#7FFFD4", high = "#8B8378") + 
-  geom_smooth(method = "lm", se = TRUE, color = "red") +
-  geom_point(data = data %>% 
-               filter(country == "United States", 
-                         year == 2018), 
-      aes(x = gini, y = polrights_fh), size = 5, color = "red") +
-  labs(x = "GINI Coeffeceint", y = "Political Rights")
-
-data %>% 
-  ggplot(aes(x = gini, y = polrights_fh)) + 
-  geom_smooth(se = FALSE)
-
-r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
-
-
-subsets %>% 
-  ggplot(aes(x = df, y = adj.r.squared)) + 
-  geom_point() + 
-  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
-  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
-
-AIC <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
-
-subsets %>% 
-  ggplot(aes(x = df, y = AIC)) + 
-  geom_point() + 
-  geom_smooth(data = AIC, aes(df, AIC), se = FALSE, span = .5, color = "Green") + 
-  labs(title = "Best Subsets", x = "Parameters", y = "AIC")
-
[…]

### 2020-11-11 regression.R

@@ -1,70 +1,0 @@
-library(tidyverse)
-
-data <- readr::read_csv(here::here("data", "df.csv"))
-subsets <- readr::read_csv(here::here("data", "subsets.csv"))
-
-# First model -------------------------------------------------------------
-
-model_df5_formula <- subsets %>% filter(df == 5) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character()
-
-model_df5 <- lm(polrights_fh ~ corruption_perception_index_cpi + 
-            edu_exp_gdp_per_person + 
-            life_expectancy_years + 
-            military_spending_pct_of_gdp + 
-            murder_per_mil_people, data)
-
-subsets %>% filter(df == 9) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character()
-
-summary(model_df5)
-
-hist(resid(model_df5), breaks = 100)
-qqnorm(resid(model_df5))
-boxplot(resid(model_df5))
-
-plot(data$edu_exp_gdp_per_person, resid(model_df5))
-plot(data$corruption_perception_index_cpi, resid(model_df5))
-plot(data$polrights_fh, resid(model_df5))
-plot(data$electricity_use_per_person, resid(model_df5))
-plot(data$gini, resid(model_df5))
-plot(data$internet_users, resid(model_df5))
-plot(data$labour_force_participation_rate_percent, resid(model_df5))
-plot(data$life_expectancy_years, resid(model_df5))
-plot(data$military_spending_pct_of_gdp, resid(model_df5))
-plot(data$murder_per_mil_people, resid(model_df5))
-
-
-sort(resid(model_df5))
-data$resid <- resid(model_df5)
-
-# Second model ------------------------------------------------------------
-
-subsets %>% filter(df == 4) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  View()
-
-model_df4_formula <- subsets %>% filter(df == 4) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character() 
-
-fit_df4 <- lm(model_df4_formula, data)
-
-summary(fit_df4)
-
-# third -------------------------------------------------------------------
-
-subsets %>% filter(df == 6) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  View()
-
[…]

### 2020-11-11 isoslides.Rmd
.

---
title: "slides"
author: "Joe Despres"
date: "11/9/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
options(htmltools.dir.version = FALSE, echo = FALSE)
```

# Introduction
- political freedom as a function of 
- 
---
# Model
```{r}
equatiomatic::extract_eq(model = model_df5, intercept = "beta", terms_per_line = 1)
```

$$
\operatorname{polrights\_fh} = \beta_{0} + 
\beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +
\beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
$$

---
```{r echo=FALSE}
subsets %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(model, adj.r.squared) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 6))
```
---

# Model

# Findings

# Conclusions

### 2020-11-11 slides.Rmd
.

@@
 knitr::opts_chunk$set(echo = FALSE)
+xaringanExtra::use_slide_tone()
 ```
@@
 <font size="1">
-```{r results='asis',out.width='25%', fig.align='center'}
+```{r results='asis',out.width='25%', fig.align='center',}
 stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
@@
                      covariate.labels = c(),header = FALSE,
-single.row=FALSE,column.sep.width = "-15pt", column.separate = 1)
+single.row=FALSE,column.sep.width = "-15pt")
 ```

### 2020-11-11 R/cleaningscript.R
.

@@ -1,0 +1,41 @@
+library(tidyverse)
+
+# Read and Clean ----------------------------------------------------------
+files <- list.files(path = here::here("raw_data"), pattern = ".csv")
+
+cleaning <- function(df){
+  df <- pivot_longer(df, cols = -country, names_to = "year")
+}
+
+data <- files %>% 
+  map(function(x) read_csv(paste0("raw_data/", x))) %>% 
+  setNames(gsub("\\.csv$", "", files)) %>% 
+  map(cleaning) %>% 
+  bind_rows(.id = "id") %>% 
+  pivot_wider(names_from = id)
+
+# Filtering ---------------------------------------------------------------
+
+countries <- readRDS(here::here("data", "countries.RDS"))
+
+data <- data %>%
+  filter(year > 2000, year < 2019, country %in% countries) %>% 
+  group_by(country) %>%
+  mutate_at(vars(-country),list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
+# Iceland spent 0 so I needed to manually recode that
+  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
+  mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
+         # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
+         # these murder rates were not included in the gapminder but i didnt want to 
+         # lose 3 important countries in LA
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
+  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
+                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)
+
+# writing -----------------------------------------------------------------
+
+write_csv(data, here::here("data", "df.csv"))
+
+View(data)
+skimr::skim(ungroup(data))

### 2020-11-11 R/regression.R

@@ -1,0 +1,48 @@
+library(tidyverse)
+
+data <- readr::read_csv(here::here("data", "df.csv"))
+subsets <- readr::read_csv(here::here("data", "subsets.csv"))
+
+# First model -------------------------------------------------------------
+
+model_df5_formula <- subsets %>% filter(df == 5) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+model_df5 <- lm(polrights_fh ~ corruption_perception_index_cpi + 
+            edu_exp_gdp_per_person + 
+            life_expectancy_years + 
+            military_spending_pct_of_gdp + 
+            murder_per_mil_people, data)
+
+subsets %>% filter(df == 9) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+
+# Second model ------------------------------------------------------------
+
+subsets %>% filter(df == 4) %>% 
+  arrange(desc(adj.r.squared)) 
+
+model_df4_formula <- subsets %>% filter(df == 4) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character() 
+
+fit_df4 <- lm(model_df4_formula, data)
+
+summary(fit_df4)
+
+# third -------------------------------------------------------------------
+
+subsets %>% filter(df == 6) %>% 
+  arrange(desc(adj.r.squared)) 
+
+model_df6_formula <- subsets %>% filter(df == 6) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character() 
+
+fit_df6 <- lm(model_df6_formula, data)
+
+summary(fit_df6)
+

### 2020-11-11 R/visualization.R

@@ -1,0 +1,113 @@
+library(tidyverse)
+# Visuals -------------------------------------------------------------
+theme_set(theme_light())
+
+data <- read_csv(here::here("data", "df.csv"))
+subsets <- read_csv(here::here("data", "subsets.csv"))
+names(data)
+
+corr_matrix <- data %>% 
+  select(-year, -country) %>% 
+  cor(.,  use = "complete.obs")
+
+View(corr_matrix)
+
+names(data)
+
+data %>% 
+  ggplot(mapping = aes(x = polrights_fh)) + 
+  geom_histogram(bins = 10)
+
+data %>% 
+  ggplot(mapping = aes(x = polrights_fh)) + 
+  geom_histogram()
+
+data %>% 
+  filter(year > 2015) %>% 
+  ggplot(mapping = aes(x = gini)) + 
+  geom_histogram()
+
+data %>% 
+  ggplot(aes(x = gini, y = polrights_fh)) +
+  geom_hex(binwidth = c(3, .6)) + 
+  scale_fill_gradient(low = "#7FFFD4", high = "#8B8378") + 
+  geom_smooth(method = "lm", se = TRUE, color = "red") +
+  geom_point(data = data %>% 
+               filter(country == "United States", 
+                         year == 2018), 
+      aes(x = gini, y = polrights_fh), size = 5, color = "red") +
+  labs(x = "GINI Coeffeceint", y = "Political Rights")
+
+data %>% 
+  ggplot(aes(x = gini, y = polrights_fh)) + 
+  geom_smooth(se = FALSE)
+
+r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+
+
+subsets %>% 
+  ggplot(aes(x = df, y = adj.r.squared)) + 
+  geom_point() + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
+  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
+
+AIC <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+
+subsets %>% 
+  ggplot(aes(x = df, y = AIC)) + 
+  geom_point() + 
+  geom_smooth(data = AIC, aes(df, AIC), se = FALSE, span = .5, color = "Green") + 
+  labs(title = "Best Subsets", x = "Parameters", y = "AIC")
+
[…]

### 2020-11-11 slides.Rmd
updated slides

@@
   theme_light(base_size = 30)
-
 ```
@@
 $$
-\tiny
+\small
 \begin{align}
@@
 ---
-class: animated, fadeIn, center
+class: center
 $$
-\tiny
+\small
 \begin{align}
@@
 
-class: center, top
-<font size="1">
-```{r results='asis',out.width='25%', fig.align='center',}
+<font size="-10">
+```{r results='asis'}
 stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                      title = "Regression Results", 
-                     covariate.labels = c(),header = FALSE,
-single.row=FALSE,column.sep.width = "-15pt")
+                     covariate.labels = c(),
+                     header = FALSE,
+                     single.row = FALSE)
 ```

### 2020-11-11 slides.Rmd
resized table

@@
 
-<font size="-10">
+<font size="2">
 ```{r results='asis'}
@@
                      header = FALSE,
-                     single.row = FALSE)
+                     single.row = TRUE)
 ```

### 2020-11-11 slides.Rmd
table sized

@@
 knitr::opts_chunk$set(echo = FALSE)
-xaringanExtra::use_slide_tone()
+# xaringanExtra::use_slide_tone()
 ```

### 2020-11-11 slides.Rmd
added meeting additions

--- 2020-11-11 slides.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE) 
-xaringanExtra::use_slide_tone()
 ```
 
-# Outline
+# Research Question
 
@@
 
-* study political freedom as a function of social, economic, political factors
+* Observational study of political freedom as a function of social, economic, political factors.
+
+--
+* From Data provided by the Gapminder Foundation.
 
@@
 
-* From Data provided by the Gapminder Foundation.
+* filtered to only include OECD Countries from year 2000 to 2018 by necessity
 
@@
 
-# Data
-
-* filtered to only include OECD Countries from year 2000 to 2018
-
----
-
-# Define political freedom
-
---
-
-* Freedomhouse index
+# Political Freedom
 
@@
 ---
+
+# Data
+
+* covarites w/ exp
+
+---
+
+# Summary Stats
+
+---
+
+# Assumptions
+
+--
+* Finite mean and sd
+* independance
+* Linearity
+* Normaily
+* Homoskidasticity
+
+---
+
 # Best Subsets
@@
 ```
+
 ---
@@
 class: center
-### Best Subsets
-```{r, message=FALSE, warning=FALSE, fig.align='center', fig.width=12, fig.height=8}
+
+```{r, message=FALSE, warning=FALSE}
 r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
@@
 ---
+# Remedial measured
+
+* plot
+* 
+* vif
+car::vif(fit)
+
+* Brown Forsythe
+
+---
+# Conclusions
+
+---
+class: center, middle
+
+# Thanks You and We are Happy to Take Questions
+
+Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
+
+---
 
@@
 ```
-
----
-class: center, middle
-
-# Thanks You and We are Happy to Take Questions
-
-Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

### 2020-11-11 R/cleaningscript.R

@@ -25,11 +25,11 @@ data <- data %>%
 # Iceland spent 0 so I needed to manually recode that
   mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
   mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
          # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
          # these murder rates were not included in the gapminder but i didnt want to 
          # lose 3 important countries in LA
-         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
-         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
   relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
                                     military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)
 

### 2020-11-12 R/visualization.R
added speaking parts

@@ -97,16 +97,16 @@ hist(resid(model_df5), breaks = 100)
 qqnorm(resid(model_df5))
 boxplot(resid(model_df5))
 
-plot(data$edu_exp_gdp_per_person, resid(model_df5))
-plot(data$corruption_perception_index_cpi, resid(model_df5))
-plot(data$polrights_fh, resid(model_df5))
-plot(data$electricity_use_per_person, resid(model_df5))
-plot(data$gini, resid(model_df5))
-plot(data$internet_users, resid(model_df5))
-plot(data$labour_force_participation_rate_percent, resid(model_df5))
-plot(data$life_expectancy_years, resid(model_df5))
-plot(data$military_spending_pct_of_gdp, resid(model_df5))
-plot(data$murder_per_mil_people, resid(model_df5))
+plot(data$edu_exp_gdp_per_person, resid(fit))
+plot(data$corruption_perception_index_cpi, resid(fit))
+plot(data$polrights_fh, resid(fit))
+plot(data$electricity_use_per_person, resid(fit))
+plot(data$gini, resid(fit))
+plot(data$internet_users, resid(fit))
+plot(data$labour_force_participation_rate_percent, resid(fit))
+plot(data$life_expectancy_years, resid(fit))
+plot(data$military_spending_pct_of_gdp, resid(fit))
+plot(data$murder_per_mil_people, resid(fit))
 
 
 sort(resid(model_df5))

### 2020-11-12 slides.Rmd
updated slides

@@
 --
+
 * From Data provided by the Gapminder Foundation.
@@
 * summarsze fh index
+https://docs.google.com/spreadsheets/d/1AmmTVOAFMXZx3a-OYyKQaNM-dQJAvGCJOwfWzixo2Pk/edit#gid=266682269
 
@@
 
-# Best Subsets
+# Best Subsets by Adjusted R Squared
 ```{r message=FALSE}
@@
   arrange(desc(a_rsq)) %>% 
-DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 3), 
+              colnames = c("DF", "A_Rsq", "Model"))
+```
+
+---
+# Best Subsets by AIC
+```{r message=FALSE}
+subsets %>% 
+  group_by(df) %>% 
+  filter(AIC == min(AIC)) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  select(df, AIC, model) %>% 
+  arrange(AIC) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
+              colnames = c("DF", "AIC", "Model"))
 ```
@@
 
-class: center
+# Best Subsets by BIC
+```{r message=FALSE}
+subsets %>% 
+  group_by(df) %>% 
+  filter(BIC == min(BIC)) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  select(df, BIC, model) %>% 
+  arrange(BIC) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
+              colnames = c("DF", "BIC", "Model"))
+```
 
-```{r, message=FALSE, warning=FALSE}
+---
+
+class: center, middle
+
+# Best Subsets
+
+```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
 r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
@@
   scale_x_continuous(breaks = 1:9) + 
-  theme_light(base_size = 30)
+  theme_test(base_size = 30)
+```
+
+---
+class: center, middle
+
+# Best Subsets
+
+```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
+r <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+
+subsets %>% 
+  ggplot(aes(x = df, y = AIC)) + 
+  geom_point() + 
+  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "red") + 
+  labs(title = "", x = "Parameters", y = "AIC") + 
+  scale_x_continuous(breaks = 1:9) + 
+  theme_test(base_size = 30)
 ```
@@
 # Model
+
 ---
@@
 ```
+
+***
+```{r}
+broom::glance(model_df5) %>% 
+  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  kable()
+```
+
 ---
@@
   kable() %>% 
-  row_spec(4, bold = T, color = "white", background = "#D7261E")
+  row_spec(2, color = "white", background = "#D7261E")
+```
+
+***
+
+```{r}
+broom::glance(model_df5) %>% 
+  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  kable()
+```
+
+---
+class: center
+$$
+\small
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
+```{r}
+broom::tidy(model_df5) %>% 
+  kable() %>% 
+  row_spec(3, color = "white", background = "#D7261E")
+```
+
+***
+
+```{r}
+broom::glance(model_df5) %>% 
+  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  kable()
+```
+
+---
+class: center
+$$
+\small
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
+```{r}
+broom::tidy(model_df5) %>% 
+  kable() %>% 
+  row_spec(4, color = "white", background = "#D7261E")
+```
+
+***
+
+```{r}
+broom::glance(model_df5) %>% 
+  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  kable()
+```
+
+---
+
+class: center
+$$
+\small
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
+```{r}
+broom::tidy(model_df5) %>% 
+  kable() %>% 
+  row_spec(5, color = "white", background = "#D7261E")
+```
+
+***
+
+```{r}
+broom::glance(model_df5) %>% 
+  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  kable()
+```
+
+---
+class: center
+$$
+\small
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
+```{r}
+broom::tidy(model_df5) %>% 
+  kable() %>% 
+  row_spec(6, color = "white", background = "#D7261E")
+```
+
+***
+
+```{r}
+broom::glance(model_df5) %>% 
+  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  kable()
 ```

### 2020-11-12 slides.Rmd
worked on slides

@@
 
-* What factors are associated with an increase in political freedom?
+* This study will focus on political freedom around the world.
+
+--
+
+* We ask: What factors are associated with an increase in political freedom?
 
@@
 
-# Data
+# Covariates
 
-* covarites w/ exp
+- Country
+
+--
+
+- Year from 2000 to 2018
+
+--
+
+- Corruption Perception Index Ranging from 0 to 100 with 0 being the most corruption perception.
+
+--
+
+- Education Expenditure in GDP per Person
+
+--
+
+- Electricity use per person in Kilowatt Hours.
+
+--
+
+- Gini Coefficient. A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth.
+
+--
+
+- Percentage of population That use the Internet.
+
+--
+
+- Labor Force Participation.
+
+--
+
+- Life Expectancy
+
+--
+
+- Military Spending as a percentage of GDP
+
+--
+
+- Murders per million people.
 
@@
 
-# Summary Stats
+```{r message=FALSE}
+data %>% 
+  group_by(country) %>% 
+summarise(across(.cols = c(corruption_perception_index_cpi:murder_per_mil_people), mean)) %>% 
+  mutate_if(is.numeric, round, 2) %>% 
+  kable(
+    col.names = c("Country", "CPI", "Edu Exp", "Electric Use", "Gini", "Internet Users", "Labor Force", "Life Expectancy","Military Spending", "Murder Rate")) %>% 
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 6, fixed_thead = T)
+```
+
+---
+
+```{r}
+data %>% 
+  group_by(polrights_fh) %>% 
+  add_count(polrights_fh) %>% 
+  ggplot() + 
+  geom_bar(aes(x = polrights_fh)) + 
+  geom_text(aes(x = polrights_fh, y = n, label = n)) + 
+  scale_x_continuous(breaks = 1:7) + 
+  theme_test()
+```
 

### 2020-11-12 slides.Rmd
addded more stuff

@@
 
-* We ask: What factors are associated with an increase in political freedom?
+* We ask: What factors are associated with an increase in political freedom?.
 
@@
 
+- Freedomhouse quantifies Political Rights by 10 different indicators grouped in three subcategories.
+
 --
 
-* summarsze fh index
-https://docs.google.com/spreadsheets/d/1AmmTVOAFMXZx3a-OYyKQaNM-dQJAvGCJOwfWzixo2Pk/edit#gid=266682269
+1. Electoral Process
+
+--
+
+1. Political Participation and Pluralism
+
+--
+
+1. Discretionary Political rights.
 
@@
 $$
-
 ---
@@
 broom::tidy(model_df5) %>% 
-  kable()
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names = c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))
+
 ```
@@
 broom::tidy(model_df5) %>% 
-  kable() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))  %>% 
   row_spec(2, color = "white", background = "#D7261E")
@@
 broom::tidy(model_df5) %>% 
-  kable() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
   row_spec(3, color = "white", background = "#D7261E")
@@
 broom::tidy(model_df5) %>% 
-  kable() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
   row_spec(4, color = "white", background = "#D7261E")
@@
 broom::tidy(model_df5) %>% 
-  kable() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
   row_spec(5, color = "white", background = "#D7261E")
@@
 broom::tidy(model_df5) %>% 
-  kable() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
   row_spec(6, color = "white", background = "#D7261E")
@@
 ---
-# Remedial measured
+# Remedial measures
+```{r}
+model_df5 %>% 
+  broom::augment() %>% 
+  ggplot() + 
+  geom_histogram(aes(.resid), bins = 200) +
+  scale_x_continuous(limits = c(-4,4))
+
+```
+
+---
+# Remedial measures
+
+```{r}
+model_df5 %>% 
+  broom::augment() %>% 
+  mutate(yhat = predict(model_df5)) %>% 
+  ggplot() + 
+  geom_point(aes(x = yhat, y = .resid)) + 
+  geom_hline(yintercept = 0, color = "red") + 
+  scale_y_continuous(limits = c(-4,4))
+```
+
+---
 

### 2020-11-12 R/visualization.R

@@ -111,3 +111,15 @@ plot(data$murder_per_mil_people, resid(fit))
 
 sort(resid(model_df5))
 data$resid <- resid(model_df5)
+
+
+hsit <- model_df5 %>% 
+  broom::augment() %>% 
+  ggplot() + 
+  geom_histogram(aes(.resid), bins = 200) +
+  scale_x_continuous(limits = c(-4,4))
+
+model_df5 %>% 
+  broom::augment() %>% 
+  ggplot() + 
+  geom_qq(aes(.resid))

### 2020-11-13 slides.Rmd
plots and plots

@@
 source(here::here("R", "regression.R"))
-library(kableExtra)
+theme_set(theme_light(base_size = 30))
 options(htmltools.dir.version = FALSE, echo = FALSE)
-knitr::opts_chunk$set(echo = FALSE) 
+knitr::opts_chunk$set(echo = FALSE, fig.width=12, fig.height=8) 
 ```
@@
 ---
-
+class: center, middle
 ```{r}
@@
   ggplot() + 
-  geom_bar(aes(x = polrights_fh)) + 
-  geom_text(aes(x = polrights_fh, y = n, label = n)) + 
+  geom_bar(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "black") +
+
+  geom_text(aes(x = polrights_fh, y = n, label = n), vjust = -.75) + 
+  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
   scale_x_continuous(breaks = 1:7) + 
-  theme_test()
+  theme_test(base_size = 30) + 
+  theme(legend.position="none")
 ```
@@
   kable(col.names = c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) 
-
 ```
@@
 ---
+# F-Test on life expectancy
+
+---
+
+class: center, middle
 # Remedial measures
-```{r}
-model_df5 %>% 
-  broom::augment() %>% 
-  ggplot() + 
-  geom_histogram(aes(.resid), bins = 200) +
-  scale_x_continuous(limits = c(-4,4))
-
+```{r warning=FALSE}
+hist + qq  
 ```
@@
 ---
+class: center, middle
+# Remedial measures
+```{r message=FALSE}
+labeled_outliars + labeled_qq
+```
+
+---
+
 # Remedial measures
@@
   broom::augment() %>% 
-  mutate(yhat = predict(model_df5)) %>% 
+  mutate(yhat = predict(model_df5),
+         resid = resid(model_df5)) %>% 
   ggplot() + 
-  geom_point(aes(x = yhat, y = .resid)) + 
+  geom_point(aes(x = yhat, y = resid)) + 
   geom_hline(yintercept = 0, color = "red") + 
@@
 ---
+
+# Brown - Forthe
 

### 2020-11-13 R/regression.R

@@ -1,4 +1,6 @@
 library(tidyverse)
+library(kableExtra)
+library(patchwork)
 
 data <- readr::read_csv(here::here("data", "df.csv"))
 subsets <- readr::read_csv(here::here("data", "subsets.csv"))
@@ -46,3 +48,36 @@ fit_df6 <- lm(model_df6_formula, data)
 
 summary(fit_df6)
 
+
+
+# model stats -------------------------------------------------------------
+
+
+# remedial measures -------------------------------------------------------------------
+outliars <- model_df5 %>% 
+  broom::augment() %>% 
+  filter(.resid < -4*sd(.resid))
+
+hist <- model_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(.resid)) + 
+  geom_histogram(bins = 100, fill = "black") +
+  scale_x_continuous(limits = c(-4,4)) 
+hist
+qq <- model_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(sample = .resid)) + 
+  stat_qq() +
+  stat_qq_line() + 
+scale_x_continuous(limits = c(-4,4)) + 
+scale_y_continuous(limits = c(-4,4)) 
+
+
+
+labeled_outliars <- hist +
+  geom_point(outliars, mapping = aes(x = .resid, y = 1), color = "#D7261E", shape = 13, size = 10) + 
+  geom_label(outliars, mapping = aes(x = .resid, y = 10, label = "OUTLIARS"), color = "#D7261E", size = 3)
+
+labeled_qq <- qq + geom_point(outliars, mapping = aes(x = -3, y = -3.9), color = "#D7261E", shape = 0, size = 20) 
+
+labeled_qq 

### 2020-11-13 slides.Rmd
added textbook quote
added plots getting there

@@
 options(htmltools.dir.version = FALSE, echo = FALSE)
-knitr::opts_chunk$set(echo = FALSE, fig.width=12, fig.height=8) 
+knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 8) 
 ```
@@
 ---
+# OECD
+
+---
 class: inverse, middle, center
@@
 # Data
+
+---
+
+Inputing median
 
@@
 ---
-
+# needs work
 ```{r message=FALSE}
@@
   theme_test(base_size = 30) + 
-  theme(legend.position="none")
+  theme(legend.position = "none")
 ```
@@
 # Best Subsets by Adjusted R Squared
+?latex
 ```{r message=FALSE}
@@
 ```{r include=FALSE}
-equatiomatic::extract_eq(model = model_df5, intercept = "beta", terms_per_line = 1)
+equatiomatic::extract_eq(model = fit_df5, intercept = "beta", terms_per_line = 1)
 ```
@@
 ```{r}
-broom::tidy(model_df5) %>% 
+broom::tidy(fit_df5) %>% 
   mutate(p.value = as.character(p.value)) %>%
@@
 ```{r}
-broom::glance(model_df5) %>% 
+broom::glance(fit_df5) %>% 
   select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
@@
 ---
+
 class: center
@@
 
+---
+
+plots resids on cov
 ---
@@
 
+```{r}
+broom::tidy(fit_df5) %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
+        caption = "Included Outliers") 
+```
+
+***
+
+```{r}
+data %>% 
+  filter(polrights_fh >= 4) %>% 
+  lm(model_df5_formula, .) %>% 
+  broom::tidy() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
+        caption = "Removed Outliers") 
+```
+
+---
+
+```{r}
+broom::tidy(fit_df5) %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
+        caption = "Included Outliers") %>% 
+  row_spec(3, color = "white", background = "#D7261E")
+```
+
+***
+
+```{r}
+data %>% 
+  filter(polrights_fh >= 4) %>% 
+  lm(model_df5_formula, .) %>% 
+  broom::tidy() %>% 
+  mutate(p.value = as.character(p.value)) %>%
+  mutate_if(is.numeric, round, 3) %>% 
+  mutate(p.value = as.numeric(p.value)) %>% 
+  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
+        caption = "Removed Outliers") %>% 
+  row_spec(3, color = "white", background = "#D7261E")
+```
+
+---
+
+# Discussion of outliers
+
+- We identified these outliers.
+- confirmed they are not errors. 
+- decided to keep them because They are indicating a substancial loss in political freedom which falls outside of the scope of the model. However, is important for our reserach Q.
+***
+> A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance.
+-Chapter 3 p.108
+
+---
+
 # Remedial measures
@@
 ```{r}
-model_df5 %>% 
+fit_df5 %>% 
   broom::augment() %>% 
-  mutate(yhat = predict(model_df5),
-         resid = resid(model_df5)) %>% 
+  mutate(yhat = predict(fit_df5),
+         resid = resid(fit_df5)) %>% 
   ggplot() + 
@@
 
+```{r}
+car::vif(fit_df5)
+```
+* vif
+
+---
+
 # Brown - Forthe
-
-* plot
-* 
-* vif
-car::vif(fit)
 
@@
 # Conclusions
+
+1. we think this
+1. because
 
@@
 ```{r results='asis'}
-stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
+stargazer::stargazer(fit_df6, fit_df5, fit_df4, fit_df3, type = "html", 
                      title = "Regression Results", 

### 2020-11-13 R/regression.R

@@ -11,21 +11,9 @@ model_df5_formula <- subsets %>% filter(df == 5) %>%
   arrange(desc(adj.r.squared)) %>% 
   select(model) %>% head(1) %>% as.character()
 
-model_df5 <- lm(polrights_fh ~ corruption_perception_index_cpi + 
-            edu_exp_gdp_per_person + 
-            life_expectancy_years + 
-            military_spending_pct_of_gdp + 
-            murder_per_mil_people, data)
-
-subsets %>% filter(df == 9) %>% 
-  arrange(desc(adj.r.squared)) %>% 
-  select(model) %>% head(1) %>% as.character()
-
+fit_df5 <- lm(model_df5_formula, data)
 
 # Second model ------------------------------------------------------------
-
-subsets %>% filter(df == 4) %>% 
-  arrange(desc(adj.r.squared)) 
 
 model_df4_formula <- subsets %>% filter(df == 4) %>% 
   arrange(desc(adj.r.squared)) %>% 
@@ -33,12 +21,13 @@ model_df4_formula <- subsets %>% filter(df == 4) %>%
 
 fit_df4 <- lm(model_df4_formula, data)
 
-summary(fit_df4)
+model_df3_formula <- subsets %>% filter(df == 3) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character() 
+
+fit_df3 <- lm(model_df3_formula, data)
 
 # third -------------------------------------------------------------------
-
-subsets %>% filter(df == 6) %>% 
-  arrange(desc(adj.r.squared)) 
 
 model_df6_formula <- subsets %>% filter(df == 6) %>% 
   arrange(desc(adj.r.squared)) %>% 
@@ -46,25 +35,21 @@ model_df6_formula <- subsets %>% filter(df == 6) %>%
 
 fit_df6 <- lm(model_df6_formula, data)
 
-summary(fit_df6)
-
-
-
-# model stats -------------------------------------------------------------
-
-
 # remedial measures -------------------------------------------------------------------
-outliars <- model_df5 %>% 
+
+outliars <- fit_df5 %>% 
   broom::augment() %>% 
   filter(.resid < -4*sd(.resid))
 
-hist <- model_df5 %>% 
+hist <- fit_df5 %>% 
   broom::augment() %>% 
   ggplot(aes(.resid)) + 
[…]

### 2020-11-14 slides.Rmd
slides rough

@@
 ---
+class: center
 # OECD
+
+![](OECD.jpeg)
 
@@
 # Data
-
----
-
-Inputing median
 
@@
 ---
-# needs work
+
+class: center
+# Inputing Median
+
+```{r}
+set.seed(69)
+t1 <- cbind(1:5, round(runif(5, 200, 300), 2))
+t1[3,2] <- NA
+t2 <- t1
+colnames(t1) <- c("Obs. Number", "Data Point")
+t2[3,2] <- median(t1[,2], na.rm = TRUE)
+colnames(t2) <- c("Obs. Number", "Data Point")
+knitr::kable(list(t1, t2), caption = "Illustrated Example")
+```
+
+---
+
 ```{r message=FALSE}
@@
   theme_test(base_size = 30) + 
-  theme(legend.position = "none")
+  theme(legend.position = "none") + 
+  labs(y = "Number", x = "Political Freedom", title = "Distribution of Political Freedom Within the OECD")
 ```
@@
 # Best Subsets by Adjusted R Squared
-?latex
 ```{r message=FALSE}
@@
 ---
-# F-Test on life expectancy
-
----
-
-plots resids on cov
----
 
 class: center, middle
-# Remedial measures
+
 ```{r warning=FALSE}
@@
 class: center, middle
-# Remedial measures
+
 ```{r message=FALSE}
 labeled_outliars + labeled_qq
+```
+---
+
+```{r}
+fit_df5 %>% 
+  broom::augment() %>% 
+  mutate(yhat = predict(fit_df5),
+         resid = resid(fit_df5)) %>% 
+  ggplot() + 
+  geom_point(aes(x = yhat, y = resid)) + 
+  geom_hline(yintercept = 0, color = "red") + 
+  scale_y_continuous(limits = c(-4,4)) + 
+  labs(y = "Residual", x = "Predicted Value")
 ```
@@
 
-# Remedial measures
+# Brown Forsythe Test
 
 ```{r}
-fit_df5 %>% 
-  broom::augment() %>% 
-  mutate(yhat = predict(fit_df5),
-         resid = resid(fit_df5)) %>% 
-  ggplot() + 
-  geom_point(aes(x = yhat, y = resid)) + 
-  geom_hline(yintercept = 0, color = "red") + 
-  scale_y_continuous(limits = c(-4,4))
+df <- data %>% 
+  mutate(predict = predict(fit_df5),
+               e = resid(fit_df5)) %>% 
+  arrange(predict)
+
+lower <- df %>% filter(predict < quantile(predict, .5)) %>% arrange(predict)
+upper <- df %>% filter(predict >= quantile(predict, .5)) %>% arrange(desc(predict))
+
+d1 <- mean(abs(lower$e - median(lower$e)))
+d2 <- mean(abs(upper$e - median(upper$e)))
+
+s <- sum((abs(lower$e - median(lower$e)) - d1)^2) +
+     sum((abs(upper$e - median(upper$e)) - d2)^2)
+sq <- s / (nrow(df) - 2)
+s <- sqrt(sq)
+sq <- sqrt((1/nrow(lower)) + (1/nrow(upper)))
+tstar <- (d1 - d2) / (s*sq)
+# qt(p = .975, 79)
+# c(d1, d2, s, tstar)
 ```
+
+$$ 
+\begin{align}
+d_{{i1}}=\left\vert e_{{i1}}-{\tilde  {e}}_{1}\right\vert  \quad  \quad  \quad  \quad d_{{i2}}=\left\vert e_{{i2}}-{\tilde  {e}}_{2}\right\vert \\
+\end{align}
+$$
+***
+
+$$ 
+\begin{align}
+\bar{d_{{1}}}= 0.489 \quad  \quad \quad  \quad  \quad \bar{d_{{2}}}=0.177 \\
+\end{align}
+$$
+***
+
+$$
+\begin{align}
+{\displaystyle t^{*}_{BF} ={\frac {{\bar {d}}_{1}-{\bar {d}}_{2}}{s^2 {\sqrt {{\frac {1}{n_{1}}}+{\frac {1}{n_{2}}}}}}}}
+\end{align}
+$$
+***
+
+$$
+\begin{align}
+{\displaystyle t^{*}_{BF} ={\frac {0.489 -{0.177}}{0.176 {\sqrt {{\frac {1}{324}}+{\frac {1}{324}}}}}}} = 9.49
+\end{align}
+$$
+
+$$
+\begin{align}
+t(.975; 643) = 1.963
+\end{align}
+$$
+- Conclude Error variance is not constant
 
@@
 
+# Brown Forsythe Test Dropping Outliars
+
 ```{r}
-car::vif(fit_df5)
+df <- data %>% 
+  mutate(predict = predict(fit_df5),
+               e = resid(fit_df5)) %>% 
+  filter(polrights_fh >= 4) %>% 
+  arrange(predict)
+
+lower <- df %>% filter(predict < quantile(predict, .5)) %>% arrange(predict)
+upper <- df %>% filter(predict >= quantile(predict, .5)) %>% arrange(desc(predict))
+
+d1 <- mean(abs(lower$e - median(lower$e)))
+d2 <- mean(abs(upper$e - median(upper$e)))
+
+s <- sum((abs(lower$e - median(lower$e)) - d1)^2) +
+     sum((abs(upper$e - median(upper$e)) - d2)^2)
+sq <- s / (nrow(df) - 2)
+s <- sqrt(sq)
+sq <- sqrt((1/nrow(lower)) + (1/nrow(upper)))
+tstar <- (d1 - d2) / (s*sq)
+# qt(p = .975, 79)
+# c(d1, d2, s, tstar)
 ```
-* vif
 
----
+$$ 
+\begin{align}
+d_{{i1}}=\left\vert e_{{i1}}-{\tilde  {e}}_{1}\right\vert  \quad  \quad  \quad  \quad d_{{i2}}=\left\vert e_{{i2}}-{\tilde  {e}}_{2}\right\vert \\
+\end{align}
+$$
+***
 
-# Brown - Forthe
+$$ 
+\begin{align}
+\bar{d_{{1}}}= 0.447 \quad  \quad \quad  \quad  \quad \bar{d_{{2}}}=0.176 \\
+\end{align}
+$$
+***
 
-* Brown Forsythe
+$$
+\begin{align}
+{\displaystyle t^{*}_{BF} ={\frac {{\bar {d}}_{1}-{\bar {d}}_{2}}{s^2 {\sqrt {{\frac {1}{n_{1}}}+{\frac {1}{n_{2}}}}}}}}
+\end{align}
+$$
+***
+
+$$
+\begin{align}
+{\displaystyle t^{*}_{BF} ={\frac {0.447 -{0.176}}{0.176 {\sqrt {{\frac {1}{322}}+{\frac {1}{322}}}}}}} = 10.274
+\end{align}
+$$
+
+$$
+\begin{align}
+t(.975; 639) = 1.963
+\end{align}
+$$
+- Conclude again Error variance is not constant even when outliars are removed
 

### 2020-11-14 R/regression.R

@@ -45,7 +45,7 @@ hist <- fit_df5 %>%
   broom::augment() %>% 
   ggplot(aes(.resid)) + 
   geom_histogram(bins = 100, fill = "black") +
-  scale_x_continuous(limits = c(-4,4)) 
+  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", "Histogram")
 
 hist
 
@@ -55,7 +55,7 @@ qq <- fit_df5 %>%
   stat_qq() +
   stat_qq_line() + 
 scale_x_continuous(limits = c(-4,4)) + 
-scale_y_continuous(limits = c(-4,4)) 
+scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected")
 
 labeled_outliars <- hist +
   geom_point(outliars, mapping = aes(x = .resid, y = 1), color = "#D7261E", shape = 13, size = 10) + 

### 2020-11-15 slides.Rmd
added median
added anim

@@
 ```{r setup, include=FALSE}
-source(here::here("R", "regression.R"))
+library(tidyverse)
+library(kableExtra)
+library(patchwork)
+
 theme_set(theme_light(base_size = 30))
@@
 knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 8)
+
+data <- readr::read_csv(here::here("data", "df.csv"))
+subsets <- readr::read_csv(here::here("data", "subsets.csv"))
 ```
@@
 
-- Country
-
---
-
-- Year from 2000 to 2018
-
---
-
 - Corruption Perception Index Ranging from 0 to 100 with 0 being the most corruption perception.
@@
 
+$$Median = 264.98$$
+---
+class: inverse, middle, center
+
+# Summary Statistics
 ---
@@
 ```{r}
+lab <- data %>% 
+  group_by(polrights_fh) %>% 
+  add_count(polrights_fh) %>% 
+  distinct(n)
+
 data %>% 
@@
   add_count(polrights_fh) %>% 
-  ggplot() + 
-  geom_bar(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "black") +
-
-  geom_text(aes(x = polrights_fh, y = n, label = n), vjust = -.75) + 
+  ggplot(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "black") + 
+  geom_bar() + 
+  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n), vjust = -.75) + 
   viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
@@
 class: center, middle
+```{r}
+model_df5_formula <- subsets %>% filter(df == 5) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df5 <- lm(model_df5_formula, data)
+```
 
@@
 ```{r warning=FALSE}
+
+hist <- fit_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(.resid)) + 
+  geom_histogram(bins = 100, fill = "black") +
+  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")
+
+qq <- fit_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(sample = .resid)) + 
+  stat_qq() +
+  stat_qq_line() + 
+scale_x_continuous(limits = c(-4,4)) + 
+scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected")
+```
+
+```{r}
 hist + qq
@@
 class: center, middle
+
+```{r}
+outliars <- fit_df5 %>% 
+  broom::augment() %>% 
+  filter(.resid < -4*sd(.resid))
+
+labeled_outliars <- hist +
+  geom_point(outliars, mapping = aes(x = .resid, y = 1), color = "#D7261E", shape = 13, size = 10) + 
+  geom_label(outliars, mapping = aes(x = -3.3, y = 5, label = "OUTLIARS"), color = "#D7261E", size = 3)
+
+labeled_qq <- qq + geom_point(outliars, mapping = aes(x = -3, y = -3.9), color = "#D7261E", shape = 0, size = 15) +
+                   geom_point(outliars, mapping = aes(x = -2.6, y = -2.7), color = "#D7261E", shape = 0, size = 15) +
+                   geom_label(outliars, mapping = aes(x = -3, y = -3.5, label = "OUTLIARS"), color = "#D7261E", size = 3)
+
+```
 
@@
   row_spec(3, color = "white", background = "#D7261E")
+```
+
+---
+```{r, animation.hook="gifski", interval = .1}
+for(i in 1:(nrow(data))/5){
+plot(data$electricity_use_per_person[1:i*5], resid(fit_df5)[1:i*5], xlim=c(0,6000), ylim = c(-4, 1.25))
+}
+
 ```
@@
 
+```{r}
+model_df6_formula <- subsets %>% filter(df == 6) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df6 <- lm(model_df6_formula, data)
+
+model_df4_formula <- subsets %>% filter(df == 4) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df4 <- lm(model_df4_formula, data)
+
+model_df3_formula <- subsets %>% filter(df == 3) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df3 <- lm(model_df3_formula, data)
+
+```
+
 <font size="2">

### 2020-11-15 R/visualization.R

@@ -98,8 +98,11 @@ qqnorm(resid(model_df5))
 boxplot(resid(model_df5))
 
 plot(data$edu_exp_gdp_per_person, resid(fit))
+
 plot(data$corruption_perception_index_cpi, resid(fit))
+
 plot(data$polrights_fh, resid(fit))
+
 plot(data$electricity_use_per_person, resid(fit))
 plot(data$gini, resid(fit))
 plot(data$internet_users, resid(fit))
@@ -108,9 +111,6 @@ plot(data$life_expectancy_years, resid(fit))
 plot(data$military_spending_pct_of_gdp, resid(fit))
 plot(data$murder_per_mil_people, resid(fit))
 
-
-sort(resid(model_df5))
-data$resid <- resid(model_df5)
 
 
 hsit <- model_df5 %>% 

### 2020-11-15 slides.Rmd
added theme

@@
 library(patchwork)
+library(xaringanthemer)
 
+style_mono_accent_inverse(base_color = "#3C989E")
 theme_set(theme_light(base_size = 30))
@@
 subsets <- readr::read_csv(here::here("data", "subsets.csv"))
+```
+
+```{r xaringan-themer, include=FALSE, warning=FALSE}
+
 ```
@@
 ```{r}
-set.seed(69)
 t1 <- cbind(1:5, round(runif(5, 200, 300), 2))

### 2020-11-15 themed_slides.Rmd
added theme

--- 2020-11-15 slides.Rmd
@@
     lib_dir: libs
+    css: xaringan-themer.css
     nature:
@@
 subsets <- readr::read_csv(here::here("data", "subsets.csv"))
-```
-
-```{r xaringan-themer, include=FALSE, warning=FALSE}
-
 ```
@@
 ---
-class: center
+
+class: center, white
+
 # OECD
@@
 ```{r}
+set.seed(69)
 t1 <- cbind(1:5, round(runif(5, 200, 300), 2))
@@
   add_count(polrights_fh) %>% 
-  ggplot(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "black") + 
+  ggplot(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "#3C989E") + 
   geom_bar() + 
-  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n), vjust = -.75) + 
+  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n), color = "#3C989E", size = 8) + 
   viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
@@
   theme_test(base_size = 30) + 
+  theme_xaringan() + 
   theme(legend.position = "none") + 
@@
   geom_point() + 
-  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "red") + 
   labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
   scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = 30)
+  theme_test(base_size = 30) + 
+  theme_xaringan() 
 ```
@@
   scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = 30)
+  theme_test(base_size = 30) + 
+  theme_xaringan() 
 ```
@@
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))  %>% 
-  row_spec(2, color = "white", background = "#D7261E")
+  row_spec(2, color = "white", background = "#3C989E")
 ```
@@
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(3, color = "white", background = "#D7261E")
+  row_spec(3, color = "white", background = "#3C989E")
 ```
@@
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(4, color = "white", background = "#D7261E")
+  row_spec(4, color = "white", background = "#3C989E")
 ```
@@
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(5, color = "white", background = "#D7261E")
+  row_spec(5, color = "white", background = "#3C989E")
 ```
@@
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(6, color = "white", background = "#D7261E")
+  row_spec(6, color = "white", background = "#3C989E")
 ```
@@
   ggplot(aes(.resid)) + 
-  geom_histogram(bins = 100, fill = "black") +
-  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")
+  geom_histogram(bins = 100) +
+  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram") + theme_xaringan()
 
@@
 scale_x_continuous(limits = c(-4,4)) + 
-scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected")
+scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected") + theme_xaringan() 
 ```
@@
   scale_y_continuous(limits = c(-4,4)) + 
+  theme_xaringan() +
   labs(y = "Residual", x = "Predicted Value")
@@
         caption = "Included Outliers") %>% 
-  row_spec(3, color = "white", background = "#D7261E")
+  row_spec(3, color = "white", background = "#3C989E")
 ```
@@
         caption = "Removed Outliers") %>% 
-  row_spec(3, color = "white", background = "#D7261E")
-```
-
----
-```{r, animation.hook="gifski", interval = .1}
-for(i in 1:(nrow(data))/5){
-plot(data$electricity_use_per_person[1:i*5], resid(fit_df5)[1:i*5], xlim=c(0,6000), ylim = c(-4, 1.25))
-}
-
+  row_spec(3, color = "white", background = "#3C989E")
 ```
@@
 ***
-> A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance.
+> "A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance".
 -Chapter 3 p.108
@@
 ---
-
+class: center
 # Brown Forsythe Test

### 2020-11-15 R/cleaningscript.R

@@ -16,7 +16,8 @@ data <- files %>%
 
 # Filtering ---------------------------------------------------------------
 
-countries <- readRDS(here::here("data", "countries.RDS"))
+countries <- readRDS(here::here("data", "countries.RDS"))[15:51]
+
 
 data <- data %>%
   filter(year > 2000, year < 2019, country %in% countries) %>% 

### 2020-11-15 themed_slides.Rmd
added theme and fixed tables

@@
 
+class: middle, center
+
+```{r message=FALSE}
+data %>% 
+  group_by(country) %>% 
+summarise(across(.cols = c(corruption_perception_index_cpi:murder_per_mil_people), mean)) %>% 
+select(country, internet_users:murder_per_mil_people) %>% 
+    mutate_if(is.numeric, round, 2) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), caption = "Mean", 
+            colnames =  c("Country","Internet Users", "Labor Force", "Life Expectancy", "Military Spending", "Murder Rate") )
+```
+
+---
+class: middle, center
+
 ```{r message=FALSE}
@@
   mutate_if(is.numeric, round, 2) %>% 
-  kable(
-    col.names = c("Country", "CPI", "Edu Exp", "Electric Use", "Gini", "Internet Users", "Labor Force", "Life Expectancy","Military Spending", "Murder Rate")) %>% 
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 6, fixed_thead = T)
+select(country, corruption_perception_index_cpi:gini) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), caption = "Mean", 
+              colnames = c("Country", "CPI", "Edu Exp", "Electric Use", "Gini"))
 ```
@@
 ---
+
 class: center, middle
@@
   geom_bar() + 
-  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n), color = "#3C989E", size = 8) + 
+  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n),
+            color = "#3C989E", size = 8, vjust = -.10) + 
   viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
@@
 ```{r}
-outliars <- fit_df5 %>% 
+outliers <- fit_df5 %>% 
   broom::augment() %>% 
@@
 
-labeled_outliars <- hist +
-  geom_point(outliars, mapping = aes(x = .resid, y = 1), color = "#D7261E", shape = 13, size = 10) + 
-  geom_label(outliars, mapping = aes(x = -3.3, y = 5, label = "OUTLIARS"), color = "#D7261E", size = 3)
+labeled_outliers <- hist +
+  geom_point(outliers, mapping = aes(x = .resid, y = 1), color = "#D7261E", shape = 13, size = 10) + 
+  geom_label(outliers, mapping = aes(x = -3.3, y = 5, label = "OUTLIERS"), 
+             color = "#D7261E", size = 5)
 
-labeled_qq <- qq + geom_point(outliars, mapping = aes(x = -3, y = -3.9), color = "#D7261E", shape = 0, size = 15) +
-                   geom_point(outliars, mapping = aes(x = -2.6, y = -2.7), color = "#D7261E", shape = 0, size = 15) +
-                   geom_label(outliars, mapping = aes(x = -3, y = -3.5, label = "OUTLIARS"), color = "#D7261E", size = 3)
+labeled_qq <- qq + geom_point(outliers, mapping = aes(x = -3, y = -3.9),
+                              color = "#D7261E", shape = 0, size = 15) +
+                   geom_point(outliers, mapping = aes(x = -2.6, y = -2.7), color = "#D7261E", shape = 0, size = 15) +
+                   geom_label(outliers, mapping = aes(x = -3, y = -3.5, label = "OUTLIERS"), color = "#D7261E", size = 5)
 
@@
 ```{r message=FALSE}
-labeled_outliars + labeled_qq
+labeled_outliers + labeled_qq
 ```
@@
 ---
-class: center
-# Brown Forsythe Test
+
+#### Brown Forsythe Test Dropping outliers
 
@@
 
-# Brown Forsythe Test Dropping Outliars
+#### Brown Forsythe Test Dropping outliers
 
@@
 $$
-- Conclude again Error variance is not constant even when outliars are removed
+- Conclude again Error variance is not constant even when outliers are removed
 

### 2020-11-15 slides.Rmd
revert

--- 2020-11-14 slides.Rmd
@@
 ```{r setup, include=FALSE}
-source(here::here("R", "regression.R"))
+library(tidyverse)
+library(kableExtra)
+library(patchwork)
+library(xaringanthemer)
+
+style_mono_accent_inverse(base_color = "#3C989E")
 theme_set(theme_light(base_size = 30))
@@
 # Covariates
-
-- Country
-
---
-
-- Year from 2000 to 2018
-
---
 
@@
 
+$$Median = 264.98$$
 ---
+class: inverse, middle, center
+
+# Summary Statistics
+---
+
+class: middle, center
+
+```{r message=FALSE}
+data %>% 
+  group_by(country) %>% 
+summarise(across(.cols = c(corruption_perception_index_cpi:murder_per_mil_people), mean)) %>% 
+select(country, internet_users:murder_per_mil_people) %>% 
+    mutate_if(is.numeric, round, 2) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), caption = "Mean", 
+            colnames =  c("Country","Internet Users", "Labor Force", "Life Expectancy", "Military Spending", "Murder Rate") )
+```
+
+---
+class: middle, center
 
@@
 ---
+
 class: center, middle
 ```{r}
+lab <- data %>% 
+  group_by(polrights_fh) %>% 
+  add_count(polrights_fh) %>% 
+  distinct(n)
+
 data %>% 
@@
   add_count(polrights_fh) %>% 
-  ggplot() + 
-  geom_bar(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "black") +
-
-  geom_text(aes(x = polrights_fh, y = n, label = n), vjust = -.75) + 
+  ggplot(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "#3C989E") + 
+  geom_bar() + 
+  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n),
+            color = "#3C989E", size = 8, vjust = -.10) + 
   viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
@@
   theme_test(base_size = 30) + 
+#  #  theme_xaringan() +  + 
   theme(legend.position = "none") + 
-  labs(y = "Number", x = "Political Freedom", title = "Distribution of Political Freedom Within the OECD")
+  labs(y = "Number", x = "Political Freedom", title = "Distribution of Political Freedom")
 ```
@@
 * Finite mean and sd
-* independance
+* independence
 * Linearity
-* Normaily
+* Normality
 * Homoskidasticity
@@
   select(df, a_rsq, model) %>% 
+  mutate(
+    model = str_replace_all(model, "_", " "),
+    model = str_replace(model, "~", "=")) %>% 
   arrange(desc(a_rsq)) %>% 
@@
   select(df, AIC, model) %>% 
+    mutate(
+    model = str_replace_all(model, "_", " "),
+    model = str_replace(model, "~", "=")) %>% 
   arrange(AIC) %>% 
@@
   select(df, BIC, model) %>% 
+    mutate(
+    model = str_replace_all(model, "_", " "),
+    model = str_replace(model, "~", "=")) %>% 
   arrange(BIC) %>% 
@@
   geom_point() + 
-  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "red") + 
   labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
@@
   theme_test(base_size = 30) 
+  #  #  theme_xaringan() +  +  
 ```
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names = c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) 
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))  %>%
-  row_spec(2, color = "white", background = "#D7261E")
+  row_spec(2, color = "white", background = "#3C989E")
 ```
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(3, color = "white", background = "#D7261E")
+  row_spec(3, color = "white", background = "#3C989E")
 ```
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(4, color = "white", background = "#D7261E")
+  row_spec(4, color = "white", background = "#3C989E")
 ```
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(5, color = "white", background = "#D7261E")
+  row_spec(5, color = "white", background = "#3C989E")
 ```
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
-  row_spec(6, color = "white", background = "#D7261E")
+  row_spec(6, color = "white", background = "#3C989E")
 ```
@@
 ```{r warning=FALSE}
+
+hist <- fit_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(.resid)) + 
+  geom_histogram(bins = 100) +
+  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")  #  #  theme_xaringan() +  +
+
+qq <- fit_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(sample = .resid)) + 
+  stat_qq() +
+  stat_qq_line() + 
+scale_x_continuous(limits = c(-4,4)) + 
+scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected") #  theme_xaringan() +  
+```
+
+```{r}
 hist + qq
@@
 
+```{r}
+outliers <- fit_df5 %>% 
+  broom::augment() %>% 
+  filter(.resid < -4*sd(.resid))
+
+labeled_outliers <- hist +
+  geom_point(outliers, mapping = aes(x = .resid, y = 1), color = "#D7261E", shape = 13, size = 10) + 
+  geom_label(outliers, mapping = aes(x = -3.3, y = 5, label = "OUTLIERS"), 
+             color = "#D7261E", size = 5)
+
+labeled_qq <- qq + geom_point(outliers, mapping = aes(x = -3, y = -3.9),
+                              color = "#D7261E", shape = 0, size = 15) +
+                   geom_point(outliers, mapping = aes(x = -2.6, y = -2.7), color = "#D7261E", shape = 0, size = 15) +
+                   geom_label(outliers, mapping = aes(x = -3, y = -3.5, label = "OUTLIERS"), color = "#D7261E", size = 5)
+
+```
+
 ```{r message=FALSE}
-labeled_outliars + labeled_qq
+labeled_outliers + labeled_qq
 ```
@@
   scale_y_continuous(limits = c(-4,4)) + 
+  #  theme_xaringan() +  +
   labs(y = "Residual", x = "Predicted Value")
@@
         caption = "Removed Outliers") %>% 
-  row_spec(3, color = "white", background = "#D7261E")
+  row_spec(3, color = "white", background = "#3C989E")
 ```
@@
 
-# Brown Forsythe Test
+#### Brown Forsythe Test Dropping outliers
 

### 2020-11-15 themed_slides.Rmd
revert

@@
 library(patchwork)
-library(xaringanthemer)
+# library(xaringanthemer)
+# 
+# style_mono_accent_inverse(base_color = "#9596a3", 
+#                           background_color = "#9596a3",
+#                           text_color = "#000000", 
+#                           header_color  ="#000000" )
 
-style_mono_accent_inverse(base_color = "#3C989E")
 theme_set(theme_light(base_size = 30))
@@
   theme_test(base_size = 30) + 
-  theme_xaringan() + 
+#  #  theme_xaringan() +  + 
   theme(legend.position = "none") + 
@@
   scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = 30) + 
-  theme_xaringan() 
+  theme_test(base_size = 30) 
+  #  #  theme_xaringan() +  +  
 ```
@@
   geom_histogram(bins = 100) +
-  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram") + theme_xaringan()
+  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")  #  #  theme_xaringan() +  +
 
@@
 scale_x_continuous(limits = c(-4,4)) + 
-scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected") + theme_xaringan() 
+scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected") #  theme_xaringan() +  
 ```
@@
   scale_y_continuous(limits = c(-4,4)) + 
-  theme_xaringan() +
+  #  theme_xaringan() +  +
   labs(y = "Residual", x = "Predicted Value")

### 2020-11-16 slides.Rmd
added corrections

@@
 
-* From Data provided by the Gapminder Foundation.
+* From data provided by the Gapminder Foundation.
 
@@
 
-* filtered to only include OECD Countries from year 2000 to 2018 by necessity
+* Filtered to only include OECD Countries from year 2000 to 2018 by necessity.
 
@@
 
-1. Electoral Process
+### 1. Electoral Process
 
@@
 
-1. Political Participation and Pluralism
+### 2. Political Participation and Pluralism
 
@@
 
-1. Discretionary Political rights.
+### 3. Discretionary Political Rights
 
@@
 
-- Corruption Perception Index Ranging from 0 to 100 with 0 being the most corruption perception.
+- Corruption Perception Index ranges from 0 to 100 with 0 being the highest perception of corruption
 
@@
 
-- Electricity use per person in Kilowatt Hours.
+- Electricity use per person in Kilowatt Hours
 
@@
 
-- Gini Coefficient. A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth.
+- Gini Coefficient: A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth
 
@@
 
-- Percentage of population That use the Internet.
+- Percentage of population That use the Internet
 
@@
 
-- Labor Force Participation.
+- Labor Force Participation
 
@@
 
-- Murders per million people.
+- Murders per million people
 
+---
+class: center
+
+### Illustriated example Inputing Median
+
+```{r}
+set.seed(69)
+t1 <- cbind(1:5, round(runif(5, 200, 300), 2))
+t1[3,2] <- NA
+t2 <- t1
+colnames(t1) <- c("Obs. Number", "Data Point")
+
+colnames(t2) <- c("Obs. Number", "Data Point")
+
+kable(t1, align = "c") %>%
+  kable_styling(position = "float_left", full_width = F, html_font = "Cambria") %>% 
+  row_spec(3, color = "white", background = "#3C989E")
+
+kable(t2, align = "c") %>%
+  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria")
+```
+
+---
+class: center
+
+### Illustriated example Inputing Median
+
+```{r}
+set.seed(69)
+t1 <- cbind(1:5, round(runif(5, 200, 300), 2))
+t1[3,2] <- NA
+t2 <- t1
+colnames(t1) <- c("Obs. Number", "Data Point")
+
+colnames(t2) <- c("Obs. Number", "Data Point")
+
+kable(t1, align = "c") %>%
+  kable_styling(position = "float_left", full_width = F, html_font = "Cambria") %>% 
+  row_spec(3, color = "white", background = "#3C989E")
+
+kable(t2, align = "c") %>%
+  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria")
+```
+
+$$Median = 264.98$$
 ---
@@
 class: center
-# Inputing Median
+
+### Illustriated example Inputing Median
 
@@
 colnames(t2) <- c("Obs. Number", "Data Point")
-knitr::kable(list(t1, t2), caption = "Illustrated Example")
+
+kable(t1, align = "c") %>%
+  kable_styling(position = "float_left", full_width = F, html_font = "Cambria") %>% 
+  row_spec(3, color = "white", background = "#3C989E")
+
+kable(t2, align = "c") %>%
+  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria") %>% 
+  row_spec(3, color = "white", background = "#3C989E")
 ```
@@
   theme_test(base_size = 30) + 
-#  #  theme_xaringan() +  + 
+#    + 
   theme(legend.position = "none") + 
@@
 --
-* Finite mean and sd
-* independence
-* Linearity
-* Normality
-* Homoskidasticity
+### Finite Mean and Standard Deviation
+### Independence
+### Linearity
+### Normality
+### Homoskidasticity
 
@@
   theme_test(base_size = 30) 
-  #  #  theme_xaringan() +  +  
+  #    +  
 ```
@@
   geom_histogram(bins = 100) +
-  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")  #  #  theme_xaringan() +  +
+  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")
 
@@
 scale_x_continuous(limits = c(-4,4)) + 
-scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected") #  theme_xaringan() +  
+scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected")   
 ```
@@
   scale_y_continuous(limits = c(-4,4)) + 
-  #  theme_xaringan() +  +
   labs(y = "Residual", x = "Predicted Value")
@@
 - We identified these outliers.
-- confirmed they are not errors. 
-- decided to keep them because They are indicating a substancial loss in political freedom which falls outside of the scope of the model. However, is important for our reserach Q.
+- Confirmed they are not errors. 
+- Decided to keep them because they are indicating a substantial loss in political freedom which falls outside of the scope of the model. However, is important for our research question.
 ***
@@
 
-#### Brown Forsythe Test Dropping outliers
+#### Brown-Forsythe Test Dropping outliers
 
@@
 $$
-- Conclude Error variance is not constant
+- Conclude error variance is not constant
 
@@
 $$
-- Conclude again Error variance is not constant even when outliers are removed
+- Conclude again error variance is not constant even when outliers are removed
 

### 2020-11-16 slides.Rmd
fixed homoscedasticity

@@
 kable(t1, align = "c") %>%
-  kable_styling(position = "float_left", full_width = F, html_font = "Cambria") %>% 
+  kable_styling(position = "float_left", full_width = F) %>% 
   row_spec(3, color = "white", background = "#3C989E")
@@
 kable(t2, align = "c") %>%
-  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria")
+  kable_styling(full_width = FALSE, position = "left")
 ```
@@
 kable(t2, align = "c") %>%
-  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria") %>% 
+  kable_styling(full_width = FALSE, position = "left") %>% 
   row_spec(3, color = "white", background = "#3C989E")
@@
 ### Normality
-### Homoskidasticity
+### Homoscedasticity
 

### 2020-11-18 R/best_subset_selection.R
.

@@ -1,0 +1,35 @@
+library(tidyverse)
+
+# best_subset_selection ---------------------------------------------------
+
+data <- read_csv(here::here("data", "df.csv"))
+
+names(data)
+
+vars <- data %>% 
+  select(-country, -year, -ends_with("_fh")) %>%
+  names()
+
+outcome <- "polrights_fh"
+
+models <- list()
+for (i in 1:length(vars)) {
+  vc <- combn(vars,i)
+  for (j in 1:ncol(vc)) {
+    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
+    models <- c(models, model)
+  }
+}
+
+subsets <- map(models, function(x) lm(x, data)) %>% 
+  map(broom::glance) %>% 
+  setNames(models) %>% 
+  bind_rows(.id = "id") %>% 
+  distinct() %>% 
+  rename(model = id) 
+
+# writing -----------------------------------------------------------------
+
+write_csv(subsets, here::here("data", "subsets.csv"))
+
+subsets %>% select(model) %>% tail(1) %>% as.character()

### 2020-11-18 R/readinghwdata.R

@@ -1,0 +1,14 @@
+
+# reading in hw data ------------------------------------------------------
+
+
+devtools::install_github("bryangoodrich/ALSM")
+library(ALSM)
+
+
+set_names <- function(data){
+  colnames(data) <- setNames(nm = c(paste0("x", seq_along(data) - 1)))
+  colnames(data)[1] <- "y"
+  data
+}
+df <- set_names(CH06PR05)

### 2020-11-18 R/visualization.R

@@ -1,0 +1,125 @@
+library(tidyverse)
+# Visuals -------------------------------------------------------------
+theme_set(theme_light())
+
+data <- read_csv(here::here("data", "df.csv"))
+subsets <- read_csv(here::here("data", "subsets.csv"))
+names(data)
+
+corr_matrix <- data %>% 
+  select(-year, -country) %>% 
+  cor(.,  use = "complete.obs")
+
+View(corr_matrix)
+
+names(data)
+
+data %>% 
+  ggplot(mapping = aes(x = polrights_fh)) + 
+  geom_histogram(bins = 10)
+
+data %>% 
+  ggplot(mapping = aes(x = polrights_fh)) + 
+  geom_histogram()
+
+data %>% 
+  filter(year > 2015) %>% 
+  ggplot(mapping = aes(x = gini)) + 
+  geom_histogram()
+
+data %>% 
+  ggplot(aes(x = gini, y = polrights_fh)) +
+  geom_hex(binwidth = c(3, .6)) + 
+  scale_fill_gradient(low = "#7FFFD4", high = "#8B8378") + 
+  geom_smooth(method = "lm", se = TRUE, color = "red") +
+  geom_point(data = data %>% 
+               filter(country == "United States", 
+                         year == 2018), 
+      aes(x = gini, y = polrights_fh), size = 5, color = "red") +
+  labs(x = "GINI Coeffeceint", y = "Political Rights")
+
+data %>% 
+  ggplot(aes(x = gini, y = polrights_fh)) + 
+  geom_smooth(se = FALSE)
+
+r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+
+
+subsets %>% 
+  ggplot(aes(x = df, y = adj.r.squared)) + 
+  geom_point() + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
+  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared")
+
+AIC <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+
+subsets %>% 
+  ggplot(aes(x = df, y = AIC)) + 
+  geom_point() + 
+  geom_smooth(data = AIC, aes(df, AIC), se = FALSE, span = .5, color = "Green") + 
[…]

### 2020-11-19 slides.Rmd
.
updated slides

@@
 
-class: middle, center
-
+class: center
+# Mean Values of Covatiates by Country
 ```{r message=FALSE}
@@
 ---
-class: middle, center
+class: center
 
+# Mean Values of Covatiates by Country
 ```{r message=FALSE}
@@
 \begin{align}
-{\displaystyle t^{*}_{BF} ={\frac {{\bar {d}}_{1}-{\bar {d}}_{2}}{s^2 {\sqrt {{\frac {1}{n_{1}}}+{\frac {1}{n_{2}}}}}}}}
+{\displaystyle t^{*}_{BF} ={\frac {\bar {d}_{1}-{\bar {d}}_{2}}{s^2 {\sqrt {{\frac {1}{n_{1}}}+{\frac {1}{n_{2}}}}}}}}
 \end{align}

### 2020-11-19 R/best_subset_selection.R

@@ -26,7 +26,12 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   setNames(models) %>% 
   bind_rows(.id = "id") %>% 
   distinct() %>% 
-  rename(model = id) 
+  rename(model = id) %>% 
+  mutate(
+    model = str_replace_all(model, "_", " "),
+    model = str_replace(model, "~", "="), 
+    model = str_to_title(model))
+
 
 # writing -----------------------------------------------------------------
 

### 2020-11-19 slides.Rmd
data needed some cleaning and added some equasions

@@
   rename(a_rsq = adj.r.squared) %>% 
-  select(df, a_rsq, model) %>% 
-  mutate(
-    model = str_replace_all(model, "_", " "),
-    model = str_replace(model, "~", "=")) %>% 
+  select(df, a_rsq, Model) %>%
   arrange(desc(a_rsq)) %>% 
 DT::datatable(fillContainer = FALSE, options = list(pageLength = 3), 
-              colnames = c("DF", "A_Rsq", "Model"))
+              colnames = c("DF", "$$R^{2}_a$$", "Model"))
 ```
@@
   mutate_if(is.numeric, round, 3) %>% 
-  select(df, AIC, model) %>% 
-    mutate(
-    model = str_replace_all(model, "_", " "),
-    model = str_replace(model, "~", "=")) %>% 
+  select(df, AIC, Model) %>% 
   arrange(AIC) %>% 
@@
   mutate_if(is.numeric, round, 3) %>% 
-  select(df, BIC, model) %>% 
-    mutate(
-    model = str_replace_all(model, "_", " "),
-    model = str_replace(model, "~", "=")) %>% 
+  select(df, BIC, Model) %>% 
   arrange(BIC) %>% 
@@
   geom_point() + 
-  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "red") + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "#3C989E") + 
   labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
@@
   geom_point() + 
-  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "red") + 
+  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "#3C989E") + 
   labs(title = "", x = "Parameters", y = "AIC") + 

### 2020-11-19 R/best_subset_selection.R
made more friendly

@@ -28,9 +28,9 @@ subsets <- map(models, function(x) lm(x, data)) %>%
   distinct() %>% 
   rename(model = id) %>% 
   mutate(
-    model = str_replace_all(model, "_", " "),
-    model = str_replace(model, "~", "="), 
-    model = str_to_title(model))
+    Model = str_replace_all(model, "_", " "),
+    Model = str_replace(Model, "~", "="), 
+    Model = str_to_title(Model))
 
 
 # writing -----------------------------------------------------------------

### 2020-11-22 paper/paper.Rmd
preped paper

---
title             : "Identifying Factors That Affect Political Freedom Within the OECD"
shorttitle        : "Political Freedom Within the OECD"

author: 
  - name          : "Joe Despres"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
  - name          : "Sabrina Ball"
    affiliation   : "1"
  - name          : "Jacob?"
    affiliation   : "1"
  - name          : "Joe Sigler"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Michigan State University"

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Using @Gapminder

## Introduction/Motivation

## Results

## Conclusion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-11-22 paper/paper.tex
preped paper

--- 2020-11-03 paper.tex
@@
 \hypersetup{
-  pdftitle={The title},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdftitle={Identifying Factors That Affect Political Freedom Within the OECD},
+  pdfauthor={Joe Despres1, Sabrina Ball1, Jacob?1, \& Joe Sigler1},
   pdflang={en-EN},
@@
 \makeatother
-\shorttitle{Title}
+\shorttitle{Political Freedom Within the OECD}
 \keywords{keywords\newline\indent Word count: X}
@@
 
-\title{The title}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\title{Identifying Factors That Affect Political Freedom Within the OECD}
+\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob?\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
 \date{}
 
-\authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
-The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
-
-\abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
-}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Michigan State University}
 
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+Using Rosling (2020)
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-We used R (Version 4.0.2; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.
+\hypertarget{introductionmotivation}{%
+\subsection{Introduction/Motivation}\label{introductionmotivation}}
 
 \hypertarget{results}{%
-\section{Results}\label{results}}
+\subsection{Results}\label{results}}
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 
@@
 \begin{cslreferences}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+\leavevmode\hypertarget{ref-Gapminder}{}%
+Rosling, H. (2020). \emph{Gapminder}. Retrieved from \url{https://www.gapminder.org/data/}
 \end{cslreferences}

### 2020-11-23 slides.Rmd
usless git commit
rm comment

@@
 # Summary Statistics
+
 ---
@@
   scale_x_continuous(breaks = 1:7) + 
-  theme_test(base_size = 30) + 
-#    + 
   theme(legend.position = "none") + 
@@
 
+---
+
+```{r}
+data %>% 
+  ggplot(aes(x = year, y = polrights_fh)) + 
+  geom_col() +
+  facet_wrap(~country) + 
+  coord_flip() + 
+  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
+  scale_x_continuous(breaks = 1:7) + 
+  theme(legend.position = "none")
+  theme_light(base_size = 12)
+```
 ---
@@
 
-#### Brown-Forsythe Test Dropping outliers
+#### Brown-Forsythe Test
 
@@
 \begin{align}
+t(.975; 643) = 1.963
+\end{align}
+$$
+***
+
+$$
+\begin{align}
 {\displaystyle t^{*}_{BF} ={\frac {0.489 -{0.177}}{0.176 {\sqrt {{\frac {1}{324}}+{\frac {1}{324}}}}}}} = 9.49
@@
 
-$$
-\begin{align}
-t(.975; 643) = 1.963
-\end{align}
-$$
 - Conclude error variance is not constant
@@
 ***
+$$
+\begin{align}
+t(.975; 639) = 1.963
+\end{align}
+$$
+***
 
@@
 
-$$
-\begin{align}
-t(.975; 639) = 1.963
-\end{align}
-$$
 - Conclude again error variance is not constant even when outliers are removed

### 2020-11-23 R/cleaningscript.R
reoiented cpi

@@ -32,11 +32,9 @@ data <- data %>%
          # these murder rates were not included in the gapminder but i didnt want to 
          # lose 3 important countries in LA
   relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
-                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)
+                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)%>% 
+  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1)
 
 # writing -----------------------------------------------------------------
 
 write_csv(data, here::here("data", "df.csv"))
-
-View(data)
-skimr::skim(ungroup(data))

### 2020-11-24 R/best_subset_selection.R
ran best subsets with interactions

@@ -16,8 +16,14 @@ models <- list()
 for (i in 1:length(vars)) {
   vc <- combn(vars,i)
   for (j in 1:ncol(vc)) {
+    for(k in 1:ncol(vc)){
+    if(k == j){
     model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
+    }else{
+    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j],"*", vc[,k], collapse = " + ")))
+    }
     models <- c(models, model)
+    }
   }
 }
 
@@ -31,10 +37,11 @@ subsets <- map(models, function(x) lm(x, data)) %>%
     Model = str_replace_all(model, "_", " "),
     Model = str_replace(Model, "~", "="), 
     Model = str_to_title(Model))
+View(subsets)
 
-
+beepr::beep()
 # writing -----------------------------------------------------------------
 
-write_csv(subsets, here::here("data", "subsets.csv"))
+#write_csv(subsets, here::here("data", "subsets.csv"))
 
 subsets %>% select(model) %>% tail(1) %>% as.character()

### 2020-11-24 R/regression.R

@@ -12,6 +12,13 @@ model_df5_formula <- subsets %>% filter(df == 5) %>%
   select(model) %>% head(1) %>% as.character()
 
 fit_df5 <- lm(model_df5_formula, data)
+lm(polrights_fh ~ corruption_perception_index_cpi + 
+     I(corruption_perception_index_cpi^2) +  
+     edu_exp_gdp_per_person + 
+     life_expectancy_years + 
+     military_spending_pct_of_gdp + 
+     murder_per_mil_people, data) %>% summary()
+
 
 # Second model ------------------------------------------------------------
 

### 2020-11-24 slides.Rmd
rm plot
worked on slides

@@
 options(htmltools.dir.version = FALSE, echo = FALSE)
-knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 8)
+knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 8)
 
@@
 
-* We ask: What factors are associated with an increase in political freedom?.
+* We ask: What factors are associated with an increase in political freedom?
 
@@
 * Filtered to only include OECD Countries from year 2000 to 2018 by necessity.
+--
+
+* Made adjustments for more intuitive interpretations.
 
@@
 
-- Corruption Perception Index ranges from 0 to 100 with 0 being the highest perception of corruption
+- **Corruption Perception** Index ranges from 0 to 100 with 100 being the highest perception of corruption
 
@@
 
-- Education Expenditure in GDP per Person
+- **Education Expenditure** in GDP per Person
 
@@
 
-- Electricity use per person in Kilowatt Hours
+- **Electricity use** per person in Kilowatt Hours
 
@@
 
-- Gini Coefficient: A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth
+- **Gini Coefficient:** A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth
 
@@
 
-- Percentage of population That use the Internet
+- **Internet Users** as percentage of Population
 
@@
 
-- Labor Force Participation
+- **Labor Force** Participation rate
 
@@
 
-- Life Expectancy
+- **Life Expectancy**
 
@@
 
-- Military Spending as a percentage of GDP
+- **Military Spending** as a percentage of GDP
 
@@
 
-- Murders per million people
+- **Murders rate** per million people
 
@@
 
-```{r}
-data %>% 
-  ggplot(aes(x = year, y = polrights_fh)) + 
-  geom_col() +
-  facet_wrap(~country) + 
-  coord_flip() + 
-  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
-  scale_x_continuous(breaks = 1:7) + 
-  theme(legend.position = "none")
-  theme_light(base_size = 12)
-```
----
-
 # Assumptions
@@
   select(df, a_rsq, Model) %>%
-  arrange(desc(a_rsq)) %>% 
+  arrange(match(df, c(5, 4, 6)), desc(a_rsq)) %>% 
 DT::datatable(fillContainer = FALSE, options = list(pageLength = 3), 
@@
 ```
-
 ---
-# Best Subsets by AIC
-```{r message=FALSE}
-subsets %>% 
-  group_by(df) %>% 
-  filter(AIC == min(AIC)) %>% 
-  mutate_if(is.numeric, round, 3) %>% 
-  select(df, AIC, Model) %>% 
-  arrange(AIC) %>% 
-DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
-              colnames = c("DF", "AIC", "Model"))
-```
-
----
-
-# Best Subsets by BIC
-```{r message=FALSE}
-subsets %>% 
-  group_by(df) %>% 
-  filter(BIC == min(BIC)) %>% 
-  mutate_if(is.numeric, round, 3) %>% 
-  select(df, BIC, Model) %>% 
-  arrange(BIC) %>% 
-DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
-              colnames = c("DF", "BIC", "Model"))
-```
-
----
-
 class: center, middle
 
-# Best Subsets
+# Best Subsets by Adjusted R Squared
 
@@
   theme_test(base_size = 30) 
-  #    +  
 ```
@@
 ---
+# Best Subsets by AIC
+```{r message=FALSE}
+subsets %>% 
+  group_by(df) %>% 
+  filter(AIC == min(AIC)) %>% 
+  mutate_if(is.numeric, round, 3) %>% 
+  select(df, AIC, Model) %>% 
+  arrange(match(df, c(5, 4, 6)), desc(AIC)) %>% 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
+              colnames = c("DF", "AIC", "Model"))
+```
+
+---
+
 class: center, middle
 
-# Best Subsets
+# Best Subsets by AIC
 
@@
 
-class: inverse, middle, center
-
+class: inverse, center
 # Model
-
----
-
-class: center, middle
 ```{r}
@@
 class: center
+$$
+\scriptsize
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
+
+```{r message=FALSE}
+size <- 18
+a <- data %>% 
+  ggplot(aes(x = corruption_perception_index_cpi, y = polrights_fh)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
+  scale_y_continuous(breaks = 1:7) + 
+  labs(x = "Corruption Perception", y = "Political Rights") + theme_light(base_size = size)
+
+b <- data %>% 
+  ggplot(aes(x = edu_exp_gdp_per_person, y = polrights_fh)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
+    scale_y_continuous(breaks = 1:7) + 
+  labs(x = "Education Expendature", y = "") + theme_light(base_size = size)
+
+c <- data %>% 
+  ggplot(aes(x = life_expectancy_years, y = polrights_fh)) + 
+  geom_point()+ 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
+    scale_y_continuous(breaks = 1:7) + 
+  labs(x = "Life Expectacy", y = "") + theme_light(base_size = size)
+
+d <- data %>% 
+  ggplot(aes(x = military_spending_pct_of_gdp, y = polrights_fh)) + 
+  geom_point()+ 
+  scale_y_continuous(breaks = 1:7) + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
+  labs(x = "Military Spending", y = "")+ theme_light(base_size = size)
+
+e <- data %>% 
+  ggplot(aes(x = murder_per_mil_people, y = polrights_fh)) + 
+  geom_point() + 
+  scale_y_continuous(breaks = 1:7) + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
+  labs(x = "Murder Rate", y = "") + theme_light(base_size = size)
+
+(a + b) / (c + d + e) 
+```
+
+---
+class: center
 
 $$
-\small
+\scriptsize
+\begin{align}
+\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
+\end{align}
+$$
+# Correlation Matrix
+```{r}
+corr_matrix <- data %>%
+  select(polrights_fh,corruption_perception_index_cpi,edu_exp_gdp_per_person,life_expectancy_years,military_spending_pct_of_gdp,murder_per_mil_people) %>% 
+  cor()
+
+rownames(corr_matrix) <- c("Political Rights", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")
+colnames(corr_matrix) <-  c("Political Rights", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")
+kable(round(corr_matrix, 2)) %>% 
+  kable_styling(font_size = 12)
+```
+
+---
+
+class: center
+
+$$
+\scriptsize
 \begin{align}
@@
 $$
-\small
+\scriptsize
 \begin{align}
@@
 
-```{r warning=FALSE}
+```{r}
 
@@
   ggplot(aes(.resid)) + 
-  geom_histogram(bins = 100) +
+  geom_histogram(bins = 75, fill = "black") +
   scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")
@@
   stat_qq() +
-  stat_qq_line() + 
+  stat_qq_line(color = "#3C989E") + 
 scale_x_continuous(limits = c(-4,4)) + 
@@
         caption = "Removed Outliers")
+
+vars <- rownames(summary(fit_df5)$coef)
+vars[1] <- "polrights_fh"
 ```
@@
 
+> "A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance".
+-Chapter 3 p.108
+
+***
 - We identified these outliers.
@@
 - Decided to keep them because they are indicating a substantial loss in political freedom which falls outside of the scope of the model. However, is important for our research question.
-***
-> "A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance".
--Chapter 3 p.108
 
@@
 
-- Conclude again error variance is not constant even when outliers are removed
+- Conclude, again, error variance is not constant even when outliers are removed.
+- The model does a much better job at predicting political freedom in countries with more. This is likely due to the fact that our sample is the OCED that skews twards more Political Freedom
 
@@
 
-1. we think this
+1. Despite minor problems with outliers we found that statistically significant 
 1. because

### 2020-11-24 paper/paper.Rmd
half way done with paper

@@
 title             : "Identifying Factors That Affect Political Freedom Within the OECD"
-shorttitle        : "Political Freedom Within the OECD"
+shorttitle        : "RUNNING HEAD: Political Freedom Within the OECD"
 
@@
     affiliation   : "1"
-  - name          : "Jacob?"
+  - name          : "Jacob Haywood"
     affiliation   : "1"
@@
 
+date: 
+  - "Last compiled `r format(Sys.time(), '%H:%M')`"
+
 keywords          : "keywords"
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 ```{r setup, include = FALSE}
+library(tidyverse)
+library(kableExtra)
+library(stargazer)
+
 library("papaja")
 r_refs("r-references.bib")
+source(here::here("R", "regression.R"))
+knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 8)
+
+data <- readr::read_csv(here::here("data", "df.csv")) 
+subsets <- readr::read_csv(here::here("data", "subsets.csv"))
+
+stats_summary <- function(df, x, group_var1, group_var2, rounding_digits = 1){
+
+    x <- dplyr::enquo(x)
+
+    group_var1 <- dplyr::enquo(group_var1)
+    group_var2 <- dplyr::enquo(group_var2)
+
+    df %>%
+      dplyr::group_by(!!group_var1, !!group_var2) %>%
+      dplyr::summarise(Total = sum ( !! x),
+                       Mean  = mean( !! x),
+                     Median  = median( !! x),
+                `Mean - Med` =  mean( !! x) - median( !! x),
+                         Std = sd  ( !! x),
+                         Min = min ( !! x),
+                         Max = max ( !! x),
+                      Number = n() ) %>%
+      dplyr::mutate_if(is.numeric, round, rounding_digits)
+  }
 ```
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+## Introduction
+
+2020 is an election year, which has many of use reflecting on political freedoms.
+Political freedoms are important because they have a dramatic impact on the quality of life for the citizens of a country.
+Such reflection has us asking: What factors are associated with an increase in political freedom around the world?
+Political freedom is an abstract concept that does not lend well to quantification.
+However, Freedom House @Freedomhouse, a U.S.
+based think tank and research institute, attempts this by assigning a index of political rights to each country every year based on a fixed criteria.
+
+The Political Rights Index is comprised of three subcategories.
+Electoral process, political participation, and functioning government.
+Electoral process is a score based on how the current government leaders were selected.
+How fairly the positions was obtained and kept.
+As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
+Political Participation is evaluated on four criteria, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Functioning government, is the current heads of government determine policies, safeguards against corruption, and openness and transparency of government operation.
+Political freedom has been measured in this manner for every country from the years 1978 to present.
+
+Although such a metric is far from perfect.
+This will serve as a reasonable measure of political freedom around the world and will serve as an adequate sample to study political freedom.
+We obtained this from the Gapminder Foundation @Gapminder, a non-profit organization that studies and promotes economic development.
+After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
+To explain a country's political rights index we selected: Corruption Perception Index, Education Expenditure, Electricity Use, Gini Coefficient, Internet Users as a percentage, Labor Force Participation Rate, Military Spending as percentage of GDP, and Murders per million.
+
+## Data
+
+These data sets were separate so we downloaded them individually, cleaned and combined them together using R @R-base and the Tidyverse Package @R-tidyverse.
+This resulted in a data set with all 196 countries form years 1950 to 2030 (data after 2019 were projections).
+It was immediately apparent that there was a substantial amount of missing data in an obvious pattern.
+Less developed countries tended to have more missing data points.
+Also, the further back in time the more missing data points.
+Had we conducted this study as it was it would have been severely biased towards more developed countries as missing data points would be dropped.
+This forced us to narrow the scope of the study and focus only on countries within the Organization for Economic Co-operation and Development (OECD).
+This subset of countries has a reasonably complete data.
+Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
+
+This remedied most of the missing datapoints.
+However, even within the OEDC there were sparse few missing data points.
+From there, we imputed the median of each country's variable.
+For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period.
+Which afforded us the ability to keep even more data with minimal compromise.
+This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
+After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0% of their GDP, so we replaced the NA with a 0.
+This afforded us a full data set with no missing data points.
+
+## Descriptive Statistics
+
+```{r fig.align="center", results='asis'}
+stat <- function(df = data, x, rounding_digits = 2){
+
+    x <- dplyr::enquo(x)
+    df %>%
+      dplyr::summarise(
+                       Mean  = mean( !! x),
+                     Median  = median( !! x),
+                         Std = sd  ( !! x),
+                         Min = min ( !! x),
+                         Max = max ( !! x),
+                       Range = max(!! x) - min(!! x) ) %>%
+      dplyr::mutate_if(is.numeric, round, rounding_digits)
+  }
+
+data %>% 
+  select(-country) %>% 
+map(function(x){stat(x, df = data)}) %>% 
+  bind_rows(.id = "Variable") %>% 
+  mutate(Variable = replace(Variable, 
+                            values = c("Political Rights", "Year", "Corruption Perception", "Education Expenditure", "Electricity Use", "Gini", "Internet Users","Life Expectancy", "Labor Force Participation", "Military Spending", "Murders rate"))) %>%
+kable(
+  format = "latex",
+  booktabs = TRUE,
+  escape = FALSE,
+  longtable = TRUE,
+ caption = "Descriptive Statistics")
 ```
 
-Using @Gapminder
+Table 1 made with the @R-kableExtra contains Basic summary statistics from our dataset.
+We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
+This is not ideal.
+We would much prefer that it was continuous with a substantial variation.
+First, the methodology of rather than taking continuous values Freedomhouse's classification is discrete classifying countries political rights taking values of the integers 1-7.
+Secondly countries with a low political rights by nature have a suspect data reporting process.
+Which is why we had to select a subset of countries and that subset leans towards having more political freedom.
+We precede on the understanding that there are moderate problems with the data, first having a discrete response variable and the nature of the distribution being skewed towards the maximum 7/7 political freedom.
 
-## Introduction/Motivation
+With such considerations taken into account, we will not be making any non-linear transformation or variables.
+First, we examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+With a clean, complete, and dataset that is contains flaws but is still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
+This lead us to choose between the following models.
+From the graph of the subsets we can see that the increase in $R^2$ and $AIC$ by adding additional paramaters.
+
+```{r fig.show="hold", out.width="50%"}
+r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+
+subsets %>% 
+  ggplot(aes(x = df, y = adj.r.squared)) + 
+  geom_point() + 
+  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "#3C989E") + 
+  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
+  scale_x_continuous(breaks = 1:9) + 
+  theme_test(base_size = 30)
+
+r <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+
+subsets %>% 
+  ggplot(aes(x = df, y = AIC)) + 
+  geom_point() + 
+  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "#3C989E") + 
+  labs(title = "", x = "Parameters", y = "AIC") + 
+  scale_x_continuous(breaks = 1:9) + 
+  theme_test(base_size = 30)
+
+```
+
+## Model
+
+$\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) + \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon$
+
+(chart here)
+
+The model that displayed the most statistical sense in conjuction with our exsistin inutitions is.
+(formula here)
 
 ## Results
+See table 1 made in stargazer @R-stargazer
+
+```{r results="asis"}
+stargazer(fit_df6, fit_df5, fit_df4, type = "latex", 
+                     title = "Regression Results", 
+                     covariate.labels = c("(Intercept)", "Corruption Perception", 
+                                          "Education Expendature", "Life Expectancy",
+                                          "Military Spending", "Murder Rate"),
+                     dep.var.caption = "Political Rights Index",
+                     dep.var.labels = NULL,
+                     dep.var.labels.include = FALSE, 
+                     model.names = FALSE,
+                     model.numbers = FALSE,
+                     df = FALSE, 
+                     header = FALSE,
+                     column.labels = c("DF = 6", "DF = 5", "DF = 4"),
+                     no.space = TRUE)
+```
+
+## Remeidal Measures
 

### 2020-11-24 paper/paper.tex
half way done with paper

@@
   english,
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
   pdftitle={Identifying Factors That Affect Political Freedom Within the OECD},
-  pdfauthor={Joe Despres1, Sabrina Ball1, Jacob?1, \& Joe Sigler1},
+  pdfauthor={Joe Despres1, Sabrina Ball1, Jacob Haywood1, \& Joe Sigler1},
   pdflang={en-EN},
@@
 \makeatother
-\shorttitle{Political Freedom Within the OECD}
+\shorttitle{RUNNING HEAD: Political Freedom Within the OECD}
 \keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 \title{Identifying Factors That Affect Political Freedom Within the OECD}
-\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob?\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
-\date{}
+\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
+\date{Last compiled 18:41}
 
@@
 
-Using Rosling (2020)
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
-\hypertarget{introductionmotivation}{%
-\subsection{Introduction/Motivation}\label{introductionmotivation}}
+2020 is an election year, which has many of use reflecting on political freedoms.
+Political freedoms are important because they have a dramatic impact on the quality of life for the citizens of a country.
+Such reflection has us asking: What factors are associated with an increase in political freedom around the world?
+Political freedom is an abstract concept that does not lend well to quantification.
+However, Freedom House (\emph{Countries and Territories}, 2020), a U.S.
+based think tank and research institute, attempts this by assigning a index of political rights to each country every year based on a fixed criteria.
+
+The Political Rights Index is comprised of three subcategories.
+Electoral process, political participation, and functioning government.
+Electoral process is a score based on how the current government leaders were selected.
+How fairly the positions was obtained and kept.
+As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
+Political Participation is evaluated on four criteria, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Functioning government, is the current heads of government determine policies, safeguards against corruption, and openness and transparency of government operation.
+Political freedom has been measured in this manner for every country from the years 1978 to present.
+
+Although such a metric is far from perfect.
+This will serve as a reasonable measure of political freedom around the world and will serve as an adequate sample to study political freedom.
+We obtained this from the Gapminder Foundation Rosling (2020), a non-profit organization that studies and promotes economic development.
+After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
+To explain a country's political rights index we selected: Corruption Perception Index, Education Expenditure, Electricity Use, Gini Coefficient, Internet Users as a percentage, Labor Force Participation Rate, Military Spending as percentage of GDP, and Murders per million.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+These data sets were separate so we downloaded them individually, cleaned and combined them together using R R Core Team (2020) and the Tidyverse Package Wickham et al.
+(2019).
+This resulted in a data set with all 196 countries form years 1950 to 2030 (data after 2019 were projections).
+It was immediately apparent that there was a substantial amount of missing data in an obvious pattern.
+Less developed countries tended to have more missing data points.
+Also, the further back in time the more missing data points.
+Had we conducted this study as it was it would have been severely biased towards more developed countries as missing data points would be dropped.
+This forced us to narrow the scope of the study and focus only on countries within the Organization for Economic Co-operation and Development (OECD).
+This subset of countries has a reasonably complete data.
+Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
+
+This remedied most of the missing datapoints.
+However, even within the OEDC there were sparse few missing data points.
+From there, we imputed the median of each country's variable.
+For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period.
+Which afforded us the ability to keep even more data with minimal compromise.
+This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
+After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0\% of their GDP, so we replaced the NA with a 0.
+This afforded us a full data set with no missing data points.
+
+\hypertarget{descriptive-statistics}{%
+\subsection{Descriptive Statistics}\label{descriptive-statistics}}
+
+\begin{longtable}[t]{lrrrrrr}
+\caption{\label{tab:unnamed-chunk-1}Descriptive Statistics}\\
+\toprule
+Variable & Mean & Median & Std & Min & Max & Range\\
+\midrule
+Political Rights & 6.60 & 7.00 & 0.79 & 2.00 & 7.00 & 5.00\\
+Year & 2009.50 & 2009.50 & 5.19 & 2001.00 & 2018.00 & 17.00\\
+Corruption Perception & 31.95 & 29.00 & 15.87 & 8.00 & 71.00 & 63.00\\
+Education Expenditure & 0.20 & 0.20 & 0.04 & 0.10 & 0.37 & 0.27\\
+Electricity Use & 8682.17 & 6695.00 & 7533.32 & 866.00 & 54800.00 & 53934.00\\
+\addlinespace
+Gini & 33.77 & 32.70 & 6.35 & 24.40 & 56.80 & 32.40\\
+Internet Users & 65.41 & 70.90 & 22.93 & 2.85 & 99.00 & 96.15\\
+Life Expectancy & 0.60 & 0.61 & 0.06 & 0.45 & 0.78 & 0.33\\
+Labor Force Participation & 79.30 & 80.00 & 2.84 & 70.20 & 84.40 & 14.20\\
+Military Spending & 1.68 & 1.41 & 1.16 & 0.00 & 8.54 & 8.54\\
+\addlinespace
+Murders rate & 3.13 & 1.04 & 6.15 & 0.15 & 29.07 & 28.92\\
+\bottomrule
+\end{longtable}
+
+Table 1 made with the Zhu (2020) contains Basic summary statistics from our dataset.
+We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
+This is not ideal.
+We would much prefer that it was continuous with a substantial variation.
+First, the methodology of rather than taking continuous values Freedomhouse's classification is discrete classifying countries political rights taking values of the integers 1-7.
+Secondly countries with a low political rights by nature have a suspect data reporting process.
+Which is why we had to select a subset of countries and that subset leans towards having more political freedom.
+We precede on the understanding that there are moderate problems with the data, first having a discrete response variable and the nature of the distribution being skewed towards the maximum 7/7 political freedom.
+
+With such considerations taken into account, we will not be making any non-linear transformation or variables.
+First, we examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+With a clean, complete, and dataset that is contains flaws but is still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
+This lead us to choose between the following models.
+From the graph of the subsets we can see that the increase in \(R^2\) and \(AIC\) by adding additional paramaters.
+
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-2-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-2-2} \caption{ }\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\hypertarget{model}{%
+\subsection{Model}\label{model}}
+
+\(\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) + \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\)
+
+(chart here)
+
+The model that displayed the most statistical sense in conjuction with our exsistin inutitions is.
+(formula here)
 
@@
 \subsection{Results}\label{results}}
+
+See table 1 made in stargazer Hlavac (2018)
+
+\begin{table}[!htbp] \centering 
+  \caption{Regression Results} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{3}{c}{Political Rights Index} \\ 
+\cline{2-4} 
+ & DF = 6 & DF = 5 & DF = 4 \\ 
+\hline \\[-1.8ex] 
+ (Intercept) & $-$0.023$^{***}$ & $-$0.023$^{***}$ & $-$0.022$^{***}$ \\ 
+  & (0.002) & (0.002) & (0.002) \\ 
+  Corruption Perception & 1.746$^{***}$ & 1.900$^{***}$ & 1.898$^{***}$ \\ 
+  & (0.562) & (0.534) & (0.536) \\ 
+  Education Expendature & 0.001 &  &  \\ 
+  & (0.001) &  &  \\ 
+  Life Expectancy & $-$0.025$^{***}$ & $-$0.021$^{**}$ &  \\ 
+  & (0.009) & (0.008) &  \\ 
+  Military Spending & $-$0.146$^{***}$ & $-$0.150$^{***}$ & $-$0.153$^{***}$ \\ 
+  & (0.019) & (0.019) & (0.019) \\ 
+  Murder Rate & $-$0.035$^{***}$ & $-$0.035$^{***}$ & $-$0.033$^{***}$ \\ 
+  & (0.004) & (0.004) & (0.004) \\ 
+  Constant & 9.212$^{***}$ & 8.979$^{***}$ & 7.284$^{***}$ \\ 
+  & (0.742) & (0.692) & (0.123) \\ 
+ \hline \\[-1.8ex] 
+Observations & 648 & 648 & 648 \\ 
+R$^{2}$ & 0.548 & 0.547 & 0.543 \\ 
+Adjusted R$^{2}$ & 0.543 & 0.544 & 0.540 \\ 
+Residual Std. Error & 0.531 & 0.531 & 0.533 \\ 
+F Statistic & 129.343$^{***}$ & 155.112$^{***}$ & 190.808$^{***}$ \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\hypertarget{remeidal-measures}{%
+\subsection{Remeidal Measures}\label{remeidal-measures}}
 
@@
 \begin{cslreferences}
+\leavevmode\hypertarget{ref-Freedomhouse}{}%
+\emph{Countries and territories}. (2020). Washington D.C.: Freedomhouse. Retrieved from \url{https://freedomhouse.org}
+
+\leavevmode\hypertarget{ref-R-stargazer}{}%
+Hlavac, M.
+(2018).
+\emph{Stargazer: Well-formatted regression and summary statistics tables}.
+Bratislava, Slovakia: Central European Labour Studies Institute (CELSI).
+Retrieved from \url{https://CRAN.R-project.org/package=stargazer}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
 \leavevmode\hypertarget{ref-Gapminder}{}%
 Rosling, H. (2020). \emph{Gapminder}. Retrieved from \url{https://www.gapminder.org/data/}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the tidyverse.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-kableExtra}{}%
+Zhu, H. (2020). \emph{KableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
 \end{cslreferences}

### 2020-11-25 paper/paper.Rmd
done for the day

@@
 title             : "Identifying Factors That Affect Political Freedom Within the OECD"
-shorttitle        : "RUNNING HEAD: Political Freedom Within the OECD"
+shorttitle        : "Political Freedom Within the OECD"
 
@@
 floatsintext      : yes
-figurelist        : no
-tablelist         : no
+figurelist        : yes
+tablelist         : yes
 footnotelist      : no
@@
 library(stargazer)
+library(patchwork)
+size <- 30
 
@@
 r_refs("r-references.bib")
-source(here::here("R", "regression.R"))
-knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 8)
 
-data <- readr::read_csv(here::here("data", "df.csv")) 
-subsets <- readr::read_csv(here::here("data", "subsets.csv"))
+knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, 
+                      fig.width = 12, fig.height = 8)
 
-stats_summary <- function(df, x, group_var1, group_var2, rounding_digits = 1){
+# Read and Clean ----------------------------------------------------------
+files <- list.files(path = here::here("raw_data"), pattern = ".csv")
 
-    x <- dplyr::enquo(x)
+cleaning <- function(df){
+  df <- pivot_longer(df, cols = -country, names_to = "year")
+}
 
-    group_var1 <- dplyr::enquo(group_var1)
-    group_var2 <- dplyr::enquo(group_var2)
+data <- files %>% 
+  map(function(x) read_csv(paste0("raw_data/", x))) %>% 
+  setNames(gsub("\\.csv$", "", files)) %>% 
+  map(cleaning) %>% 
+  bind_rows(.id = "id") %>% 
+  pivot_wider(names_from = id)
 
-    df %>%
-      dplyr::group_by(!!group_var1, !!group_var2) %>%
-      dplyr::summarise(Total = sum ( !! x),
-                       Mean  = mean( !! x),
-                     Median  = median( !! x),
-                `Mean - Med` =  mean( !! x) - median( !! x),
-                         Std = sd  ( !! x),
-                         Min = min ( !! x),
-                         Max = max ( !! x),
-                      Number = n() ) %>%
-      dplyr::mutate_if(is.numeric, round, rounding_digits)
+# Filtering ---------------------------------------------------------------
+
+countries <- readRDS(here::here("data", "countries.RDS"))
+
+data <- data %>%
+  filter(year > 2000, year < 2019, country %in% countries) %>% 
+  group_by(country) %>%
+  mutate_at(vars(-country),list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
+# Iceland spent 0 so I needed to manually recode that
+  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
+  mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
+         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
+         # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
+         # these murder rates were not included in the gapminder but i didnt want to 
+         # lose 3 important countries in LA
+  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
+                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)%>% 
+  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1)
+
+# Best Subset Selection ---------------------------------------------------------------
+
+vars <- data %>% 
+  select(-country, -year, -ends_with("_fh")) %>%
+  names()
+
+outcome <- "polrights_fh"
+
+models <- list()
+for (i in 1:length(vars)) {
+  vc <- combn(vars,i)
+  for (j in 1:ncol(vc)) {
+    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
+    models <- c(models, model)
+
     }
+  }
+
+subsets <- map(models, function(x) lm(x, data)) %>% 
+  map(broom::glance) %>% 
+  setNames(models) %>% 
+  bind_rows(.id = "id") %>% 
+  distinct() %>% 
+  rename(model = id) %>% 
+  mutate(
+    Model = str_replace_all(model, "_", " "),
+    Model = str_replace(Model, "~", "="), 
+    Model = str_to_title(Model))
+```
+
+```{r models}
+model_df6_formula <- subsets %>% filter(df == 6) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df6 <- lm(model_df6_formula, data)
+
+model_df5_formula <- subsets %>% filter(df == 5) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df5 <- lm(model_df5_formula, data)
+
+model_df4_formula <- subsets %>% filter(df == 4) %>% 
+  arrange(desc(adj.r.squared)) %>% 
+  select(model) %>% head(1) %>% as.character()
+
+fit_df4 <- lm(model_df4_formula, data)
 ```
@@
 Political freedom is an abstract concept that does not lend well to quantification.
-However, Freedom House @Freedomhouse, a U.S.
+However, Freedom House [@Freedomhouse], a U.S.
 based think tank and research institute, attempts this by assigning a index of political rights to each country every year based on a fixed criteria.
+Using the Papaja Package by [@R-papaja] package we take rmarkdown directly to APA format.
 
-The Political Rights Index is comprised of three subcategories.
+The **Political Rights** Index is comprised of three subcategories.
 Electoral process, political participation, and functioning government.
@@
 This will serve as a reasonable measure of political freedom around the world and will serve as an adequate sample to study political freedom.
-We obtained this from the Gapminder Foundation @Gapminder, a non-profit organization that studies and promotes economic development.
+We obtained this from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
@@
 
-These data sets were separate so we downloaded them individually, cleaned and combined them together using R @R-base and the Tidyverse Package @R-tidyverse.
+These data sets were separate so we downloaded them individually, cleaned and combined them together using R [@R-base] and the Tidyverse Package [@R-tidyverse].
 This resulted in a data set with all 196 countries form years 1950 to 2030 (data after 2019 were projections).
@@
 This afforded us a full data set with no missing data points.
+The only other adjustment made was to make a few of the variables more intuitive.
+Corruption perception for example was originally having 0 be the most perception of corruption and 100 being the least.
+For us we wanted to have a more intuitve interpretation so we subtracted 100 and mulitplied by negaitve one.
 
@@
   mutate(Variable = replace(Variable, 
-                            values = c("Political Rights", "Year", "Corruption Perception", "Education Expenditure", "Electricity Use", "Gini", "Internet Users","Life Expectancy", "Labor Force Participation", "Military Spending", "Murders rate"))) %>%
+                            values = c("Political Rights", "Year", 
+                                       "Corruption Perception", 
+                                       "Education Expenditure", 
+                                       "Electricity Use", 
+                                       "Gini", 
+                                       "Internet Users",
+                                       "Life Expectancy", 
+                                       "Labor Force Participation", 
+                                       "Military Spending", 
+                                       "Murders rate"))) %>% 
 kable(
@@
 
-Table 1 made with the @R-kableExtra contains Basic summary statistics from our dataset.
+Table 1 made with the [@R-kableExtra] contains Basic summary statistics from our dataset.
 We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
@@
 This lead us to choose between the following models.
-From the graph of the subsets we can see that the increase in $R^2$ and $AIC$ by adding additional paramaters.
+From the graph of the subsets we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
 
 ```{r fig.show="hold", out.width="50%"}
-r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))
+r <- subsets %>% 
+  group_by(df) %>% 
+  summarise(adj = max(adj.r.squared, na.rm = T))
 
@@
   geom_point() + 
-  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "#3C989E") + 
+  geom_smooth(data = r, aes(df, adj), 
+              se = FALSE, span = 0.5, color = "#3C989E") + 
   labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
   scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = 30)
+  theme_test(base_size = size)
 
-r <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
+r <- subsets %>% 
+  group_by(df) %>% 
+  summarise(AIC = max(AIC, na.rm = T))
 
@@
   geom_point() + 
-  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "#3C989E") + 
+  geom_smooth(data = r, aes(df, AIC), 
+              se = FALSE, span = 0.5, color = "#3C989E") + 
   labs(title = "", x = "Parameters", y = "AIC") + 
   scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = 30)
+  theme_test(base_size = size)
 
 ```
-
-## Model
-
-$\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) + \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon$
-
-(chart here)
-
-The model that displayed the most statistical sense in conjuction with our exsistin inutitions is.
-(formula here)
-
-## Results
-See table 1 made in stargazer @R-stargazer
 
@@
                      title = "Regression Results", 
-                     covariate.labels = c("(Intercept)", "Corruption Perception", 
-                                          "Education Expendature", "Life Expectancy",
-                                          "Military Spending", "Murder Rate"),
+                     covariate.labels = c("Corruption Perception", "Education Expendature",
+                                          "Internet Users", "Life Expectancy",
+                                          "Military Spending", "Murder Rate", 
+                                          "Intercept"),
                      dep.var.caption = "Political Rights Index",
@@
 
+## Model Selection
+
+From the best subsets, it was appropriate to narrow our model choices down to three.
+First, the model with six degrees of freedom, next one with five, and one with four.
+The results from these three models is in Table 2 made using Stargazer [@R-stargazer] on the next page.
+The model with six degrees of freedom contains **Internet Users** which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way.
+Looking at the model with five degrees of freedom, all of our coefficients are statistically significant at $p < 0.01$.
+The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
+Counterintuitively, politically freedom seems to decrease as life expectancy increases.
+We are not qualified to attempt explain that we can only speculate.
+We are going to choose the model with five degrees of freedom.
+So we arrived at the following model.
+Double spacing makes this dificult
+$$\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +$$
+$$ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon$$
+```{r message=FALSE}
+size <- 18
+a <- data %>% 
+  ggplot(aes(x = corruption_perception_index_cpi, y = polrights_fh)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
+  scale_y_continuous(breaks = 1:7) + 
+  labs(x = "Corruption Perception", y = "Political Rights") +
+  theme_light(base_size = size)
+
+b <- data %>% 
+  ggplot(aes(x = edu_exp_gdp_per_person, y = polrights_fh)) + 
+  geom_point() + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
+    scale_y_continuous(breaks = 1:7) + 
+  labs(x = "Education Expendature", y = "") +
+  theme_light(base_size = size)
+
+c <- data %>% 
+  ggplot(aes(x = life_expectancy_years, y = polrights_fh)) + 
+  geom_point()+ 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
+    scale_y_continuous(breaks = 1:7) + 
+  labs(x = "Life Expectacy", y = "") +
+  theme_light(base_size = size)
+
+d <- data %>% 
+  ggplot(aes(x = military_spending_pct_of_gdp, y = polrights_fh)) + 
+  geom_point()+ 
+  scale_y_continuous(breaks = 1:7) + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
+  labs(x = "Military Spending", y = "")+ theme_light(base_size = size)
+
+e <- data %>% 
+  ggplot(aes(x = murder_per_mil_people, y = polrights_fh)) + 
+  geom_point() + 
+  scale_y_continuous(breaks = 1:7) + 
+  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
+  labs(x = "Murder Rate", y = "") + theme_light(base_size = size)
+
+(a + b) / (c + d + e) 
+```
+The scatter plots look a bit strange at first because of the nature of the discrete response variable.
+However, this does seem to fit the data reasonably.
+There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coeffeceintes.
+
 ## Remeidal Measures
+Now we will examine some remedial measures to analyze the performance and identify problems. 
+Let's start with plots of residuals.
+Figure 2, contains a histogram of the residuals adjcent to a QQ normal plot.
+It is clear that there are substantial outliers at the lower end of political freedom.
+Upon further inspection found that these outliers are turkey from 2016 to 2018.
+These residuals are large and suggest a substancial loss in political freedom.
+This is confirmed by Freedomhouse [@Freedomhouse] reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
+After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reasion to eliminate it.
+It was clear to us that there is substancial error variance and likely not constant from the posative residuals to negtive residuals.
+A Brown-Forsythe test confirmed our suspicians telling us that the error variance is significantly higher when the residuals are negative.
+This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
+
+```{r fig.show="hold", out.width="50%"}
+fit_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(.resid)) + 
+  geom_histogram(bins = 75, fill = "black") +
+  scale_x_continuous(limits = c(-4,4)) + 
+  labs(y = "Density", x = "Residual", title = "Histogram") + 
+  theme_light(base_size = size + 10)
+
+fit_df5 %>% 
+  broom::augment() %>% 
+  ggplot(aes(sample = .resid)) + 
+  stat_qq() +
+  stat_qq_line(color = "#3C989E", size = 3) + 
+scale_x_continuous(limits = c(-4,4)) + 
+scale_y_continuous(limits = c(-4,4)) + 
+  labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected") + 
+  theme_light(base_size = size + 10)
+```
 
 ## Conclusion
+
+The results are statistically significant but can only be interpreted for countries in the OECD.
+The model does a reasonably good job predicting political freedom in the 6 and 7 range.
+However, completely falls apart at the one case of a substantial loss in freedom.
+Again, we don't have an exhaustive sample of countries losing freedom so this is consistent with the dataset we have.
+However, we can conclude as one of our more robust results is that an increase in education expenditure is associated with an increase in political freedom.
+The less corrupt a country is perceived to be the more freedom the citizens are afforded.
+Military spending is associated with a decrease in political freedom.
 
@@
 
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
 
-<div id="refs" custom-style="Bibliography"></div>
 \endgroup
+
+\newpage
+# Appendix: All code for this report
+
+```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
+```
+
+```{r include=FALSE}
+beepr::beep()
+```

### 2020-11-25 paper/paper.tex
done for the day

@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 \makeatother
-\shorttitle{RUNNING HEAD: Political Freedom Within the OECD}
+\shorttitle{Political Freedom Within the OECD}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
+\cftpagenumbersoff{table}
+\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
+\renewcommand{\cfttabaftersnum}{.\space}
+\setlength{\cfttabindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifxetex
@@
 \author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
-\date{Last compiled 18:41}
+\date{Last compiled 20:41}
 
@@
 based think tank and research institute, attempts this by assigning a index of political rights to each country every year based on a fixed criteria.
+Using the Papaja Package by (Aust \& Barth, 2020) package we take rmarkdown directly to APA format.
 
-The Political Rights Index is comprised of three subcategories.
+The \textbf{Political Rights} Index is comprised of three subcategories.
 Electoral process, political participation, and functioning government.
@@
 This will serve as a reasonable measure of political freedom around the world and will serve as an adequate sample to study political freedom.
-We obtained this from the Gapminder Foundation Rosling (2020), a non-profit organization that studies and promotes economic development.
+We obtained this from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
@@
 
-These data sets were separate so we downloaded them individually, cleaned and combined them together using R R Core Team (2020) and the Tidyverse Package Wickham et al.
-(2019).
+These data sets were separate so we downloaded them individually, cleaned and combined them together using R (R Core Team, 2020) and the Tidyverse Package (Wickham et al., 2019).
 This resulted in a data set with all 196 countries form years 1950 to 2030 (data after 2019 were projections).
@@
 
-Table 1 made with the Zhu (2020) contains Basic summary statistics from our dataset.
+Table 1 made with the (Zhu, 2020) contains Basic summary statistics from our dataset.
 We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
@@
 This lead us to choose between the following models.
-From the graph of the subsets we can see that the increase in \(R^2\) and \(AIC\) by adding additional paramaters.
+From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.
 
@@
 \end{figure}
-
-\hypertarget{model}{%
-\subsection{Model}\label{model}}
-
-\(\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) + \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\)
-
-(chart here)
-
-The model that displayed the most statistical sense in conjuction with our exsistin inutitions is.
-(formula here)
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-See table 1 made in stargazer Hlavac (2018)
 
@@
 \hline \\[-1.8ex] 
- (Intercept) & $-$0.023$^{***}$ & $-$0.023$^{***}$ & $-$0.022$^{***}$ \\ 
+ Corruption Perception & $-$0.023$^{***}$ & $-$0.023$^{***}$ & $-$0.022$^{***}$ \\ 
   & (0.002) & (0.002) & (0.002) \\ 
-  Corruption Perception & 1.746$^{***}$ & 1.900$^{***}$ & 1.898$^{***}$ \\ 
+  Education Expendature & 1.746$^{***}$ & 1.900$^{***}$ & 1.898$^{***}$ \\ 
   & (0.562) & (0.534) & (0.536) \\ 
-  Education Expendature & 0.001 &  &  \\ 
+  Internet Users & 0.001 &  &  \\ 
   & (0.001) &  &  \\ 
@@
   & (0.004) & (0.004) & (0.004) \\ 
-  Constant & 9.212$^{***}$ & 8.979$^{***}$ & 7.284$^{***}$ \\ 
+  Intercept & 9.212$^{***}$ & 8.979$^{***}$ & 7.284$^{***}$ \\ 
   & (0.742) & (0.692) & (0.123) \\ 
@@
 
+\hypertarget{model-selection}{%
+\subsection{Model Selection}\label{model-selection}}
+
+From the best subsets, it was appropriate to narrow our model choices down to three.
+First, the model with six degrees of freedom, next one with five, and one with four.
+The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018) on the next page.
+The model with six degrees of freedom contains \textbf{Internet Users} which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way.
+Looking at the model with five degrees of freedom, all of our coefficients are statistically significant at \(p < 0.01\).
+The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
+Counterintuitively, politically freedom seems to decrease as life expectancy increases.
+We are not qualified to attempt explain that we can only speculate.
+We are going to choose the model with five degrees of freedom.
+So we arrived at the following model.\\
+Double spacing makes this dificult
+\[\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\]
+\[ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\]
+\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
+The scatter plots look a bit strange at first because of the nature of the discrete response variable.
+However, this does seem to fit the data reasonably.
+There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coeffeceintes.
+
 \hypertarget{remeidal-measures}{%
@@
 
+Now we will examine some remedial measures to analyze the performance and identify problems.
+Let's start with plots of residuals.
+Figure 2, contains a histogram of the residuals adjcent to a QQ normal plot.
+It is clear that there are substantial outliers at the lower end of political freedom.
+Upon further inspection found that these outliers are turkey from 2016 to 2018.
+These residuals are large and suggest a substancial loss in political freedom.
+This is confirmed by Freedomhouse (\emph{Countries and Territories}, 2020) reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
+After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reasion to eliminate it.\\
+It was clear to us that there is substancial error variance and likely not constant from the posative residuals to negtive residuals.
+A Brown-Forsythe test confirmed our suspicians telling us that the error variance is significantly higher when the residuals are negative.
+This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
+
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-5-2} \caption{ }\label{fig:unnamed-chunk-5}
+\end{figure}
+
 \hypertarget{conclusion}{%
 \subsection{Conclusion}\label{conclusion}}
+
+The results are statistically significant but can only be interpreted for countries in the OECD.
+The model does a reasonably good job predicting political freedom in the 6 and 7 range.
+However, completely falls apart at the one case of a substantial loss in freedom.
+Again, we don't have an exhaustive sample of countries losing freedom so this is consistent with the dataset we have.
+However, we can conclude as one of our more robust results is that an increase in education expenditure is associated with an increase in political freedom.
+The less corrupt a country is perceived to be the more freedom the citizens are afforded.
+Military spending is associated with a decrease in political freedom.
 
@@
 \begin{cslreferences}
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
 \leavevmode\hypertarget{ref-Freedomhouse}{}%
@@
 
+\newpage
+
+\hypertarget{appendix-all-code-for-this-report}{%
+\section{Appendix: All code for this report}\label{appendix-all-code-for-this-report}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{library}\NormalTok{(tidyverse)}
+\KeywordTok{library}\NormalTok{(kableExtra)}
+\KeywordTok{library}\NormalTok{(stargazer)}
+\KeywordTok{library}\NormalTok{(patchwork)}
+\NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}
+
+\KeywordTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
+\KeywordTok{r\_refs}\NormalTok{(}\StringTok{"r{-}references.bib"}\NormalTok{)}
+
+\NormalTok{knitr}\OperatorTok{::}\NormalTok{opts\_chunk}\OperatorTok{$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{echo =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{warning=}\OtherTok{FALSE}\NormalTok{, }\DataTypeTok{message =} \OtherTok{FALSE}\NormalTok{, }
+                      \DataTypeTok{fig.width =} \DecValTok{12}\NormalTok{, }\DataTypeTok{fig.height =} \DecValTok{8}\NormalTok{) }
+
+\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{readr}\OperatorTok{::}\KeywordTok{read\_csv}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"df.csv"}\NormalTok{)) }
+\NormalTok{subsets \textless{}{-}}\StringTok{ }\NormalTok{readr}\OperatorTok{::}\KeywordTok{read\_csv}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"subsets.csv"}\NormalTok{))}
+\NormalTok{model\_df6\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{6}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }
+
+\NormalTok{fit\_df6 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df6\_formula, data)}
+
+\NormalTok{model\_df5\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{5}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{()}
+
+\NormalTok{fit\_df5 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df5\_formula, data)}
+
+\NormalTok{model\_df4\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }
+
+\NormalTok{fit\_df4 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df4\_formula, data)}
+\NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{df =}\NormalTok{ data, x, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
+
+\NormalTok{    x \textless{}{-}}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{enquo}\NormalTok{(x)}
+\NormalTok{    df }\OperatorTok{\%\textgreater{}\%}
+\StringTok{      }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{summarise}\NormalTok{(}
+                       \DataTypeTok{Mean  =} \KeywordTok{mean}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
+                     \DataTypeTok{Median  =} \KeywordTok{median}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
+                         \DataTypeTok{Std =} \KeywordTok{sd}\NormalTok{  ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
+                         \DataTypeTok{Min =} \KeywordTok{min}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
+                         \DataTypeTok{Max =} \KeywordTok{max}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
+                       \DataTypeTok{Range =} \KeywordTok{max}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) }\OperatorTok{{-}}\StringTok{ }\KeywordTok{min}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) ) }\OperatorTok{\%\textgreater{}\%}
+\StringTok{      }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
+\NormalTok{  \}}
+
+\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\KeywordTok{stat}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data)\}) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Variable =} \KeywordTok{replace}\NormalTok{(Variable, }
+                            \DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\StringTok{"Political Rights"}\NormalTok{, }\StringTok{"Year"}\NormalTok{, }
+                                       \StringTok{"Corruption Perception"}\NormalTok{, }
+                                       \StringTok{"Education Expenditure"}\NormalTok{, }
+                                       \StringTok{"Electricity Use"}\NormalTok{, }
+                                       \StringTok{"Gini"}\NormalTok{, }
+                                       \StringTok{"Internet Users"}\NormalTok{,}
+                                       \StringTok{"Life Expectancy"}\NormalTok{, }
+                                       \StringTok{"Labor Force Participation"}\NormalTok{, }
+                                       \StringTok{"Military Spending"}\NormalTok{, }
+                                       \StringTok{"Murders rate"}\NormalTok{))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\KeywordTok{kable}\NormalTok{(}
+  \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{,}
+  \DataTypeTok{booktabs =} \OtherTok{TRUE}\NormalTok{,}
+  \DataTypeTok{escape =} \OtherTok{FALSE}\NormalTok{,}
+  \DataTypeTok{longtable =} \OtherTok{TRUE}\NormalTok{,}
+ \DataTypeTok{caption =} \StringTok{"Descriptive Statistics"}\NormalTok{)}
+\NormalTok{r \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{group\_by}\NormalTok{(df) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{adj =} \KeywordTok{max}\NormalTok{(adj.r.squared, }\DataTypeTok{na.rm =}\NormalTok{ T))}
+
+\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df, }\DataTypeTok{y =}\NormalTok{ adj.r.squared)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ r, }\KeywordTok{aes}\NormalTok{(df, adj), }
+              \DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{span =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{""}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Adjusted R Squared"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{theme\_test}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }
+
+\NormalTok{r \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{group\_by}\NormalTok{(df) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{AIC =} \KeywordTok{max}\NormalTok{(AIC, }\DataTypeTok{na.rm =}\NormalTok{ T))}
+
+\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df, }\DataTypeTok{y =}\NormalTok{ AIC)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ r, }\KeywordTok{aes}\NormalTok{(df, AIC), }
+              \DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{span =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{""}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"AIC"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{theme\_test}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }
+
+\KeywordTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }\DataTypeTok{type =} \StringTok{"latex"}\NormalTok{, }
+                     \DataTypeTok{title =} \StringTok{"Regression Results"}\NormalTok{, }
+                     \DataTypeTok{covariate.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Corruption Perception"}\NormalTok{, }\StringTok{"Education Expendature"}\NormalTok{,}
+                                          \StringTok{"Internet Users"}\NormalTok{, }\StringTok{"Life Expectancy"}\NormalTok{,}
+                                          \StringTok{"Military Spending"}\NormalTok{, }\StringTok{"Murder Rate"}\NormalTok{, }
+                                          \StringTok{"Intercept"}\NormalTok{),}
+                     \DataTypeTok{dep.var.caption =} \StringTok{"Political Rights Index"}\NormalTok{,}
+                     \DataTypeTok{dep.var.labels =} \OtherTok{NULL}\NormalTok{,}
+                     \DataTypeTok{dep.var.labels.include =} \OtherTok{FALSE}\NormalTok{, }
+                     \DataTypeTok{model.names =} \OtherTok{FALSE}\NormalTok{,}
+                     \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
+                     \DataTypeTok{df =} \OtherTok{FALSE}\NormalTok{, }
+                     \DataTypeTok{header =} \OtherTok{FALSE}\NormalTok{,}
+                     \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"DF = 6"}\NormalTok{, }\StringTok{"DF = 5"}\NormalTok{, }\StringTok{"DF = 4"}\NormalTok{),}
+                     \DataTypeTok{no.space =} \OtherTok{TRUE}\NormalTok{)}
+\NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{18}
+\NormalTok{a \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ corruption\_perception\_index\_cpi, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Corruption Perception"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Political Rights"}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+
+\NormalTok{b \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ edu\_exp\_gdp\_per\_person, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}
+\StringTok{    }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Education Expendature"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+
+\NormalTok{c \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ life\_expectancy\_years, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{()}\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}
+\StringTok{    }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Life Expectacy"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+
+\NormalTok{d \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ military\_spending\_pct\_of\_gdp, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{()}\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Military Spending"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+
+\NormalTok{e \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ murder\_per\_mil\_people, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Murder Rate"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+
+\NormalTok{(a }\OperatorTok{+}\StringTok{ }\NormalTok{b) }\OperatorTok{/}\StringTok{ }\NormalTok{(c }\OperatorTok{+}\StringTok{ }\NormalTok{d }\OperatorTok{+}\StringTok{ }\NormalTok{e) }
+\NormalTok{fit\_df5 }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\NormalTok{broom}\OperatorTok{::}\KeywordTok{augment}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(.resid)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{geom\_histogram}\NormalTok{(}\DataTypeTok{bins =} \DecValTok{75}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"black"}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Density"}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Residual"}\NormalTok{, }\DataTypeTok{title =} \StringTok{"Histogram"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size }\OperatorTok{+}\StringTok{ }\DecValTok{10}\NormalTok{)}
+
+\NormalTok{fit\_df5 }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\NormalTok{broom}\OperatorTok{::}\KeywordTok{augment}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{sample =}\NormalTok{ .resid)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{stat\_qq}\NormalTok{() }\OperatorTok{+}
+\StringTok{  }\KeywordTok{stat\_qq\_line}\NormalTok{(}\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{3}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
+\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"QQ Plot of Residuals "}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Residual"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Expected"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size }\OperatorTok{+}\StringTok{ }\DecValTok{10}\NormalTok{)}
+\NormalTok{beepr}\OperatorTok{::}\KeywordTok{beep}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\clearpage
+\renewcommand{\listfigurename}{Figure captions}
+
+\clearpage
+\renewcommand{\listtablename}{Table captions}
+
 \end{document}

### 2020-11-25 R/best_subset_selection.R

@@ -4,8 +4,6 @@ library(tidyverse)
 
 data <- read_csv(here::here("data", "df.csv"))
 
-names(data)
-
 vars <- data %>% 
   select(-country, -year, -ends_with("_fh")) %>%
   names()
@@ -16,16 +14,11 @@ models <- list()
 for (i in 1:length(vars)) {
   vc <- combn(vars,i)
   for (j in 1:ncol(vc)) {
-    for(k in 1:ncol(vc)){
-    if(k == j){
     model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
-    }else{
-    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j],"*", vc[,k], collapse = " + ")))
-    }
     models <- c(models, model)
+    
     }
   }
-}
 
 subsets <- map(models, function(x) lm(x, data)) %>% 
   map(broom::glance) %>% 

### 2020-11-25 R/cleaningscript.R

@@ -16,7 +16,7 @@ data <- files %>%
 
 # Filtering ---------------------------------------------------------------
 
-countries <- readRDS(here::here("data", "countries.RDS"))[15:51]
+countries <- readRDS(here::here("data", "countries.RDS"))
 
 
 data <- data %>%

### 2020-11-25 paper/paper.Rmd
fixed issue

@@
 
-```{r setup, include = FALSE}
+```{r setup}
 library(tidyverse)
@@
 library(patchwork)
+
 size <- 30
@@
                       fig.width = 12, fig.height = 8) 
+```
+
+```{r, cache=TRUE}
 
@@
 # Iceland spent 0 so I needed to manually recode that
-  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
+  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0), 
+         year = as.numeric(year)) %>% 
   mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
@@
          # lose 3 important countries in LA
-  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
-                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)%>% 
-  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1)
+  relocate(polrights_fh) %>% 
+  mutate(polrights_fh = (8 - polrights_fh),
+                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100) %>% 
+  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1) %>% 
+  ungroup()
 
@@
 ```{r fig.align="center", results='asis'}
-stat <- function(df = data, x, rounding_digits = 2){
+stat <- function(x, df = data, rounding_digits = 2){
 
-    x <- dplyr::enquo(x)
+    x <- enquo(x)
     df %>%
-      dplyr::summarise(
+      summarise(
                        Mean  = mean( !! x),
@@
                        Range = max(!! x) - min(!! x) ) %>%
-      dplyr::mutate_if(is.numeric, round, rounding_digits)
+      mutate_if(is.numeric, round, rounding_digits)
 }
@@
   select(-country) %>% 
-map(function(x){stat(x, df = data)}) %>% 
+map(function(x){stat(x)}) %>% 
   bind_rows(.id = "Variable") %>% 
@@
                      title = "Regression Results", 
-                     covariate.labels = c("Corruption Perception", "Education Expendature",
-                                          "Internet Users", "Life Expectancy",
-                                          "Military Spending", "Murder Rate", 
+                     covariate.labels = c("Corruption Perception", 
+                                          "Education Expendature",
+                                          "Internet Users", 
+                                          "Life Expectancy",
+                                          "Military Spending", 
+                                          "Murder Rate", 
                                           "Intercept"),

### 2020-11-25 paper/paper.tex
fixed issue

@@
 \author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
-\date{Last compiled 20:41}
+\date{Last compiled 21:15}
 
@@
 \begin{longtable}[t]{lrrrrrr}
-\caption{\label{tab:unnamed-chunk-1}Descriptive Statistics}\\
+\caption{\label{tab:unnamed-chunk-2}Descriptive Statistics}\\
 \toprule
@@
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-2-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-2-2} \caption{ }\label{fig:unnamed-chunk-2}
+\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-3-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-3-2} \caption{ }\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 \[ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\]
-\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
 The scatter plots look a bit strange at first because of the nature of the discrete response variable.
@@
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-5-2} \caption{ }\label{fig:unnamed-chunk-5}
+\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-6-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-6-2} \caption{ }\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 \KeywordTok{library}\NormalTok{(patchwork)}
+
 \NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}
@@
 
-\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{readr}\OperatorTok{::}\KeywordTok{read\_csv}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"df.csv"}\NormalTok{)) }
-\NormalTok{subsets \textless{}{-}}\StringTok{ }\NormalTok{readr}\OperatorTok{::}\KeywordTok{read\_csv}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"subsets.csv"}\NormalTok{))}
+\CommentTok{\# Read and Clean {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\NormalTok{files \textless{}{-}}\StringTok{ }\KeywordTok{list.files}\NormalTok{(}\DataTypeTok{path =}\NormalTok{ here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"raw\_data"}\NormalTok{), }\DataTypeTok{pattern =} \StringTok{".csv"}\NormalTok{)}
+
+\NormalTok{cleaning \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(df)\{}
+\NormalTok{  df \textless{}{-}}\StringTok{ }\KeywordTok{pivot\_longer}\NormalTok{(df, }\DataTypeTok{cols =} \OperatorTok{{-}}\NormalTok{country, }\DataTypeTok{names\_to =} \StringTok{"year"}\NormalTok{)}
+\NormalTok{\}}
+
+\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{files }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{read\_csv}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(}\StringTok{"raw\_data/"}\NormalTok{, x))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{setNames}\NormalTok{(}\KeywordTok{gsub}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{.csv$"}\NormalTok{, }\StringTok{""}\NormalTok{, files)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{map}\NormalTok{(cleaning) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{pivot\_wider}\NormalTok{(}\DataTypeTok{names\_from =}\NormalTok{ id)}
+
+\CommentTok{\# Filtering {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+
+\NormalTok{countries \textless{}{-}}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"countries.RDS"}\NormalTok{))}
+
+\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}
+\StringTok{  }\KeywordTok{filter}\NormalTok{(year }\OperatorTok{\textgreater{}}\StringTok{ }\DecValTok{2000}\NormalTok{, year }\OperatorTok{\textless{}}\StringTok{ }\DecValTok{2019}\NormalTok{, country }\OperatorTok{\%in\%}\StringTok{ }\NormalTok{countries) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{group\_by}\NormalTok{(country) }\OperatorTok{\%\textgreater{}\%}
+\StringTok{  }\KeywordTok{mutate\_at}\NormalTok{(}\KeywordTok{vars}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country),}\KeywordTok{list}\NormalTok{(}\OperatorTok{\textasciitilde{}}\KeywordTok{ifelse}\NormalTok{(}\KeywordTok{is.na}\NormalTok{(.), }\KeywordTok{median}\NormalTok{(., }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{), .))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\CommentTok{\# Iceland spent 0 so I needed to manually recode that}
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{military\_spending\_pct\_of\_gdp =} \KeywordTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{), }
+         \DataTypeTok{year =} \KeywordTok{as.numeric}\NormalTok{(year)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
+         \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Chile"}\NormalTok{, }\FloatTok{4.4}\NormalTok{),}
+         \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Colombia"}\NormalTok{, }\FloatTok{25.34}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{         }\CommentTok{\# https://en.wikipedia.org/wiki/List\_of\_countries\_by\_intentional\_homicide\_rate}
+\StringTok{         }\CommentTok{\# these murder rates were not included in the gapminder but i didnt want to }
+\StringTok{         }\CommentTok{\# lose 3 important countries in LA}
+\StringTok{  }\KeywordTok{relocate}\NormalTok{(polrights\_fh) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{polrights\_fh =}\NormalTok{ (}\DecValTok{8} \OperatorTok{{-}}\StringTok{ }\NormalTok{polrights\_fh),}
+                                    \DataTypeTok{military\_spending\_pct\_of\_gdp =}\NormalTok{ military\_spending\_pct\_of\_gdp }\OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (corruption\_perception\_index\_cpi }\OperatorTok{{-}}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{*}\StringTok{ }\DecValTok{{-}1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{ungroup}\NormalTok{()}
+
+\CommentTok{\# Best Subset Selection {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+
+\NormalTok{vars \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country, }\OperatorTok{{-}}\NormalTok{year, }\OperatorTok{{-}}\KeywordTok{ends\_with}\NormalTok{(}\StringTok{"\_fh"}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}
+\StringTok{  }\KeywordTok{names}\NormalTok{()}
+
+\NormalTok{outcome \textless{}{-}}\StringTok{ "polrights\_fh"}
+
+\NormalTok{models \textless{}{-}}\StringTok{ }\KeywordTok{list}\NormalTok{()}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(vars)) \{}
+\NormalTok{  vc \textless{}{-}}\StringTok{ }\KeywordTok{combn}\NormalTok{(vars,i)}
+  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(vc)) \{}
+\NormalTok{    model \textless{}{-}}\StringTok{ }\KeywordTok{as.formula}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(outcome, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\KeywordTok{paste0}\NormalTok{(vc[,j], }\DataTypeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
+\NormalTok{    models \textless{}{-}}\StringTok{ }\KeywordTok{c}\NormalTok{(models, model)}
+
+\NormalTok{    \}}
+\NormalTok{  \}}
+
+\NormalTok{subsets \textless{}{-}}\StringTok{ }\KeywordTok{map}\NormalTok{(models, }\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{lm}\NormalTok{(x, data)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{map}\NormalTok{(broom}\OperatorTok{::}\NormalTok{glance) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{setNames}\NormalTok{(models) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{distinct}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ id) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
+    \DataTypeTok{Model =} \KeywordTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
+    \DataTypeTok{Model =} \KeywordTok{str\_replace}\NormalTok{(Model, }\StringTok{"\textasciitilde{}"}\NormalTok{, }\StringTok{"="}\NormalTok{), }
+    \DataTypeTok{Model =} \KeywordTok{str\_to\_title}\NormalTok{(Model))}
 \NormalTok{model\_df6\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{6}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \NormalTok{fit\_df4 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df4\_formula, data)}
-\NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{df =}\NormalTok{ data, x, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
+\NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
 
-\NormalTok{    x \textless{}{-}}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{enquo}\NormalTok{(x)}
+\NormalTok{    x \textless{}{-}}\StringTok{ }\KeywordTok{enquo}\NormalTok{(x)}
 \NormalTok{    df }\OperatorTok{\%\textgreater{}\%}
-\StringTok{      }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{summarise}\NormalTok{(}
+\StringTok{      }\KeywordTok{summarise}\NormalTok{(}
                        \DataTypeTok{Mean  =} \KeywordTok{mean}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
@@
                        \DataTypeTok{Range =} \KeywordTok{max}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) }\OperatorTok{{-}}\StringTok{ }\KeywordTok{min}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) ) }\OperatorTok{\%\textgreater{}\%}
-\StringTok{      }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
-\NormalTok{  \}}
+\StringTok{      }\KeywordTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
+\NormalTok{\}}
 
@@
 \StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\KeywordTok{stat}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data)\}) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\KeywordTok{stat}\NormalTok{(x)\}) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
 \StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
                      \DataTypeTok{title =} \StringTok{"Regression Results"}\NormalTok{, }
-                     \DataTypeTok{covariate.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Corruption Perception"}\NormalTok{, }\StringTok{"Education Expendature"}\NormalTok{,}
-                                          \StringTok{"Internet Users"}\NormalTok{, }\StringTok{"Life Expectancy"}\NormalTok{,}
-                                          \StringTok{"Military Spending"}\NormalTok{, }\StringTok{"Murder Rate"}\NormalTok{, }
+                     \DataTypeTok{covariate.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Corruption Perception"}\NormalTok{, }
+                                          \StringTok{"Education Expendature"}\NormalTok{,}
+                                          \StringTok{"Internet Users"}\NormalTok{, }
+                                          \StringTok{"Life Expectancy"}\NormalTok{,}
+                                          \StringTok{"Military Spending"}\NormalTok{, }
+                                          \StringTok{"Murder Rate"}\NormalTok{, }
                                           \StringTok{"Intercept"}\NormalTok{),}

### 2020-11-25 paper/paper.Rmd
added date

@@
   - name          : "Joe Despres"
-    affiliation   : "1"
+    affiliation   : ""
     corresponding : yes    # Define only one corresponding author
   - name          : "Sabrina Ball"
-    affiliation   : "1"
+    affiliation   : ""
   - name          : "Jacob Haywood"
-    affiliation   : "1"
+    affiliation   : ""
   - name          : "Joe Sigler"
-    affiliation   : "1"
+    affiliation   : ""
 
 affiliation:
-  - id            : "1"
-    institution   : "Michigan State University"
+  - id            : ""
+    institution   : "Michigan State University  \n  November 30, 2020"
 
-date: 
-  - "Last compiled `r format(Sys.time(), '%H:%M')`"
-
-keywords          : "keywords"
+keywords          : "keyword"
 wordcount         : "X"

### 2020-11-25 paper/paper.tex
added date

@@
   pdftitle={Identifying Factors That Affect Political Freedom Within the OECD},
-  pdfauthor={Joe Despres1, Sabrina Ball1, Jacob Haywood1, \& Joe Sigler1},
+  pdfauthor={Joe Despres, Sabrina Ball, Jacob Haywood, \& Joe Sigler},
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={keyword},
   hidelinks,
@@
 \shorttitle{Political Freedom Within the OECD}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{keyword\newline\indent Word count: X}
 \usepackage{lineno}
@@
 \title{Identifying Factors That Affect Political Freedom Within the OECD}
-\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
-\date{Last compiled 21:15}
+\author{Joe Despres\textsuperscript{}, Sabrina Ball\textsuperscript{}, Jacob Haywood\textsuperscript{}, \& Joe Sigler\textsuperscript{}}
+\date{}
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Michigan State University}
+\affiliation{\vspace{0.5cm}\textsuperscript{} Michigan State University\\
+November 30, 2020}
 

### 2020-11-25 paper/paper.Rmd
made adjustments

@@
 floatsintext      : yes
-figurelist        : yes
-tablelist         : yes
+figurelist        : no
+tablelist         : no
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 library(patchwork)
-
 size <- 30
-
 library("papaja")
 r_refs("r-references.bib")
-
 knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, 
@@
 ```{r, cache=TRUE}
-
 # Read and Clean ----------------------------------------------------------
 files <- list.files(path = here::here("raw_data"), pattern = ".csv")
-
 cleaning <- function(df){
@@
 }
-
 data <- files %>% 
@@
 # Filtering ---------------------------------------------------------------
-
 countries <- readRDS(here::here("data", "countries.RDS"))
-
 data <- data %>%
-  filter(year > 2000, year < 2019, country %in% countries) %>% 
+  mutate(year = as.numeric(year)) %>% 
+  filter(year >= 2000, year < 2019, country %in% countries) %>% 
   group_by(country) %>%
@@
   mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0),
-         year = as.numeric(year)) %>% 
-  mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
+  murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
          murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
          murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
-         # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
-         # these murder rates were not included in the gapminder but i didnt want to 
-         # lose 3 important countries in LA
   relocate(polrights_fh) %>% 
@@
  military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100) %>% 
-  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1) %>% 
+  mutate(corruption_perception_index_cpi = (100 - corruption_perception_index_cpi)) %>% 
   ungroup()
-
 # Best Subset Selection ---------------------------------------------------------------
-
 vars <- data %>% 
@@
   names()
-
-outcome <- "polrights_fh"
-
 models <- list()
@@
   for (j in 1:ncol(vc)) {
-    model <- as.formula(paste0(outcome, " ~", paste0(vc[,j], collapse = " + ")))
+    model <- as.formula(paste0("polrights_fh", " ~", paste0(vc[,j], collapse = " + ")))
     models <- c(models, model)
-
     }
   }
-
 subsets <- map(models, function(x) lm(x, data)) %>% 
@@
   bind_rows(.id = "id") %>% 
-  distinct() %>% 
   rename(model = id) %>% 
-  mutate(
-    Model = str_replace_all(model, "_", " "),
+  mutate(Model = str_replace_all(model, "_", " "),
          Model = str_replace(Model, "~", "="), 
@@
   select(model) %>% head(1) %>% as.character() 
-
 fit_df6 <- lm(model_df6_formula, data)
-
 model_df5_formula <- subsets %>% filter(df == 5) %>% 
@@
   select(model) %>% head(1) %>% as.character()
-
 fit_df5 <- lm(model_df5_formula, data)
-
 model_df4_formula <- subsets %>% filter(df == 4) %>% 
@@
   select(model) %>% head(1) %>% as.character() 
-
 fit_df4 <- lm(model_df4_formula, data)
@@
 Political freedom is an abstract concept that does not lend well to quantification.
-However, Freedom House [@Freedomhouse], a U.S.
-based think tank and research institute, attempts this by assigning a index of political rights to each country every year based on a fixed criteria.
-Using the Papaja Package by [@R-papaja] package we take rmarkdown directly to APA format.
+However, Freedomhouse [@Freedomhouse], a U.S.
+based think tank and research institute, attempts this by assigning an index of political rights to each country every year based on a fixed criteria.
+Using the Papaja Package by [@R-papaja] we take Rmarkdown directly to APA format.
 
@@
 Electoral process is a score based on how the current government leaders were selected.
-How fairly the positions was obtained and kept.
+How fairly the positions were obtained and kept.
 As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
-Political Participation is evaluated on four criteria, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
-Functioning government, is the current heads of government determine policies, safeguards against corruption, and openness and transparency of government operation.
-Political freedom has been measured in this manner for every country from the years 1978 to present.
+Political Participation is evaluated on four criterion, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Functioning government, measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
+Freedom house has measured political freedom in this manner for every country from the years 1978 to present.
 
-Although such a metric is far from perfect.
-This will serve as a reasonable measure of political freedom around the world and will serve as an adequate sample to study political freedom.
-We obtained this from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
+Although such a metric is far from perfect and often debatable, this will serve as a reasonable measure of political freedom around the world to study political freedom.
+We obtained the dataset from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
-To explain a country's political rights index we selected: Corruption Perception Index, Education Expenditure, Electricity Use, Gini Coefficient, Internet Users as a percentage, Labor Force Participation Rate, Military Spending as percentage of GDP, and Murders per million.
+To explain a country's political rights index we selected: **Corruption Perception Index**, **Education Expenditure**, **Electricity Use**, **Gini Coefficient**, **Internet Users** as a percentage, **Labor Force Participation** Rate, **Military Spending** as percentage of GDP, and **Murders** per million.
 
@@
 These data sets were separate so we downloaded them individually, cleaned and combined them together using R [@R-base] and the Tidyverse Package [@R-tidyverse].
-This resulted in a data set with all 196 countries form years 1950 to 2030 (data after 2019 were projections).
+This resulted in a data set with all 196 countries from years 1950 to 2030 (data after 2019 were projections).
 It was immediately apparent that there was a substantial amount of missing data in an obvious pattern.
-Less developed countries tended to have more missing data points.
-Also, the further back in time the more missing data points.
+Less developed countries tended to have more missing data points, and the further back in time the more missing data.
 Had we conducted this study as it was it would have been severely biased towards more developed countries as missing data points would be dropped.
 This forced us to narrow the scope of the study and focus only on countries within the Organization for Economic Co-operation and Development (OECD).
-This subset of countries has a reasonably complete data.
+This subset of countries has reasonably complete data.
 Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
@@
 This remedied most of the missing datapoints.
-However, even within the OEDC there were sparse few missing data points.
+However, even within the OEDC there were a few missing data points.
 From there, we imputed the median of each country's variable.
-For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period.
-Which afforded us the ability to keep even more data with minimal compromise.
+For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period and inputted it where there was an NA.
+This afforded us the ability to keep even more data with minimal compromise.
 This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
 After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0% of their GDP, so we replaced the NA with a 0.
-This afforded us a full data set with no missing data points.
+This is how we obtained a complete and full data set with no missing data points.
 The only other adjustment made was to make a few of the variables more intuitive.
 Corruption perception for example was originally having 0 be the most perception of corruption and 100 being the least.
-For us we wanted to have a more intuitve interpretation so we subtracted 100 and mulitplied by negaitve one.
+We wanted to have a more intuitive interpretation so we subtracted 100 and multiplied by negative one.
+This gives us an interpretation of of 0 being the least corrupt and 100 the most corrupt.
+We did the same for political rights, which originally 1 was the most political freedom and 7 being the least.
+We want to interpret a higher number to having more political rights.
 
@@
 stat <- function(x, df = data, rounding_digits = 2){
-
     x <- enquo(x)
@@
 }
-
 data %>% 
@@
 
-Table 1 made with the [@R-kableExtra] contains Basic summary statistics from our dataset.
+Table 1, made with the KableExtra package [@R-kableExtra] contains basic summary statistics from our dataset.
 We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
 This is not ideal.
-We would much prefer that it was continuous with a substantial variation.
-First, the methodology of rather than taking continuous values Freedomhouse's classification is discrete classifying countries political rights taking values of the integers 1-7.
-Secondly countries with a low political rights by nature have a suspect data reporting process.
-Which is why we had to select a subset of countries and that subset leans towards having more political freedom.
+Freedomhouse's classification of political freedom is in discrete values from 1-7.
+Additionally, countries with a low political freedom have suspect data reporting.
+We had to select a subset of countries and that subset leans towards having more political freedom.
 We precede on the understanding that there are moderate problems with the data, first having a discrete response variable and the nature of the distribution being skewed towards the maximum 7/7 political freedom.
-
-With such considerations taken into account, we will not be making any non-linear transformation or variables.
-First, we examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
-With a clean, complete, and dataset that is contains flaws but is still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
-This lead us to choose between the following models.
-From the graph of the subsets we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
 
@@
   scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = size)
+  theme_test(base_size = size) + labs(title = "Best Subset Selection")
 
@@
 
+We examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+We will not be making any non-linear transformation or variables.
+With a dataset that contains flaws but still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
+This lead us to choose between the following models.
+From the graph of the subsets we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
+
+## Model Selection
 ```{r results="asis"}
-stargazer(fit_df6, fit_df5, fit_df4, type = "latex", 
+stargazer(fit_df6, fit_df5, fit_df4, 
+                     type = "latex", 
                      title = "Regression Results", 
@@
                      column.labels = c("DF = 6", "DF = 5", "DF = 4"),
-                     no.space = TRUE)
+                     no.space = TRUE, 
+                     notes.label = "Note: Standard Errors are in Prentices")
 ```
-
-## Model Selection
 
@@
 First, the model with six degrees of freedom, next one with five, and one with four.
-The results from these three models is in Table 2 made using Stargazer [@R-stargazer] on the next page.
+The results from these three models is in Table 2 made using Stargazer [@R-stargazer].
 The model with six degrees of freedom contains **Internet Users** which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way.
@@
 We are going to choose the model with five degrees of freedom.
-So we arrived at the following model.
-Double spacing makes this dificult
-$$\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +$$
-$$ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon$$
+So we arrived at the model with five degrees of freedom.
+
 ```{r message=FALSE}
@@
   labs(x = "Corruption Perception", y = "Political Rights") +
-  theme_light(base_size = size)
+  theme_light(base_size = size) + labs(title = "Response Term on Convariates")
 
@@
 However, this does seem to fit the data reasonably.
-There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coeffeceintes.
+There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coefficient.
+Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.
 
-## Remeidal Measures
+## Assumptions
+
 Now we will examine some remedial measures to analyze the performance and identify problems. 
 Let's start with plots of residuals.
-Figure 2, contains a histogram of the residuals adjcent to a QQ normal plot.
+Figure 2, contains a histogram of the residuals adjacent to a QQ normal plot.
 It is clear that there are substantial outliers at the lower end of political freedom.
-Upon further inspection found that these outliers are turkey from 2016 to 2018.
-These residuals are large and suggest a substancial loss in political freedom.
+Upon further inspection we found that these outliers are Turkey from 2016 to 2018.
+These residuals are large and suggest a substantial loss in political freedom.
 This is confirmed by Freedomhouse [@Freedomhouse] reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reasion to eliminate it.
-It was clear to us that there is substancial error variance and likely not constant from the posative residuals to negtive residuals.
-A Brown-Forsythe test confirmed our suspicians telling us that the error variance is significantly higher when the residuals are negative.
+After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
+It was clear to us that there is substantial error variance and likely not constant from the positive residuals to negative residuals.
+A Brown-Forsythe test confirmed our suspicions telling us that the error variance is significantly higher when the residuals are negative.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
   scale_x_continuous(limits = c(-4,4)) + 
-  labs(y = "Density", x = "Residual", title = "Histogram") + 
+  labs(y = "Density", x = "Residual", title = "Histogram of Residuals") + 
   theme_light(base_size = size + 10)
@@
   stat_qq() +
-  stat_qq_line(color = "#3C989E", size = 3) + 
+  stat_qq_line(color = "#3C989E", size = 2) + 
 scale_x_continuous(limits = c(-4,4)) + 

### 2020-11-25 paper/paper.tex
made adjustments

@@
 \keywords{keyword\newline\indent Word count: X}
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{figure}
-\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
-\renewcommand{\cftfigaftersnum}{.\space}
-\setlength{\cftfigindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cftfignumwidth}{Figure 10.\qquad}
-\cftpagenumbersoff{table}
-\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
-\renewcommand{\cfttabaftersnum}{.\space}
-\setlength{\cfttabindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifxetex
@@
 Political freedom is an abstract concept that does not lend well to quantification.
-However, Freedom House (\emph{Countries and Territories}, 2020), a U.S.
-based think tank and research institute, attempts this by assigning a index of political rights to each country every year based on a fixed criteria.
-Using the Papaja Package by (Aust \& Barth, 2020) package we take rmarkdown directly to APA format.
+However, Freedomhouse (\emph{Countries and Territories}, 2020), a U.S.
+based think tank and research institute, attempts this by assigning an index of political rights to each country every year based on a fixed criteria.
+Using the Papaja Package by (Aust \& Barth, 2020) we take Rmarkdown directly to APA format.
 
@@
 Electoral process is a score based on how the current government leaders were selected.
-How fairly the positions was obtained and kept.
+How fairly the positions were obtained and kept.
 As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
-Political Participation is evaluated on four criteria, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
-Functioning government, is the current heads of government determine policies, safeguards against corruption, and openness and transparency of government operation.
-Political freedom has been measured in this manner for every country from the years 1978 to present.
+Political Participation is evaluated on four criterion, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Functioning government, measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
+Freedom house has measured political freedom in this manner for every country from the years 1978 to present.
 
-Although such a metric is far from perfect.
-This will serve as a reasonable measure of political freedom around the world and will serve as an adequate sample to study political freedom.
-We obtained this from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
+Although such a metric is far from perfect and often debatable, this will serve as a reasonable measure of political freedom around the world to study political freedom.
+We obtained the dataset from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
-To explain a country's political rights index we selected: Corruption Perception Index, Education Expenditure, Electricity Use, Gini Coefficient, Internet Users as a percentage, Labor Force Participation Rate, Military Spending as percentage of GDP, and Murders per million.
+To explain a country's political rights index we selected: \textbf{Corruption Perception Index}, \textbf{Education Expenditure}, \textbf{Electricity Use}, \textbf{Gini Coefficient}, \textbf{Internet Users} as a percentage, \textbf{Labor Force Participation} Rate, \textbf{Military Spending} as percentage of GDP, and \textbf{Murders} per million.
 
@@
 These data sets were separate so we downloaded them individually, cleaned and combined them together using R (R Core Team, 2020) and the Tidyverse Package (Wickham et al., 2019).
-This resulted in a data set with all 196 countries form years 1950 to 2030 (data after 2019 were projections).
+This resulted in a data set with all 196 countries from years 1950 to 2030 (data after 2019 were projections).
 It was immediately apparent that there was a substantial amount of missing data in an obvious pattern.
-Less developed countries tended to have more missing data points.
-Also, the further back in time the more missing data points.
+Less developed countries tended to have more missing data points, and the further back in time the more missing data.
 Had we conducted this study as it was it would have been severely biased towards more developed countries as missing data points would be dropped.
 This forced us to narrow the scope of the study and focus only on countries within the Organization for Economic Co-operation and Development (OECD).
-This subset of countries has a reasonably complete data.
+This subset of countries has reasonably complete data.
 Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
@@
 This remedied most of the missing datapoints.
-However, even within the OEDC there were sparse few missing data points.
+However, even within the OEDC there were a few missing data points.
 From there, we imputed the median of each country's variable.
-For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period.
-Which afforded us the ability to keep even more data with minimal compromise.
+For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period and inputted it where there was an NA.
+This afforded us the ability to keep even more data with minimal compromise.
 This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
 After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0\% of their GDP, so we replaced the NA with a 0.
-This afforded us a full data set with no missing data points.
+This is how we obtained a complete and full data set with no missing data points.
 The only other adjustment made was to make a few of the variables more intuitive.
 Corruption perception for example was originally having 0 be the most perception of corruption and 100 being the least.
-For us we wanted to have a more intuitve interpretation so we subtracted 100 and mulitplied by negaitve one.
+We wanted to have a more intuitive interpretation so we subtracted 100 and multiplied by negative one.
+This gives us an interpretation of of 0 being the least corrupt and 100 the most corrupt.
+We did the same for political rights, which originally 1 was the most political freedom and 7 being the least.
+We want to interpret a higher number to having more political rights.
 
@@
 \midrule
-Political Rights & 6.60 & 7.00 & 0.79 & 2.00 & 7.00 & 5.00\\
-Year & 2009.50 & 2009.50 & 5.19 & 2001.00 & 2018.00 & 17.00\\
+Political Rights & 6.58 & 7.00 & 0.80 & 2.00 & 7.00 & 5.00\\
+Year & 2009.00 & 2009.00 & 5.48 & 2000.00 & 2018.00 & 18.00\\
 Corruption Perception & 31.95 & 29.00 & 15.87 & 8.00 & 71.00 & 63.00\\
 Education Expenditure & 0.20 & 0.20 & 0.04 & 0.10 & 0.37 & 0.27\\
-Electricity Use & 8682.17 & 6695.00 & 7533.32 & 866.00 & 54800.00 & 53934.00\\
+Electricity Use & 8598.03 & 6660.00 & 7297.72 & 846.00 & 54800.00 & 53954.00\\
 \addlinespace
-Gini & 33.77 & 32.70 & 6.35 & 24.40 & 56.80 & 32.40\\
-Internet Users & 65.41 & 70.90 & 22.93 & 2.85 & 99.00 & 96.15\\
-Life Expectancy & 0.60 & 0.61 & 0.06 & 0.45 & 0.78 & 0.33\\
-Labor Force Participation & 79.30 & 80.00 & 2.84 & 70.20 & 84.40 & 14.20\\
-Military Spending & 1.68 & 1.41 & 1.16 & 0.00 & 8.54 & 8.54\\
+Gini & 33.77 & 32.70 & 6.41 & 24.40 & 57.70 & 33.30\\
+Internet Users & 63.32 & 69.70 & 24.25 & 2.21 & 99.00 & 96.79\\
+Life Expectancy & 0.60 & 0.60 & 0.06 & 0.45 & 0.78 & 0.33\\
+Labor Force Participation & 79.18 & 79.80 & 2.88 & 70.20 & 84.40 & 14.20\\
+Military Spending & 1.69 & 1.43 & 1.16 & 0.00 & 8.54 & 8.54\\
 \addlinespace
-Murders rate & 3.13 & 1.04 & 6.15 & 0.15 & 29.07 & 28.92\\
+Murders rate & 3.17 & 1.06 & 6.16 & 0.15 & 29.07 & 28.92\\
 \bottomrule
@@
 
-Table 1 made with the (Zhu, 2020) contains Basic summary statistics from our dataset.
+Table 1, made with the KableExtra package (Zhu, 2020) contains basic summary statistics from our dataset.
 We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
 This is not ideal.
-We would much prefer that it was continuous with a substantial variation.
-First, the methodology of rather than taking continuous values Freedomhouse's classification is discrete classifying countries political rights taking values of the integers 1-7.
-Secondly countries with a low political rights by nature have a suspect data reporting process.
-Which is why we had to select a subset of countries and that subset leans towards having more political freedom.
+Freedomhouse's classification of political freedom is in discrete values from 1-7.
+Additionally, countries with a low political freedom have suspect data reporting.
+We had to select a subset of countries and that subset leans towards having more political freedom.
 We precede on the understanding that there are moderate problems with the data, first having a discrete response variable and the nature of the distribution being skewed towards the maximum 7/7 political freedom.
-
-With such considerations taken into account, we will not be making any non-linear transformation or variables.
-First, we examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
-With a clean, complete, and dataset that is contains flaws but is still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
-This lead us to choose between the following models.
-From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.
 
@@
 \end{figure}
+
+We examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+We will not be making any non-linear transformation or variables.
+With a dataset that contains flaws but still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
+This lead us to choose between the following models.
+From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.
+
+\hypertarget{model-selection}{%
+\subsection{Model Selection}\label{model-selection}}
 
@@
 \hline \\[-1.8ex] 
- Corruption Perception & $-$0.023$^{***}$ & $-$0.023$^{***}$ & $-$0.022$^{***}$ \\ 
+ Corruption Perception & $-$0.022$^{***}$ & $-$0.023$^{***}$ & $-$0.023$^{***}$ \\ 
   & (0.002) & (0.002) & (0.002) \\ 
-  Education Expendature & 1.746$^{***}$ & 1.900$^{***}$ & 1.898$^{***}$ \\ 
-  & (0.562) & (0.534) & (0.536) \\ 
-  Internet Users & 0.001 &  &  \\ 
+  Education Expendature & 1.655$^{***}$ & 2.076$^{***}$ & 2.064$^{***}$ \\ 
+  & (0.550) & (0.525) & (0.526) \\ 
+  Internet Users & 0.003$^{**}$ &  &  \\ 
   & (0.001) &  &  \\ 
-  Life Expectancy & $-$0.025$^{***}$ & $-$0.021$^{**}$ &  \\ 
+  Life Expectancy & $-$0.024$^{***}$ & $-$0.013 &  \\ 
   & (0.009) & (0.008) &  \\ 
-  Military Spending & $-$0.146$^{***}$ & $-$0.150$^{***}$ & $-$0.153$^{***}$ \\ 
-  & (0.019) & (0.019) & (0.019) \\ 
-  Murder Rate & $-$0.035$^{***}$ & $-$0.035$^{***}$ & $-$0.033$^{***}$ \\ 
+  Military Spending & $-$0.149$^{***}$ & $-$0.160$^{***}$ & $-$0.162$^{***}$ \\ 
+  & (0.019) & (0.018) & (0.018) \\ 
+  Murder Rate & $-$0.034$^{***}$ & $-$0.033$^{***}$ & $-$0.031$^{***}$ \\ 
   & (0.004) & (0.004) & (0.004) \\ 
-  Intercept & 9.212$^{***}$ & 8.979$^{***}$ & 7.284$^{***}$ \\ 
-  & (0.742) & (0.692) & (0.123) \\ 
+  Intercept & 9.035$^{***}$ & 8.306$^{***}$ & 7.264$^{***}$ \\ 
+  & (0.731) & (0.672) & (0.120) \\ 
  \hline \\[-1.8ex] 
-Observations & 648 & 648 & 648 \\ 
-R$^{2}$ & 0.548 & 0.547 & 0.543 \\ 
-Adjusted R$^{2}$ & 0.543 & 0.544 & 0.540 \\ 
-Residual Std. Error & 0.531 & 0.531 & 0.533 \\ 
-F Statistic & 129.343$^{***}$ & 155.112$^{***}$ & 190.808$^{***}$ \\ 
+Observations & 684 & 684 & 684 \\ 
+R$^{2}$ & 0.552 & 0.548 & 0.546 \\ 
+Adjusted R$^{2}$ & 0.548 & 0.545 & 0.544 \\ 
+Residual Std. Error & 0.536 & 0.538 & 0.539 \\ 
+F Statistic & 139.150$^{***}$ & 164.500$^{***}$ & 204.559$^{***}$ \\ 
 \hline 
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+Note: Standard Errors are in Prentices & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
@@
 
-\hypertarget{model-selection}{%
-\subsection{Model Selection}\label{model-selection}}
-
 From the best subsets, it was appropriate to narrow our model choices down to three.
 First, the model with six degrees of freedom, next one with five, and one with four.
-The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018) on the next page.
+The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018).
 The model with six degrees of freedom contains \textbf{Internet Users} which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way.
@@
 We are going to choose the model with five degrees of freedom.
-So we arrived at the following model.\\
-Double spacing makes this dificult
-\[\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\]
-\[ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\]
+So we arrived at the model with five degrees of freedom.
+
 \includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
@@
 However, this does seem to fit the data reasonably.
-There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coeffeceintes.
+There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coefficient.
+Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.
 
-\hypertarget{remeidal-measures}{%
-\subsection{Remeidal Measures}\label{remeidal-measures}}
+\hypertarget{assumptions}{%
+\subsection{Assumptions}\label{assumptions}}
 
@@
 Let's start with plots of residuals.
-Figure 2, contains a histogram of the residuals adjcent to a QQ normal plot.
+Figure 2, contains a histogram of the residuals adjacent to a QQ normal plot.
 It is clear that there are substantial outliers at the lower end of political freedom.
-Upon further inspection found that these outliers are turkey from 2016 to 2018.
-These residuals are large and suggest a substancial loss in political freedom.
+Upon further inspection we found that these outliers are Turkey from 2016 to 2018.
+These residuals are large and suggest a substantial loss in political freedom.
 This is confirmed by Freedomhouse (\emph{Countries and Territories}, 2020) reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reasion to eliminate it.\\
-It was clear to us that there is substancial error variance and likely not constant from the posative residuals to negtive residuals.
-A Brown-Forsythe test confirmed our suspicians telling us that the error variance is significantly higher when the residuals are negative.
+After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.\\
+It was clear to us that there is substantial error variance and likely not constant from the positive residuals to negative residuals.
+A Brown-Forsythe test confirmed our suspicions telling us that the error variance is significantly higher when the residuals are negative.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
 \KeywordTok{library}\NormalTok{(patchwork)}
-
 \NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}
-
 \KeywordTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
 \KeywordTok{r\_refs}\NormalTok{(}\StringTok{"r{-}references.bib"}\NormalTok{)}
-
 \NormalTok{knitr}\OperatorTok{::}\NormalTok{opts\_chunk}\OperatorTok{$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{echo =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{warning=}\OtherTok{FALSE}\NormalTok{, }\DataTypeTok{message =} \OtherTok{FALSE}\NormalTok{, }
                       \DataTypeTok{fig.width =} \DecValTok{12}\NormalTok{, }\DataTypeTok{fig.height =} \DecValTok{8}\NormalTok{) }
-
 \CommentTok{\# Read and Clean {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
 \NormalTok{files \textless{}{-}}\StringTok{ }\KeywordTok{list.files}\NormalTok{(}\DataTypeTok{path =}\NormalTok{ here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"raw\_data"}\NormalTok{), }\DataTypeTok{pattern =} \StringTok{".csv"}\NormalTok{)}
-
 \NormalTok{cleaning \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(df)\{}
@@
 \NormalTok{\}}
-
 \NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{files }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \CommentTok{\# Filtering {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-
 \NormalTok{countries \textless{}{-}}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"countries.RDS"}\NormalTok{))}
-
 \NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}
-\StringTok{  }\KeywordTok{filter}\NormalTok{(year }\OperatorTok{\textgreater{}}\StringTok{ }\DecValTok{2000}\NormalTok{, year }\OperatorTok{\textless{}}\StringTok{ }\DecValTok{2019}\NormalTok{, country }\OperatorTok{\%in\%}\StringTok{ }\NormalTok{countries) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{year =} \KeywordTok{as.numeric}\NormalTok{(year)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{filter}\NormalTok{(year }\OperatorTok{\textgreater{}=}\StringTok{ }\DecValTok{2000}\NormalTok{, year }\OperatorTok{\textless{}}\StringTok{ }\DecValTok{2019}\NormalTok{, country }\OperatorTok{\%in\%}\StringTok{ }\NormalTok{countries) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
 \StringTok{  }\KeywordTok{group\_by}\NormalTok{(country) }\OperatorTok{\%\textgreater{}\%}
@@
 \CommentTok{\# Iceland spent 0 so I needed to manually recode that}
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{military\_spending\_pct\_of\_gdp =} \KeywordTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{), }
-         \DataTypeTok{year =} \KeywordTok{as.numeric}\NormalTok{(year)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{military\_spending\_pct\_of\_gdp =} \KeywordTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{),}
+  \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
          \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Chile"}\NormalTok{, }\FloatTok{4.4}\NormalTok{),}
          \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Colombia"}\NormalTok{, }\FloatTok{25.34}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{         }\CommentTok{\# https://en.wikipedia.org/wiki/List\_of\_countries\_by\_intentional\_homicide\_rate}
-\StringTok{         }\CommentTok{\# these murder rates were not included in the gapminder but i didnt want to }
-\StringTok{         }\CommentTok{\# lose 3 important countries in LA}
 \StringTok{  }\KeywordTok{relocate}\NormalTok{(polrights\_fh) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
  \DataTypeTok{military\_spending\_pct\_of\_gdp =}\NormalTok{ military\_spending\_pct\_of\_gdp }\OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (corruption\_perception\_index\_cpi }\OperatorTok{{-}}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{*}\StringTok{ }\DecValTok{{-}1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (}\DecValTok{100} \OperatorTok{{-}}\StringTok{ }\NormalTok{corruption\_perception\_index\_cpi)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
 \StringTok{  }\KeywordTok{ungroup}\NormalTok{()}
-
 \CommentTok{\# Best Subset Selection {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-
 \NormalTok{vars \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \StringTok{  }\KeywordTok{names}\NormalTok{()}
-
-\NormalTok{outcome \textless{}{-}}\StringTok{ "polrights\_fh"}
-
 \NormalTok{models \textless{}{-}}\StringTok{ }\KeywordTok{list}\NormalTok{()}
@@
   \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(vc)) \{}
-\NormalTok{    model \textless{}{-}}\StringTok{ }\KeywordTok{as.formula}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(outcome, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\KeywordTok{paste0}\NormalTok{(vc[,j], }\DataTypeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
+\NormalTok{    model \textless{}{-}}\StringTok{ }\KeywordTok{as.formula}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(}\StringTok{"polrights\_fh"}\NormalTok{, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\KeywordTok{paste0}\NormalTok{(vc[,j], }\DataTypeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
 \NormalTok{    models \textless{}{-}}\StringTok{ }\KeywordTok{c}\NormalTok{(models, model)}
-
 \NormalTok{    \}}
 \NormalTok{  \}}
-
 \NormalTok{subsets \textless{}{-}}\StringTok{ }\KeywordTok{map}\NormalTok{(models, }\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{lm}\NormalTok{(x, data)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{distinct}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
 \StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ id) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
-    \DataTypeTok{Model =} \KeywordTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
+\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Model =} \KeywordTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
          \DataTypeTok{Model =} \KeywordTok{str\_replace}\NormalTok{(Model, }\StringTok{"\textasciitilde{}"}\NormalTok{, }\StringTok{"="}\NormalTok{), }
@@
 \StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }
-
 \NormalTok{fit\_df6 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df6\_formula, data)}
-
 \NormalTok{model\_df5\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{5}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{()}
-
 \NormalTok{fit\_df5 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df5\_formula, data)}
-
 \NormalTok{model\_df4\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }
-
 \NormalTok{fit\_df4 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df4\_formula, data)}
 \NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
-
 \NormalTok{    x \textless{}{-}}\StringTok{ }\KeywordTok{enquo}\NormalTok{(x)}
@@
 \NormalTok{\}}
-
 \NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
@@
 \StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{theme\_test}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }
+\StringTok{  }\KeywordTok{theme\_test}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }\OperatorTok{+}\StringTok{ }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Best Subset Selection"}\NormalTok{)}
 
@@
 
-\KeywordTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }\DataTypeTok{type =} \StringTok{"latex"}\NormalTok{, }
+\KeywordTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }
+                     \DataTypeTok{type =} \StringTok{"latex"}\NormalTok{, }
                      \DataTypeTok{title =} \StringTok{"Regression Results"}\NormalTok{, }
@@
                      \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"DF = 6"}\NormalTok{, }\StringTok{"DF = 5"}\NormalTok{, }\StringTok{"DF = 4"}\NormalTok{),}
-                     \DataTypeTok{no.space =} \OtherTok{TRUE}\NormalTok{)}
+                     \DataTypeTok{no.space =} \OtherTok{TRUE}\NormalTok{, }
+                     \DataTypeTok{notes.label =} \StringTok{"Note: Standard Errors are in Prentices"}\NormalTok{)}
 \NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{18}
@@
 \StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Corruption Perception"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Political Rights"}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }\OperatorTok{+}\StringTok{ }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Response Term on Convariates"}\NormalTok{)}
 
@@
 \StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Density"}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Residual"}\NormalTok{, }\DataTypeTok{title =} \StringTok{"Histogram"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Density"}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Residual"}\NormalTok{, }\DataTypeTok{title =} \StringTok{"Histogram of Residuals"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
 \StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size }\OperatorTok{+}\StringTok{ }\DecValTok{10}\NormalTok{)}
@@
 \StringTok{  }\KeywordTok{stat\_qq}\NormalTok{() }\OperatorTok{+}
-\StringTok{  }\KeywordTok{stat\_qq\_line}\NormalTok{(}\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{3}\NormalTok{) }\OperatorTok{+}\StringTok{ }
+\StringTok{  }\KeywordTok{stat\_qq\_line}\NormalTok{(}\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }
 \KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
@@
 
-\clearpage
-\renewcommand{\listfigurename}{Figure captions}
-
-\clearpage
-\renewcommand{\listtablename}{Table captions}
-
 \end{document}

### 2020-11-29 paper/paper.Rmd
meeting

@@
 
-2020 is an election year, which has many of use reflecting on political freedoms.
+2020 is an election year, which has many of us reflecting on political freedom.
 Political freedoms are important because they have a dramatic impact on the quality of life for the citizens of a country.
@@
 Electoral process, political participation, and functioning government.
-Electoral process is a score based on how the current government leaders were selected.
-How fairly the positions were obtained and kept.
+Electoral process is a score based on how the current government leaders were selected, mainly how fairly the positions were obtained and kept.
 As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
@@
 
-Although such a metric is far from perfect and often debatable, this will serve as a reasonable measure of political freedom around the world to study political freedom.
+Although such a metric is imperfect and debatable, this will serve as a reasonable measure of political freedom around the world.
 We obtained the dataset from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
-To explain a country's political rights index we selected: **Corruption Perception Index**, **Education Expenditure**, **Electricity Use**, **Gini Coefficient**, **Internet Users** as a percentage, **Labor Force Participation** Rate, **Military Spending** as percentage of GDP, and **Murders** per million.
+To explain a country's political rights index we selected: **Corruption Perception Index**, **Education Expenditure**, **Electricity Use**, **Gini Coefficient** a measure of economic inequality, **Internet Users** as a percentage, **Labor Force Participation** Rate, **Military Spending** as percentage of GDP, and **Murders** per million.
 
@@
 This forced us to narrow the scope of the study and focus only on countries within the Organization for Economic Co-operation and Development (OECD).
-This subset of countries has reasonably complete data.
+This subset of countries has much more complete data.
 Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
@@
 We examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
-We will not be making any non-linear transformation or variables.
-With a dataset that contains flaws but still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
-This lead us to choose between the following models.
+We will not be making any non-linear transformation of variables.
+With a dataset that contains flaws but still reasonably holds assumptions we performed the best subset algorithm to obtain a model with the best fit.
 From the graph of the subsets we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
@@
 The results from these three models is in Table 2 made using Stargazer [@R-stargazer].
-The model with six degrees of freedom contains **Internet Users** which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way.
-Looking at the model with five degrees of freedom, all of our coefficients are statistically significant at $p < 0.01$.
+The model with six degrees of freedom contains **Internet Users** which is 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99% level.
 The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
 Counterintuitively, politically freedom seems to decrease as life expectancy increases.
-We are not qualified to attempt explain that we can only speculate.
-We are going to choose the model with five degrees of freedom.
-So we arrived at the model with five degrees of freedom.
+We are not qualified to explain that we can only speculate.
+This is how we arrived at the model with five degrees of freedom.
 
@@
 However, this does seem to fit the data reasonably.
-There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coefficient.
+There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficient.
 Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.
@@
 
-Now we will examine some remedial measures to analyze the performance and identify problems. 
+Now we will examine some regression diagnostics to analyze the performance and identify problems.
 Let's start with plots of residuals.

### 2020-11-29 paper/paper.tex
meeting

@@
 
-Although such a metric is far from perfect and often debatable, this will serve as a reasonable measure of political freedom around the world to study political freedom.
+Although such a metric is imperfect and debatable, this will serve as a reasonable measure of political freedom around the world.
 We obtained the dataset from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
-To explain a country's political rights index we selected: \textbf{Corruption Perception Index}, \textbf{Education Expenditure}, \textbf{Electricity Use}, \textbf{Gini Coefficient}, \textbf{Internet Users} as a percentage, \textbf{Labor Force Participation} Rate, \textbf{Military Spending} as percentage of GDP, and \textbf{Murders} per million.
+To explain a country's political rights index we selected: \textbf{Corruption Perception Index}, \textbf{Education Expenditure}, \textbf{Electricity Use}, \textbf{Gini Coefficient} a measure of economic inequality, \textbf{Internet Users} as a percentage, \textbf{Labor Force Participation} Rate, \textbf{Military Spending} as percentage of GDP, and \textbf{Murders} per million.
 
@@
 We examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
-We will not be making any non-linear transformation or variables.
-With a dataset that contains flaws but still reasonably holds assumptions we performed the best subsection algorithm to obtain a model with the best fit.
-This lead us to choose between the following models.
+We will not be making any non-linear transformation of variables.
+With a dataset that contains flaws but still reasonably holds assumptions we performed the best subset algorithm to obtain a model with the best fit.
 From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.
@@
 The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018).
-The model with six degrees of freedom contains \textbf{Internet Users} which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way.
-Looking at the model with five degrees of freedom, all of our coefficients are statistically significant at \(p < 0.01\).
+The model with six degrees of freedom contains \textbf{Internet Users} which is 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99\% level.
 The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
 Counterintuitively, politically freedom seems to decrease as life expectancy increases.
-We are not qualified to attempt explain that we can only speculate.
-We are going to choose the model with five degrees of freedom.
-So we arrived at the model with five degrees of freedom.
+We are not qualified to explain that we can only speculate.
+This is how we arrived at the model with five degrees of freedom.
 
@@
 
-Now we will examine some remedial measures to analyze the performance and identify problems.
+Now we will examine some regression diagnostics to analyze the performance and identify problems.
 Let's start with plots of residuals.

### 2020-11-29 slides.Rmd
switched order
meeting

@@
 
-* Observational study of political freedom as a function of social, economic, political factors.
+* Observational study of political freedom as a function of social, economic, and political factors.
 
@@
 
+- Political Freedom Index takes values from 1 to 7
+
 ---
@@
 
-- **Murders rate** per million people
+- **Murders per million**
 
@@
 
-# Assumptions
-
---
-### Finite Mean and Standard Deviation
-### Independence
-### Linearity
-### Normality
-### Homoscedasticity
-
----
-
 # Best Subsets by Adjusted R Squared
@@
 ---
+
+# Assumptions
+
+--
+### Finite Mean and Standard Deviation
+### Independence
+### Linearity
+### Normality
+### Homoscedasticity
+
+---
+
 class: center
@@
 $$
-
+# Regression Results
 ```{r}
@@
 $$
+# Regression Results
+
 ```{r}
@@
                    geom_label(outliers, mapping = aes(x = -3, y = -3.5, label = "OUTLIERS"), color = "#D7261E", size = 5)
-
 ```
@@
 labeled_outliers + labeled_qq
-```
----
-
-```{r}
-fit_df5 %>% 
-  broom::augment() %>% 
-  mutate(yhat = predict(fit_df5),
-         resid = resid(fit_df5)) %>% 
-  ggplot() + 
-  geom_point(aes(x = yhat, y = resid)) + 
-  geom_hline(yintercept = 0, color = "red") + 
-  scale_y_continuous(limits = c(-4,4)) + 
-  labs(y = "Residual", x = "Predicted Value")
 ```
@@
   mutate(p.value = as.numeric(p.value)) %>% 
+    mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
   kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
@@
 - Confirmed they are not errors. 
-- Decided to keep them because they are indicating a substantial loss in political freedom which falls outside of the scope of the model. However, is important for our research question.
+- Decided to keep them because they are indicating a substantial loss in political freedom which falls outside of the scope of the model. However, this is important for our research question.
 
@@
 
-- Conclude error variance is not constant
+- $t^{*}_{BF} > t(.975; 643)$ Therefore we conclude error variance is not constant
 
@@
 - Conclude, again, error variance is not constant even when outliers are removed.
-- The model does a much better job at predicting political freedom in countries with more. This is likely due to the fact that our sample is the OCED that skews twards more Political Freedom
+- The model does a much better job explaining the political freedom in countries when they have a higher degree of it.
+This is likely due to the fact that our sample is the OECD that skews towards more Political Freedom
 
@@
 
-1. Despite minor problems with outliers we found that statistically significant 
-1. because
+1. With minimal violations of assumptions, we found statistically significant associations between our response term and covariates
+
+---
+
+# Conclusions
+
+1. With minimal violations of assumptions, we found statistically significant associations between our response term and covariates
+1. There is a degree of heteroscedasticity
+
+---
+
+# Conclusions
+
+1. With minimal violations of assumptions, we found statistically significant associations between our response term and covariates
+1. There is a degree of heteroscedasticity
+1. Results are only valid for countries within the OECD and should not be used to make inferences for every country.
+
+---
+
+# Conclusions
+
+1. With minimal violations of assumptions, we found statistically significant associations between our response term and covariates
+1. There is a degree of heteroscedasticity
+1. Results are only valid for countries within the OECD and should not be used to make inferences for every country.
+1. The few outliers did not have dramatic impact on the results
 
@@
 
-# Thanks You and We are Happy to Take Questions
+# Thank You and We are Happy to Take Questions
 
@@
 ```
+
+```{r}
+beepr::beep()
+```

### 2020-11-29 paper/paper.Rmd
update

@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
 Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.
-
-## Assumptions
-
 Now we will examine some regression diagnostics to analyze the performance and identify problems.
@@
 After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
-It was clear to us that there is substantial error variance and likely not constant from the positive residuals to negative residuals.
-A Brown-Forsythe test confirmed our suspicions telling us that the error variance is significantly higher when the residuals are negative.
+
+It was clear from the plots that error variance may not be constant.
+A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
+We calculated a $t^{*}_{BF} = 9.49$ Which informed us that the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.

### 2020-11-29 paper/paper.tex
update

@@
 \keywords{keyword\newline\indent Word count: X}
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
@@
 There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficient.
-Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.
-
-\hypertarget{assumptions}{%
-\subsection{Assumptions}\label{assumptions}}
-
+Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.\\
 Now we will examine some regression diagnostics to analyze the performance and identify problems.
@@
 This is confirmed by Freedomhouse (\emph{Countries and Territories}, 2020) reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.\\
-It was clear to us that there is substantial error variance and likely not constant from the positive residuals to negative residuals.
-A Brown-Forsythe test confirmed our suspicions telling us that the error variance is significantly higher when the residuals are negative.
+After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
+
+It was clear from the plots that error variance may not be constant.
+A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
+We calculated a \(t^{*}_{BF} = 9.49\) Which informed us that the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.

### 2020-11-29 slides.Rmd
cleaned error

@@
 library(patchwork)
-library(xaringanthemer)
 
-style_mono_accent_inverse(base_color = "#3C989E")
 theme_set(theme_light(base_size = 30))
@@
     mutate_if(is.numeric, round, 2) %>% 
-DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), caption = "Mean", 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), 
             colnames =  c("Country","Internet Users", "Labor Force", "Life Expectancy", "Military Spending", "Murder Rate") )
@@
 select(country, corruption_perception_index_cpi:gini) %>% 
-DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), caption = "Mean", 
+DT::datatable(fillContainer = FALSE, options = list(pageLength = 5), 
               colnames = c("Country", "CPI", "Edu Exp", "Electric Use", "Gini"))

### 2020-11-29 paper/paper.Rmd
referenced index
.

@@
 library(patchwork)
+library("papaja")
 size <- 30
-library("papaja")
 r_refs("r-references.bib")
@@
   pivot_wider(names_from = id)
-
 # Filtering ---------------------------------------------------------------
@@
 based think tank and research institute, attempts this by assigning an index of political rights to each country every year based on a fixed criteria.
-Using the Papaja Package by [@R-papaja] we take Rmarkdown directly to APA format.
+Using the Papaja Package [@R-papaja] we take Rmarkdown directly to APA format.
 
@@
 These data sets were separate so we downloaded them individually, cleaned and combined them together using R [@R-base] and the Tidyverse Package [@R-tidyverse].
+We included all the code in the appendix.
 This resulted in a data set with all 196 countries from years 1950 to 2030 (data after 2019 were projections).

### 2020-11-30 paper/paper.Rmd
.

@@
 Less developed countries tended to have more missing data points, and the further back in time the more missing data.
-Had we conducted this study as it was it would have been severely biased towards more developed countries as missing data points would be dropped.
+Had we conducted this study as it was, it would have been severely biased towards more developed countries as missing data points would be dropped.
 This forced us to narrow the scope of the study and focus only on countries within the Organization for Economic Co-operation and Development (OECD).
@@
 For instance, Austria's electricity consumption was missing for 2012, so we took the median of Austria's consumption over the 18 year period and inputted it where there was an NA.
-This afforded us the ability to keep even more data with minimal compromise.
+This afforded us the ability to keep more data with minimal compromise.
 This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
@@
 Table 1, made with the KableExtra package [@R-kableExtra] contains basic summary statistics from our dataset.
-We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
+We observed that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
 This is not ideal.
@@
 
-We examined the results of that we did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+We examined the results and did not find compelling evidence to support making a such a transformation and the data are roughly linear.
 We will not be making any non-linear transformation of variables.
@@
 The results from these three models is in Table 2 made using Stargazer [@R-stargazer].
-The model with six degrees of freedom contains **Internet Users** which is 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+The model with six degrees of freedom contains **Internet Users** with coeffecient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
 Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99% level.
@@
   geom_point() + 
-  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
+  geom_smooth(method = "lm", se = FALSE,color = "#3C989E") +
     scale_y_continuous(breaks = 1:7) + 
@@
 ```
-The scatter plots look a bit strange at first because of the nature of the discrete response variable.
-However, this does seem to fit the data reasonably.
+
+  The scatter plots look a bit strange at first because of the nature of the discrete response variable, however, this does seem to fit the data reasonably.
 There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficient.
@@
 A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
-We calculated a $t^{*}_{BF} = 9.49$ Which informed us that the error variance is substantially higher when the values of political freedom are lower.
+We calculated a $t^{*}_{BF} = 9.49$ which informed us that the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
 The model does a reasonably good job predicting political freedom in the 6 and 7 range.
-However, completely falls apart at the one case of a substantial loss in freedom.
+However, the model completely falls apart at the one case of a substantial loss in freedom.
 Again, we don't have an exhaustive sample of countries losing freedom so this is consistent with the dataset we have.

### 2020-11-30 paper/paper.tex
referenced index
.

@@
 based think tank and research institute, attempts this by assigning an index of political rights to each country every year based on a fixed criteria.
-Using the Papaja Package by (Aust \& Barth, 2020) we take Rmarkdown directly to APA format.
+Using the Papaja Package (Aust \& Barth, 2020) we take Rmarkdown directly to APA format.
 
@@
 These data sets were separate so we downloaded them individually, cleaned and combined them together using R (R Core Team, 2020) and the Tidyverse Package (Wickham et al., 2019).
+We included all the code in the appendix.
 This resulted in a data set with all 196 countries from years 1950 to 2030 (data after 2019 were projections).
@@
 Table 1, made with the KableExtra package (Zhu, 2020) contains basic summary statistics from our dataset.
-We observe that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
+We observed that the mean political rights is 6.6 nearly full with a fairly low standard deviation.
 This is not ideal.
@@
 The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018).
-The model with six degrees of freedom contains \textbf{Internet Users} which is 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+The model with six degrees of freedom contains \textbf{Internet Users} with coeffecient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
 Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99\% level.
@@
 \includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
-The scatter plots look a bit strange at first because of the nature of the discrete response variable.
-However, this does seem to fit the data reasonably.
+
+The scatter plots look a bit strange at first because of the nature of the discrete response variable, however, this does seem to fit the data reasonably.
 There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficient.
@@
 A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
-We calculated a \(t^{*}_{BF} = 9.49\) Which informed us that the error variance is substantially higher when the values of political freedom are lower.
+We calculated a \(t^{*}_{BF} = 9.49\) which informed us that the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
 \KeywordTok{library}\NormalTok{(patchwork)}
+\KeywordTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
 \NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}
-\KeywordTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
 \KeywordTok{r\_refs}\NormalTok{(}\StringTok{"r{-}references.bib"}\NormalTok{)}
@@
 \StringTok{  }\KeywordTok{pivot\_wider}\NormalTok{(}\DataTypeTok{names\_from =}\NormalTok{ id)}
-
 \CommentTok{\# Filtering {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
@@
 \StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}
+\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{,}\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}
 \StringTok{    }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }

### 2020-11-30 slides.Rmd
rm slide

@@
               colnames = c("DF", "AIC", "Model"))
-```
-
----
-
-class: center, middle
-
-# Best Subsets by AIC
-
-```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
-r <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))
-
-subsets %>% 
-  ggplot(aes(x = df, y = AIC)) + 
-  geom_point() + 
-  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "#3C989E") + 
-  labs(title = "", x = "Parameters", y = "AIC") + 
-  scale_x_continuous(breaks = 1:9) + 
-  theme_test(base_size = 30) 
 ```

### 2020-11-30 slides.Rmd
final

@@
 subtitle: "Sabrina Ball, Joe Despres, Joe Sigler, Jacob Haywood"
-date: "Last compiled `r format(Sys.time(), '%H:%M')`"
+date: ""
 output:

### 2020-12-04 paper/paper.Rmd
.
update

@@
 
-The **Political Rights** Index is comprised of three subcategories.
+The **Political Rights Index** is comprised of three subcategories.
 Electoral process, political participation, and functioning government.
@@
 
-Although such a metric is imperfect and debatable, this will serve as a reasonable measure of political freedom around the world.
+We have little doubt that this is a meticulously calculated metric, however, this takes discrete values.
+We are going to be applying a continuous test to these data.
+Knowing this, we will advise caution is taken in interpretation.
+One should take these results knowing full well that a core assumption is violated.
+Despite this, we still know that these results can be helpful in policy recommendations and to confirm suspicion that associations may in fact exist.
+While the exact value of our regression coefficients are not to be interpreted as slope but a measure of the direction of the association.
+This will serve as a reasonable measure of political freedom around the world.
+However, measuring political freedom cannot be done in the same way as measuring weight, speed, or temperature.
+There are inherent biases in the people measuring this.
+Most obvious, data are collected and funded by people in the United States and comes a heavy cultural bias so associations should be taken to mean a western notion of the concept of freedom.
 We obtained the dataset from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
@@
 We want to interpret a higher number to having more political rights.
+\newpage
 
@@
 
-We examined the results and did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+We examined the results and due to the categorical nature we are not aware of any function that would map discrete values onto the real line.
+Therefore, we did not find compelling evidence to support making such a transformation and the data are roughly linear.
 We will not be making any non-linear transformation of variables.
-With a dataset that contains flaws but still reasonably holds assumptions we performed the best subset algorithm to obtain a model with the best fit.
+With a flawed dataset that reasonably holds all other assumptions we performed the best subset algorithm to obtain a model with the best fit.
 From the graph of the subsets we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
+## Model Selection
 
-## Model Selection
 ```{r results="asis"}
@@
 The results from these three models is in Table 2 made using Stargazer [@R-stargazer].
-The model with six degrees of freedom contains **Internet Users** with coeffecient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+The model with six degrees of freedom contains **Internet Users** with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+Also, given the violation of assumptions it seems reasonable to exude it from the model.
 Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99% level.
@@
 
-  The scatter plots look a bit strange at first because of the nature of the discrete response variable, however, this does seem to fit the data reasonably.
-There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficient.
-Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.
+  The scatter plots look a bit strange at first because of the nature of the discrete response variable, however, this does seem to fit the data reasonably well.
+There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficients.
+Life expectancy on it's own has a positive association with political freedom, however, when holding the other covariates constant we find that slope to be negative.
 Now we will examine some regression diagnostics to analyze the performance and identify problems.
@@
 It is clear that there are substantial outliers at the lower end of political freedom.
-Upon further inspection we found that these outliers are Turkey from 2016 to 2018.
+Upon further inspection, we found that these outliers are Turkey from 2016 to 2018.
 These residuals are large and suggest a substantial loss in political freedom.
 This is confirmed by Freedomhouse [@Freedomhouse] reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
+After some discussion, we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
 
@@
 A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
-We calculated a $t^{*}_{BF} = 9.49$ which informed us that the error variance is substantially higher when the values of political freedom are lower.
+We calculated a $t^{*}_{BF} = 9.49$ which informs us that the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
 Military spending is associated with a decrease in political freedom.
+After conducting this study, we are reasonably sure that a relationship exists between political freedom and social, economic, and political factors.
+We are assured these things matter.
+Therefore, because we value political freedom, we suggest that when the choice comes, policy makers should choose to spend on education opposed to military when attempting to increase political freedom.
+Other covariates, policy makers do not have such direct control over.
 

### 2020-12-04 paper/paper.tex
update

@@
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
+\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
+  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
 % \usepackage{etoolbox}
@@
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \newlength{\cslhangindent}
 \setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {\setlength{\parindent}{0pt}%
-  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
-  {\par}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 Political freedom is an abstract concept that does not lend well to quantification.
-However, Freedomhouse (\emph{Countries and Territories}, 2020), a U.S.
+However, Freedomhouse (\emph{Countries and territories}, 2020), a U.S.
 based think tank and research institute, attempts this by assigning an index of political rights to each country every year based on a fixed criteria.
@@
 
-The \textbf{Political Rights} Index is comprised of three subcategories.
+The \textbf{Political Rights Index} is comprised of three subcategories.
 Electoral process, political participation, and functioning government.
@@
 
-Although such a metric is imperfect and debatable, this will serve as a reasonable measure of political freedom around the world.
+We have little doubt that this is a meticulously calculated metric, however, this takes discrete values.
+We are going to be applying a continuous test to these data.
+Knowing this, we will advise caution is taken in interpretation.
+One should take these results knowing full well that a core assumption is violated.
+Despite this, we still know that these results can be helpful in policy recommendations and to confirm suspicion that associations may in fact exist.
+While the exact value of our regression coefficients are not to be interpreted as slope but a measure of the direction of the association.
+This will serve as a reasonable measure of political freedom around the world.
+However, measuring political freedom cannot be done in the same way as measuring weight, speed, or temperature.
+There are inherent biases in the people measuring this.
+Most obvious, data are collected and funded by people in the United States and comes a heavy cultural bias so associations should be taken to mean a western notion of the concept of freedom.
 We obtained the dataset from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
@@
 
-We examined the results and did not find compelling evidence to support making a such a transformation and the data are roughly linear.
+We examined the results and due to the categorical nature we are not aware of any function that would map discrete values onto the real line.
+Therefore, we did not find compelling evidence to support making such a transformation and the data are roughly linear.
 We will not be making any non-linear transformation of variables.
-With a dataset that contains flaws but still reasonably holds assumptions we performed the best subset algorithm to obtain a model with the best fit.
-From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.
-
-\hypertarget{model-selection}{%
-\subsection{Model Selection}\label{model-selection}}
+With a flawed dataset that reasonably holds all other assumptions we performed the best subset algorithm to obtain a model with the best fit.
+From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.\\
+\#\# Model Selection
 
@@
 The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018).
-The model with six degrees of freedom contains \textbf{Internet Users} with coeffecient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+The model with six degrees of freedom contains \textbf{Internet Users} with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+Also, given the violation of assumptions it seems reasonable to exude it from the model.
 Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99\% level.
@@
 
-The scatter plots look a bit strange at first because of the nature of the discrete response variable, however, this does seem to fit the data reasonably.
-There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficient.
-Life expectancy on its own has a positive association with political freedom, however when holding the other covariates constant we find that slope to be negative.\\
+The scatter plots look a bit strange at first because of the nature of the discrete response variable, however, this does seem to fit the data reasonably well.
+There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficients.
+Life expectancy on it's own has a positive association with political freedom, however, when holding the other covariates constant we find that slope to be negative.\\
 Now we will examine some regression diagnostics to analyze the performance and identify problems.
@@
 It is clear that there are substantial outliers at the lower end of political freedom.
-Upon further inspection we found that these outliers are Turkey from 2016 to 2018.
+Upon further inspection, we found that these outliers are Turkey from 2016 to 2018.
 These residuals are large and suggest a substantial loss in political freedom.
-This is confirmed by Freedomhouse (\emph{Countries and Territories}, 2020) reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After much discussion we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
+This is confirmed by Freedomhouse (\emph{Countries and territories}, 2020) reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
+After some discussion, we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
 
@@
 A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
-We calculated a \(t^{*}_{BF} = 9.49\) which informed us that the error variance is substantially higher when the values of political freedom are lower.
+We calculated a \(t^{*}_{BF} = 9.49\) which informs us that the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
 \hypertarget{refs}{}
-\begin{cslreferences}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 (2019).
-Welcome to the tidyverse.
+Welcome to the {tidyverse}.
 \emph{Journal of Open Source Software}, \emph{4}(43), 1686.
@@
 \leavevmode\hypertarget{ref-R-kableExtra}{}%
-Zhu, H. (2020). \emph{KableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
-\end{cslreferences}
+Zhu, H. (2020). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+
+\end{CSLReferences}
 
@@
 \begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(tidyverse)}
-\KeywordTok{library}\NormalTok{(kableExtra)}
-\KeywordTok{library}\NormalTok{(stargazer)}
-\KeywordTok{library}\NormalTok{(patchwork)}
-\KeywordTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
-\NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}
-\KeywordTok{r\_refs}\NormalTok{(}\StringTok{"r{-}references.bib"}\NormalTok{)}
-\NormalTok{knitr}\OperatorTok{::}\NormalTok{opts\_chunk}\OperatorTok{$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{echo =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{warning=}\OtherTok{FALSE}\NormalTok{, }\DataTypeTok{message =} \OtherTok{FALSE}\NormalTok{, }
-                      \DataTypeTok{fig.width =} \DecValTok{12}\NormalTok{, }\DataTypeTok{fig.height =} \DecValTok{8}\NormalTok{) }
+\FunctionTok{library}\NormalTok{(tidyverse)}
+\FunctionTok{library}\NormalTok{(kableExtra)}
+\FunctionTok{library}\NormalTok{(stargazer)}
+\FunctionTok{library}\NormalTok{(patchwork)}
+\FunctionTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
+\NormalTok{size }\OtherTok{\textless{}{-}} \DecValTok{30}
+\FunctionTok{r\_refs}\NormalTok{(}\StringTok{"r{-}references.bib"}\NormalTok{)}
+\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{echo =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{warning=}\ConstantTok{FALSE}\NormalTok{, }\AttributeTok{message =} \ConstantTok{FALSE}\NormalTok{, }
+                      \AttributeTok{fig.width =} \DecValTok{12}\NormalTok{, }\AttributeTok{fig.height =} \DecValTok{8}\NormalTok{) }
 \CommentTok{\# Read and Clean {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{files \textless{}{-}}\StringTok{ }\KeywordTok{list.files}\NormalTok{(}\DataTypeTok{path =}\NormalTok{ here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"raw\_data"}\NormalTok{), }\DataTypeTok{pattern =} \StringTok{".csv"}\NormalTok{)}
-\NormalTok{cleaning \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(df)\{}
-\NormalTok{  df \textless{}{-}}\StringTok{ }\KeywordTok{pivot\_longer}\NormalTok{(df, }\DataTypeTok{cols =} \OperatorTok{{-}}\NormalTok{country, }\DataTypeTok{names\_to =} \StringTok{"year"}\NormalTok{)}
+\NormalTok{files }\OtherTok{\textless{}{-}} \FunctionTok{list.files}\NormalTok{(}\AttributeTok{path =}\NormalTok{ here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"raw\_data"}\NormalTok{), }\AttributeTok{pattern =} \StringTok{".csv"}\NormalTok{)}
+\NormalTok{cleaning }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(df)\{}
+\NormalTok{  df }\OtherTok{\textless{}{-}} \FunctionTok{pivot\_longer}\NormalTok{(df, }\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{country, }\AttributeTok{names\_to =} \StringTok{"year"}\NormalTok{)}
 \NormalTok{\}}
-\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{files }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{read\_csv}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(}\StringTok{"raw\_data/"}\NormalTok{, x))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{setNames}\NormalTok{(}\KeywordTok{gsub}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{.csv$"}\NormalTok{, }\StringTok{""}\NormalTok{, files)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{map}\NormalTok{(cleaning) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{pivot\_wider}\NormalTok{(}\DataTypeTok{names\_from =}\NormalTok{ id)}
+\NormalTok{data }\OtherTok{\textless{}{-}}\NormalTok{ files }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) }\FunctionTok{read\_csv}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(}\StringTok{"raw\_data/"}\NormalTok{, x))) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{setNames}\NormalTok{(}\FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.csv$"}\NormalTok{, }\StringTok{""}\NormalTok{, files)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{map}\NormalTok{(cleaning) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"id"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ id)}
 \CommentTok{\# Filtering {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{countries \textless{}{-}}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"countries.RDS"}\NormalTok{))}
-\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{year =} \KeywordTok{as.numeric}\NormalTok{(year)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{filter}\NormalTok{(year }\OperatorTok{\textgreater{}=}\StringTok{ }\DecValTok{2000}\NormalTok{, year }\OperatorTok{\textless{}}\StringTok{ }\DecValTok{2019}\NormalTok{, country }\OperatorTok{\%in\%}\StringTok{ }\NormalTok{countries) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{group\_by}\NormalTok{(country) }\OperatorTok{\%\textgreater{}\%}
-\StringTok{  }\KeywordTok{mutate\_at}\NormalTok{(}\KeywordTok{vars}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country),}\KeywordTok{list}\NormalTok{(}\OperatorTok{\textasciitilde{}}\KeywordTok{ifelse}\NormalTok{(}\KeywordTok{is.na}\NormalTok{(.), }\KeywordTok{median}\NormalTok{(., }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{), .))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
+\NormalTok{countries }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"countries.RDS"}\NormalTok{))}
+\NormalTok{data }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{year =} \FunctionTok{as.numeric}\NormalTok{(year)) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{filter}\NormalTok{(year }\SpecialCharTok{\textgreater{}=} \DecValTok{2000}\NormalTok{, year }\SpecialCharTok{\textless{}} \DecValTok{2019}\NormalTok{, country }\SpecialCharTok{\%in\%}\NormalTok{ countries) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{group\_by}\NormalTok{(country) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{country),}\FunctionTok{list}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\FunctionTok{ifelse}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(.), }\FunctionTok{median}\NormalTok{(., }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{), .))) }\SpecialCharTok{\%\textgreater{}\%}
 \CommentTok{\# Iceland spent 0 so I needed to manually recode that}
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{military\_spending\_pct\_of\_gdp =} \KeywordTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{),}
-  \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
-         \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Chile"}\NormalTok{, }\FloatTok{4.4}\NormalTok{),}
-         \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Colombia"}\NormalTok{, }\FloatTok{25.34}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{relocate}\NormalTok{(polrights\_fh) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{polrights\_fh =}\NormalTok{ (}\DecValTok{8} \OperatorTok{{-}}\StringTok{ }\NormalTok{polrights\_fh),}
- \DataTypeTok{military\_spending\_pct\_of\_gdp =}\NormalTok{ military\_spending\_pct\_of\_gdp }\OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (}\DecValTok{100} \OperatorTok{{-}}\StringTok{ }\NormalTok{corruption\_perception\_index\_cpi)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ungroup}\NormalTok{()}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{military\_spending\_pct\_of\_gdp =} \FunctionTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{),}
+         \AttributeTok{murder\_per\_mil\_people =} \FunctionTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\SpecialCharTok{==} \StringTok{"Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
+         \AttributeTok{murder\_per\_mil\_people =} \FunctionTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\SpecialCharTok{==} \StringTok{"Chile"}\NormalTok{, }\FloatTok{4.4}\NormalTok{),}
+         \AttributeTok{murder\_per\_mil\_people =} \FunctionTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\SpecialCharTok{==} \StringTok{"Colombia"}\NormalTok{, }\FloatTok{25.34}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{relocate}\NormalTok{(polrights\_fh) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{polrights\_fh =}\NormalTok{ (}\DecValTok{8} \SpecialCharTok{{-}}\NormalTok{ polrights\_fh),}
+ \AttributeTok{military\_spending\_pct\_of\_gdp =}\NormalTok{ military\_spending\_pct\_of\_gdp }\SpecialCharTok{*} \DecValTok{100}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (}\DecValTok{100} \SpecialCharTok{{-}}\NormalTok{ corruption\_perception\_index\_cpi)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{ungroup}\NormalTok{()}
 \CommentTok{\# Best Subset Selection {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{vars \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country, }\OperatorTok{{-}}\NormalTok{year, }\OperatorTok{{-}}\KeywordTok{ends\_with}\NormalTok{(}\StringTok{"\_fh"}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}
-\StringTok{  }\KeywordTok{names}\NormalTok{()}
-\NormalTok{models \textless{}{-}}\StringTok{ }\KeywordTok{list}\NormalTok{()}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(vars)) \{}
-\NormalTok{  vc \textless{}{-}}\StringTok{ }\KeywordTok{combn}\NormalTok{(vars,i)}
-  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(vc)) \{}
-\NormalTok{    model \textless{}{-}}\StringTok{ }\KeywordTok{as.formula}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(}\StringTok{"polrights\_fh"}\NormalTok{, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\KeywordTok{paste0}\NormalTok{(vc[,j], }\DataTypeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
-\NormalTok{    models \textless{}{-}}\StringTok{ }\KeywordTok{c}\NormalTok{(models, model)}
+\NormalTok{vars }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{country, }\SpecialCharTok{{-}}\NormalTok{year, }\SpecialCharTok{{-}}\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_fh"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{names}\NormalTok{()}
+\NormalTok{models }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}
+\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(vars)) \{}
+\NormalTok{  vc }\OtherTok{\textless{}{-}} \FunctionTok{combn}\NormalTok{(vars,i)}
+  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{ncol}\NormalTok{(vc)) \{}
+\NormalTok{    model }\OtherTok{\textless{}{-}} \FunctionTok{as.formula}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(}\StringTok{"polrights\_fh"}\NormalTok{, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\FunctionTok{paste0}\NormalTok{(vc[,j], }\AttributeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
+\NormalTok{    models }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(models, model)}
 \NormalTok{    \}}
 \NormalTok{  \}}
-\NormalTok{subsets \textless{}{-}}\StringTok{ }\KeywordTok{map}\NormalTok{(models, }\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{lm}\NormalTok{(x, data)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{map}\NormalTok{(broom}\OperatorTok{::}\NormalTok{glance) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{setNames}\NormalTok{(models) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ id) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Model =} \KeywordTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
-         \DataTypeTok{Model =} \KeywordTok{str\_replace}\NormalTok{(Model, }\StringTok{"\textasciitilde{}"}\NormalTok{, }\StringTok{"="}\NormalTok{), }
-         \DataTypeTok{Model =} \KeywordTok{str\_to\_title}\NormalTok{(Model))}
-\NormalTok{model\_df6\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{6}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }
-\NormalTok{fit\_df6 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df6\_formula, data)}
-\NormalTok{model\_df5\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{5}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{()}
-\NormalTok{fit\_df5 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df5\_formula, data)}
-\NormalTok{model\_df4\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }
-\NormalTok{fit\_df4 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df4\_formula, data)}
-\NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
-\NormalTok{    x \textless{}{-}}\StringTok{ }\KeywordTok{enquo}\NormalTok{(x)}
-\NormalTok{    df }\OperatorTok{\%\textgreater{}\%}
-\StringTok{      }\KeywordTok{summarise}\NormalTok{(}
-                       \DataTypeTok{Mean  =} \KeywordTok{mean}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
-                     \DataTypeTok{Median  =} \KeywordTok{median}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
-                         \DataTypeTok{Std =} \KeywordTok{sd}\NormalTok{  ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
-                         \DataTypeTok{Min =} \KeywordTok{min}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
-                         \DataTypeTok{Max =} \KeywordTok{max}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
-                       \DataTypeTok{Range =} \KeywordTok{max}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) }\OperatorTok{{-}}\StringTok{ }\KeywordTok{min}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) ) }\OperatorTok{\%\textgreater{}\%}
-\StringTok{      }\KeywordTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
+\NormalTok{subsets }\OtherTok{\textless{}{-}} \FunctionTok{map}\NormalTok{(models, }\ControlFlowTok{function}\NormalTok{(x) }\FunctionTok{lm}\NormalTok{(x, data)) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{map}\NormalTok{(broom}\SpecialCharTok{::}\NormalTok{glance) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{setNames}\NormalTok{(models) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"id"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{rename}\NormalTok{(}\AttributeTok{model =}\NormalTok{ id) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Model =} \FunctionTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
+         \AttributeTok{Model =} \FunctionTok{str\_replace}\NormalTok{(Model, }\StringTok{"\textasciitilde{}"}\NormalTok{, }\StringTok{"="}\NormalTok{), }
+         \AttributeTok{Model =} \FunctionTok{str\_to\_title}\NormalTok{(Model))}
+\NormalTok{model\_df6\_formula }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(df }\SpecialCharTok{==} \DecValTok{6}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(adj.r.squared)) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(model) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{as.character}\NormalTok{() }
+\NormalTok{fit\_df6 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(model\_df6\_formula, data)}
+\NormalTok{model\_df5\_formula }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(df }\SpecialCharTok{==} \DecValTok{5}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(adj.r.squared)) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(model) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{as.character}\NormalTok{()}
+\NormalTok{fit\_df5 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(model\_df5\_formula, data)}
+\NormalTok{model\_df4\_formula }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(df }\SpecialCharTok{==} \DecValTok{4}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(adj.r.squared)) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(model) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{as.character}\NormalTok{() }
+\NormalTok{fit\_df4 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(model\_df4\_formula, data)}
+\NormalTok{stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, }\AttributeTok{df =}\NormalTok{ data, }\AttributeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
+\NormalTok{    x }\OtherTok{\textless{}{-}} \FunctionTok{enquo}\NormalTok{(x)}
+\NormalTok{    df }\SpecialCharTok{\%\textgreater{}\%}
+      \FunctionTok{summarise}\NormalTok{(}
+                       \AttributeTok{Mean  =} \FunctionTok{mean}\NormalTok{( }\SpecialCharTok{!!}\NormalTok{ x),}
+                     \AttributeTok{Median  =} \FunctionTok{median}\NormalTok{( }\SpecialCharTok{!!}\NormalTok{ x),}
+                         \AttributeTok{Std =} \FunctionTok{sd}\NormalTok{  ( }\SpecialCharTok{!!}\NormalTok{ x),}
+                         \AttributeTok{Min =} \FunctionTok{min}\NormalTok{ ( }\SpecialCharTok{!!}\NormalTok{ x),}
+                         \AttributeTok{Max =} \FunctionTok{max}\NormalTok{ ( }\SpecialCharTok{!!}\NormalTok{ x),}
+                       \AttributeTok{Range =} \FunctionTok{max}\NormalTok{(}\SpecialCharTok{!!}\NormalTok{ x) }\SpecialCharTok{{-}} \FunctionTok{min}\NormalTok{(}\SpecialCharTok{!!}\NormalTok{ x) ) }\SpecialCharTok{\%\textgreater{}\%}
+      \FunctionTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
 \NormalTok{\}}
-\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\KeywordTok{stat}\NormalTok{(x)\}) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Variable =} \KeywordTok{replace}\NormalTok{(Variable, }
-                            \DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\StringTok{"Political Rights"}\NormalTok{, }\StringTok{"Year"}\NormalTok{, }
+\NormalTok{data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{country) }\SpecialCharTok{\%\textgreater{}\%} 
+\FunctionTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{stat}\NormalTok{(x)\}) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Variable =} \FunctionTok{replace}\NormalTok{(Variable, }
+                            \AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{"Political Rights"}\NormalTok{, }\StringTok{"Year"}\NormalTok{, }
                                        \StringTok{"Corruption Perception"}\NormalTok{, }
@@
                                        \StringTok{"Military Spending"}\NormalTok{, }
-                                       \StringTok{"Murders rate"}\NormalTok{))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\KeywordTok{kable}\NormalTok{(}
-  \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{,}
-  \DataTypeTok{booktabs =} \OtherTok{TRUE}\NormalTok{,}
-  \DataTypeTok{escape =} \OtherTok{FALSE}\NormalTok{,}
-  \DataTypeTok{longtable =} \OtherTok{TRUE}\NormalTok{,}
- \DataTypeTok{caption =} \StringTok{"Descriptive Statistics"}\NormalTok{)}
-\NormalTok{r \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{group\_by}\NormalTok{(df) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{adj =} \KeywordTok{max}\NormalTok{(adj.r.squared, }\DataTypeTok{na.rm =}\NormalTok{ T))}
+                                       \StringTok{"Murders rate"}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%} 
+\FunctionTok{kable}\NormalTok{(}
+  \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
+  \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
+  \AttributeTok{escape =} \ConstantTok{FALSE}\NormalTok{,}
+  \AttributeTok{longtable =} \ConstantTok{TRUE}\NormalTok{,}
+ \AttributeTok{caption =} \StringTok{"Descriptive Statistics"}\NormalTok{)}
+\NormalTok{r }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{group\_by}\NormalTok{(df) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{adj =} \FunctionTok{max}\NormalTok{(adj.r.squared, }\AttributeTok{na.rm =}\NormalTok{ T))}
 
-\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df, }\DataTypeTok{y =}\NormalTok{ adj.r.squared)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ r, }\KeywordTok{aes}\NormalTok{(df, adj), }
-              \DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{span =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{""}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Adjusted R Squared"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{theme\_test}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }\OperatorTok{+}\StringTok{ }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Best Subset Selection"}\NormalTok{)}
+\NormalTok{subsets }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ df, }\AttributeTok{y =}\NormalTok{ adj.r.squared)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{data =}\NormalTok{ r, }\FunctionTok{aes}\NormalTok{(df, adj), }
+              \AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{span =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{""}\NormalTok{, }\AttributeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Adjusted R Squared"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{9}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{theme\_test}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Best Subset Selection"}\NormalTok{)}
 
-\NormalTok{r \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{group\_by}\NormalTok{(df) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{AIC =} \KeywordTok{max}\NormalTok{(AIC, }\DataTypeTok{na.rm =}\NormalTok{ T))}
+\NormalTok{r }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{group\_by}\NormalTok{(df) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{AIC =} \FunctionTok{max}\NormalTok{(AIC, }\AttributeTok{na.rm =}\NormalTok{ T))}
 
-\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df, }\DataTypeTok{y =}\NormalTok{ AIC)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ r, }\KeywordTok{aes}\NormalTok{(df, AIC), }
-              \DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{span =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{""}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"AIC"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{theme\_test}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }
+\NormalTok{subsets }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ df, }\AttributeTok{y =}\NormalTok{ AIC)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{data =}\NormalTok{ r, }\FunctionTok{aes}\NormalTok{(df, AIC), }
+              \AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{span =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{""}\NormalTok{, }\AttributeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\AttributeTok{y =} \StringTok{"AIC"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{9}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{theme\_test}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }
 
-\KeywordTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }
-                     \DataTypeTok{type =} \StringTok{"latex"}\NormalTok{, }
-                     \DataTypeTok{title =} \StringTok{"Regression Results"}\NormalTok{, }
-                     \DataTypeTok{covariate.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Corruption Perception"}\NormalTok{, }
+\FunctionTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }
+                     \AttributeTok{type =} \StringTok{"latex"}\NormalTok{, }
+                     \AttributeTok{title =} \StringTok{"Regression Results"}\NormalTok{, }
+                     \AttributeTok{covariate.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Corruption Perception"}\NormalTok{, }
                                           \StringTok{"Education Expendature"}\NormalTok{,}
@@
                                           \StringTok{"Intercept"}\NormalTok{),}
-                     \DataTypeTok{dep.var.caption =} \StringTok{"Political Rights Index"}\NormalTok{,}
-                     \DataTypeTok{dep.var.labels =} \OtherTok{NULL}\NormalTok{,}
-                     \DataTypeTok{dep.var.labels.include =} \OtherTok{FALSE}\NormalTok{, }
-                     \DataTypeTok{model.names =} \OtherTok{FALSE}\NormalTok{,}
-                     \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
-                     \DataTypeTok{df =} \OtherTok{FALSE}\NormalTok{, }
-                     \DataTypeTok{header =} \OtherTok{FALSE}\NormalTok{,}
-                     \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"DF = 6"}\NormalTok{, }\StringTok{"DF = 5"}\NormalTok{, }\StringTok{"DF = 4"}\NormalTok{),}
-                     \DataTypeTok{no.space =} \OtherTok{TRUE}\NormalTok{, }
-                     \DataTypeTok{notes.label =} \StringTok{"Note: Standard Errors are in Prentices"}\NormalTok{)}
-\NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{18}
-\NormalTok{a \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ corruption\_perception\_index\_cpi, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Corruption Perception"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Political Rights"}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size) }\OperatorTok{+}\StringTok{ }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"Response Term on Convariates"}\NormalTok{)}
+                     \AttributeTok{dep.var.caption =} \StringTok{"Political Rights Index"}\NormalTok{,}
+                     \AttributeTok{dep.var.labels =} \ConstantTok{NULL}\NormalTok{,}
+                     \AttributeTok{dep.var.labels.include =} \ConstantTok{FALSE}\NormalTok{, }
+                     \AttributeTok{model.names =} \ConstantTok{FALSE}\NormalTok{,}
+                     \AttributeTok{model.numbers =} \ConstantTok{FALSE}\NormalTok{,}
+                     \AttributeTok{df =} \ConstantTok{FALSE}\NormalTok{, }
+                     \AttributeTok{header =} \ConstantTok{FALSE}\NormalTok{,}
+                     \AttributeTok{column.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"DF = 6"}\NormalTok{, }\StringTok{"DF = 5"}\NormalTok{, }\StringTok{"DF = 4"}\NormalTok{),}
+                     \AttributeTok{no.space =} \ConstantTok{TRUE}\NormalTok{, }
+                     \AttributeTok{notes.label =} \StringTok{"Note: Standard Errors are in Prentices"}\NormalTok{)}
+\NormalTok{size }\OtherTok{\textless{}{-}} \DecValTok{18}
+\NormalTok{a }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ corruption\_perception\_index\_cpi, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Corruption Perception"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Political Rights"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Response Term on Convariates"}\NormalTok{)}
 
-\NormalTok{b \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ edu\_exp\_gdp\_per\_person, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{,}\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}
-\StringTok{    }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Education Expendature"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+\NormalTok{b }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ edu\_exp\_gdp\_per\_person, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{,}\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Education Expendature"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
 
-\NormalTok{c \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ life\_expectancy\_years, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{()}\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}
-\StringTok{    }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Life Expectacy"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+\NormalTok{c }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ life\_expectancy\_years, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{()}\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
+    \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Life Expectacy"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
 
-\NormalTok{d \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ military\_spending\_pct\_of\_gdp, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{()}\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Military Spending"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{)}\OperatorTok{+}\StringTok{ }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+\NormalTok{d }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ military\_spending\_pct\_of\_gdp, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{()}\SpecialCharTok{+} 
+  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Military Spending"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
 
-\NormalTok{e \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ murder\_per\_mil\_people, }\DataTypeTok{y =}\NormalTok{ polrights\_fh)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_point}\NormalTok{() }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{breaks =} \DecValTok{1}\OperatorTok{:}\DecValTok{7}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_smooth}\NormalTok{(}\DataTypeTok{method =} \StringTok{"lm"}\NormalTok{, }\DataTypeTok{se =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x =} \StringTok{"Murder Rate"}\NormalTok{, }\DataTypeTok{y =} \StringTok{""}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size)}
+\NormalTok{e }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ murder\_per\_mil\_people, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Murder Rate"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
 
-\NormalTok{(a }\OperatorTok{+}\StringTok{ }\NormalTok{b) }\OperatorTok{/}\StringTok{ }\NormalTok{(c }\OperatorTok{+}\StringTok{ }\NormalTok{d }\OperatorTok{+}\StringTok{ }\NormalTok{e) }
-\NormalTok{fit\_df5 }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\NormalTok{broom}\OperatorTok{::}\KeywordTok{augment}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(.resid)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{geom\_histogram}\NormalTok{(}\DataTypeTok{bins =} \DecValTok{75}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"black"}\NormalTok{) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Density"}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Residual"}\NormalTok{, }\DataTypeTok{title =} \StringTok{"Histogram of Residuals"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size }\OperatorTok{+}\StringTok{ }\DecValTok{10}\NormalTok{)}
+\NormalTok{(a }\SpecialCharTok{+}\NormalTok{ b) }\SpecialCharTok{/}\NormalTok{ (c }\SpecialCharTok{+}\NormalTok{ d }\SpecialCharTok{+}\NormalTok{ e) }
+\NormalTok{fit\_df5 }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  broom}\SpecialCharTok{::}\FunctionTok{augment}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(.resid)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{75}\NormalTok{, }\AttributeTok{fill =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{y =} \StringTok{"Density"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Residual"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Histogram of Residuals"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size }\SpecialCharTok{+} \DecValTok{10}\NormalTok{)}
 
-\NormalTok{fit\_df5 }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\NormalTok{broom}\OperatorTok{::}\KeywordTok{augment}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{sample =}\NormalTok{ .resid)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{stat\_qq}\NormalTok{() }\OperatorTok{+}
-\StringTok{  }\KeywordTok{stat\_qq\_line}\NormalTok{(}\DataTypeTok{color =} \StringTok{"\#3C989E"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\KeywordTok{scale\_x\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
-\KeywordTok{scale\_y\_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \StringTok{"QQ Plot of Residuals "}\NormalTok{, }\DataTypeTok{x =} \StringTok{"Residual"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Expected"}\NormalTok{) }\OperatorTok{+}\StringTok{ }
-\StringTok{  }\KeywordTok{theme\_light}\NormalTok{(}\DataTypeTok{base\_size =}\NormalTok{ size }\OperatorTok{+}\StringTok{ }\DecValTok{10}\NormalTok{)}
-\NormalTok{beepr}\OperatorTok{::}\KeywordTok{beep}\NormalTok{()}
+\NormalTok{fit\_df5 }\SpecialCharTok{\%\textgreater{}\%} 
+\NormalTok{  broom}\SpecialCharTok{::}\FunctionTok{augment}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{sample =}\NormalTok{ .resid)) }\SpecialCharTok{+} 
+  \FunctionTok{stat\_qq}\NormalTok{() }\SpecialCharTok{+}
+  \FunctionTok{stat\_qq\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{, }\AttributeTok{size =} \DecValTok{2}\NormalTok{) }\SpecialCharTok{+} 
+\FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+} 
+\FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+} 
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"QQ Plot of Residuals "}\NormalTok{, }\AttributeTok{x =} \StringTok{"Residual"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Expected"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size }\SpecialCharTok{+} \DecValTok{10}\NormalTok{)}
+\NormalTok{beepr}\SpecialCharTok{::}\FunctionTok{beep}\NormalTok{()}
 \end{Highlighting}

### 2020-12-08 paper/paper.Rmd
url blue
getting close

@@
 output            : papaja::apa6_pdf
+urlcolor: blue
 ---
@@
 
-2020 is an election year, which has many of us reflecting on political freedom.
+2020 is an election year, which has us reflecting on political freedom.
 Political freedoms are important because they have a dramatic impact on the quality of life for the citizens of a country.
@@
 
-The **Political Rights Index** is comprised of three subcategories.
-Electoral process, political participation, and functioning government.
+The **Political Rights Index** is composed of three subcategories: electoral process, political participation, and functioning government.
 Electoral process is a score based on how the current government leaders were selected, mainly how fairly the positions were obtained and kept.
-As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
-Political Participation is evaluated on four criterion, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
-Functioning government, measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
+As well as the fairness of the current electoral laws, how they are implemented, and the degree to which there is an independent judiciary.
+Political Participation is evaluated on four criterion, the right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Functioning government measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
 Freedom house has measured political freedom in this manner for every country from the years 1978 to present.
+As we will explain later we are only able to use data from 2000 to 2018.
 
@@
 One should take these results knowing full well that a core assumption is violated.
-Despite this, we still know that these results can be helpful in policy recommendations and to confirm suspicion that associations may in fact exist.
-While the exact value of our regression coefficients are not to be interpreted as slope but a measure of the direction of the association.
+Despite this, we are reasonably sure that these results can be helpful to confirm suspicion that associations may exist and make policy recommendations.
+While the exact value of our regression coefficients are not to be interpreted as slope rather an indicator pointing out direction of the association.
 This will serve as a reasonable measure of political freedom around the world.
-However, measuring political freedom cannot be done in the same way as measuring weight, speed, or temperature.
-There are inherent biases in the people measuring this.
-Most obvious, data are collected and funded by people in the United States and comes a heavy cultural bias so associations should be taken to mean a western notion of the concept of freedom.
-We obtained the dataset from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
+Additionally, measuring political freedom is done in the same way as measuring physical properties such as weight, velocity, or temperature.
+Often metrics such as political freedom are made based on scholarly judgment subject to the biases of the people measuring this.
+Most obvious, these data are collected, assigned, and funded by people in the United States.
+Naturally, this comes an incalculable cultural bias so we caution our reader to interpret increases or decreases in political freedom to a western notion of what constitutes political freedom.
+
+We began this study by obtaining data from the Gapminder Foundation [@Gapminder], a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
@@
 
-These data sets were separate so we downloaded them individually, cleaned and combined them together using R [@R-base] and the Tidyverse Package [@R-tidyverse].
+These data came in separate sets so we downloaded them individually, cleaned and combined them together using R [@R-base] and the Tidyverse Package [@R-tidyverse].
 We included all the code in the appendix.
@@
 Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
-
+Removing all countries outside of the OECD puts an additional constraint on interpretation.
+Findings here should also take care to not be interpreted as universally applicable because we are only studying the OECD by necessity.
 This remedied most of the missing datapoints.
@@
 This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
-After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0% of their GDP, so we replaced the NA with a 0.
+After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0% of their GDP.
+This was recorded as NA so we replaced the NA with a 0.
 This is how we obtained a complete and full data set with no missing data points.
@@
 We want to interpret a higher number to having more political rights.
-\newpage
 
@@
 We precede on the understanding that there are moderate problems with the data, first having a discrete response variable and the nature of the distribution being skewed towards the maximum 7/7 political freedom.
+With these assumption violations in mind, we were not compelled to make any variable transformations and proceed to selecting a model.
 
@@
   theme_test(base_size = size) 
-
 ```
 
-We examined the results and due to the categorical nature we are not aware of any function that would map discrete values onto the real line.
-Therefore, we did not find compelling evidence to support making such a transformation and the data are roughly linear.
-We will not be making any non-linear transformation of variables.
-With a flawed dataset that reasonably holds all other assumptions we performed the best subset algorithm to obtain a model with the best fit.
-From the graph of the subsets we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
 ## Model Selection
+
+To select a model we performed the best subset algorithm to select several models with the best fit.
+Graphing the performance of each subset, we can see that the increase in $R^{2}_a$ and $AIC$ by adding additional parameters diminishes quite rapidly.
+It was appropriate to narrow our model choices down to three.
+First, the model with six degrees of freedom, one with five, and one with four.
+The results from these three models is in Table 2 made using the Stargazer package [@R-stargazer].
+The model with six degrees of freedom contains **Internet Users** with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+A coefficient that small has us suspecting that the relation that does not seem practically significant.
+Also, given the violation of assumptions it seems reasonable to exclude it from the model.
+Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99% level and seem large enough to be indicative of a linear association.
+The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
+This is how we arrived at the model with five degrees of freedom.
 
@@
 ```
-
-From the best subsets, it was appropriate to narrow our model choices down to three.
-First, the model with six degrees of freedom, next one with five, and one with four.
-The results from these three models is in Table 2 made using Stargazer [@R-stargazer].
-The model with six degrees of freedom contains **Internet Users** with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
-Also, given the violation of assumptions it seems reasonable to exude it from the model.
-Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99% level.
-The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
-Counterintuitively, politically freedom seems to decrease as life expectancy increases.
-We are not qualified to explain that we can only speculate.
-This is how we arrived at the model with five degrees of freedom.
 
@@
 There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficients.
-Life expectancy on it's own has a positive association with political freedom, however, when holding the other covariates constant we find that slope to be negative.
+Life expectancy on it's own has a positive association with political freedom, however, when holding the other covariates constant we find that association to be negative.
+
 Now we will examine some regression diagnostics to analyze the performance and identify problems.
@@
 This is confirmed by Freedomhouse [@Freedomhouse] reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After some discussion, we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
+After some discussion, we concluded that since the regression results were not severely affected and this is not an entry error removing these data points is inappropriate.
 
 It was clear from the plots that error variance may not be constant.
-A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
-We calculated a $t^{*}_{BF} = 9.49$ which informs us that the error variance is substantially higher when the values of political freedom are lower.
+A Brown-Forsythe test confirmed our suspicions informing us that the error variance is not consistent.
+We calculated a $t^{*}_{BF} = 9.49$ indicating the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
 The results are statistically significant but can only be interpreted for countries in the OECD.
-The model does a reasonably good job predicting political freedom in the 6 and 7 range.
+The model performs reasonably well explaining the political freedom of countries in the 6 and 7 range.
 However, the model completely falls apart at the one case of a substantial loss in freedom.
@@
 beepr::beep()
+Sys.sleep(1)
 ```

### 2020-12-08 paper/paper.tex
.
getting close

@@
 \PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
 %
@@
   pdfkeywords={keyword},
-  hidelinks,
+  colorlinks=true,
+  linkcolor=Maroon,
+  filecolor=Maroon,
+  citecolor=Blue,
+  urlcolor=blue,
   pdfcreator={LaTeX via pandoc}}
@@
 
-The \textbf{Political Rights Index} is comprised of three subcategories.
-Electoral process, political participation, and functioning government.
+The \textbf{Political Rights Index} is composed of three subcategories: electoral process, political participation, and functioning government.
 Electoral process is a score based on how the current government leaders were selected, mainly how fairly the positions were obtained and kept.
-As well as the fairness of the current electoral laws, how they are implemented and the degree to which there is an independent judiciary.
-Political Participation is evaluated on four criterion, right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
-Functioning government, measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
+As well as the fairness of the current electoral laws, how they are implemented, and the degree to which there is an independent judiciary.
+Political Participation is evaluated on four criterion, the right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Functioning government measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
 Freedom house has measured political freedom in this manner for every country from the years 1978 to present.
+As we will explain later we are only able to use data from 2000 to 2018.
 
@@
 One should take these results knowing full well that a core assumption is violated.
-Despite this, we still know that these results can be helpful in policy recommendations and to confirm suspicion that associations may in fact exist.
-While the exact value of our regression coefficients are not to be interpreted as slope but a measure of the direction of the association.
+Despite this, we are reasonably sure that these results can be helpful to confirm suspicion that associations may exist and make policy recommendations.
+While the exact value of our regression coefficients are not to be interpreted as slope rather an indicator pointing out direction of the association.
 This will serve as a reasonable measure of political freedom around the world.
-However, measuring political freedom cannot be done in the same way as measuring weight, speed, or temperature.
-There are inherent biases in the people measuring this.
-Most obvious, data are collected and funded by people in the United States and comes a heavy cultural bias so associations should be taken to mean a western notion of the concept of freedom.
-We obtained the dataset from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
+Additionally, measuring political freedom is done in the same way as measuring physical properties such as weight, velocity, or temperature.
+Often metrics such as political freedom are made based on scholarly judgment subject to the biases of the people measuring this.
+Most obvious, these data are collected, assigned, and funded by people in the United States.
+Naturally, this comes an incalculable cultural bias so we caution our reader to interpret increases or decreases in political freedom to a western notion of what constitutes political freedom.
+
+We began this study by obtaining data from the Gapminder Foundation (Rosling, 2020), a non-profit organization that studies and promotes economic development.
 After carefully selecting a dependent variable, we browsed data that were also available from Gapminder and selected variables that we felt would be helpful in explaining political freedom in various countries.
@@
 
-These data sets were separate so we downloaded them individually, cleaned and combined them together using R (R Core Team, 2020) and the Tidyverse Package (Wickham et al., 2019).
+These data came in separate sets so we downloaded them individually, cleaned and combined them together using R (R Core Team, 2020) and the Tidyverse Package (Wickham et al., 2019).
 We included all the code in the appendix.
@@
 Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
-
+Removing all countries outside of the OECD puts an additional constraint on interpretation.
+Findings here should also take care to not be interpreted as universally applicable because we are only studying the OECD by necessity.\\
 This remedied most of the missing datapoints.
@@
 This is a reasonable procedure because the covariates do not fluctuate wildly year over year.
-After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0\% of their GDP, so we replaced the NA with a 0.
+After that, there were a few other cases which we needed to input manually, for example, Iceland's Military spending is 0\% of their GDP.
+This was recorded as NA so we replaced the NA with a 0.
 This is how we obtained a complete and full data set with no missing data points.
@@
 
-We examined the results and due to the categorical nature we are not aware of any function that would map discrete values onto the real line.
-Therefore, we did not find compelling evidence to support making such a transformation and the data are roughly linear.
-We will not be making any non-linear transformation of variables.
-With a flawed dataset that reasonably holds all other assumptions we performed the best subset algorithm to obtain a model with the best fit.
-From the graph of the subsets we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.\\
-\#\# Model Selection
+\hypertarget{model-selection}{%
+\subsection{Model Selection}\label{model-selection}}
+
+To select a model we performed the best subset algorithm to select several models with the best fit.
+Graphing the performance of each subset, we can see that the increase in \(R^{2}_a\) and \(AIC\) by adding additional parameters diminishes quite rapidly.
+It was appropriate to narrow our model choices down to three.
+First, the model with six degrees of freedom, one with five, and one with four.
+The results from these three models is in Table 2 made using the Stargazer package (Hlavac, 2018).
+The model with six degrees of freedom contains \textbf{Internet Users} with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
+A coefficient that small has us suspecting that the relation that does not seem practically significant.
+Also, given the violation of assumptions it seems reasonable to exclude it from the model.
+Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99\% level and seem large enough to be indicative of a linear association.
+The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
+This is how we arrived at the model with five degrees of freedom.
 
@@
 
-From the best subsets, it was appropriate to narrow our model choices down to three.
-First, the model with six degrees of freedom, next one with five, and one with four.
-The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018).
-The model with six degrees of freedom contains \textbf{Internet Users} with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
-Also, given the violation of assumptions it seems reasonable to exude it from the model.
-Looking at the model with five degrees of freedom, all of our coefficients are significant at the 99\% level.
-The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant.
-Counterintuitively, politically freedom seems to decrease as life expectancy increases.
-We are not qualified to explain that we can only speculate.
-This is how we arrived at the model with five degrees of freedom.
-
 \includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
@@
 There is a fairly linear relationship with a clear sloping line which, except for life expectancy, concur with the regression coefficients.
-Life expectancy on it's own has a positive association with political freedom, however, when holding the other covariates constant we find that slope to be negative.\\
+Life expectancy on it's own has a positive association with political freedom, however, when holding the other covariates constant we find that association to be negative.
+
 Now we will examine some regression diagnostics to analyze the performance and identify problems.
@@
 This is confirmed by Freedomhouse (\emph{Countries and territories}, 2020) reporting that a coup attempt in Turkey resulted in a political retaliation against perceived opponents and constitutional changes were made that concentrated political power to the president.
-After some discussion, we concluded that since the regression results were not severely affected and this is not an entry error there is not a compelling reason to eliminate it.
+After some discussion, we concluded that since the regression results were not severely affected and this is not an entry error removing these data points is inappropriate.
 
 It was clear from the plots that error variance may not be constant.
-A Brown-Forsythe test confirmed our suspicions telling us that the error variance is not consistent.
-We calculated a \(t^{*}_{BF} = 9.49\) which informs us that the error variance is substantially higher when the values of political freedom are lower.
+A Brown-Forsythe test confirmed our suspicions informing us that the error variance is not consistent.
+We calculated a \(t^{*}_{BF} = 9.49\) indicating the error variance is substantially higher when the values of political freedom are lower.
 This is likely due to the fact that our sample includes predominately values that are on the upper end of the political freedom.
@@
   \FunctionTok{theme\_test}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }
-
 \FunctionTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }
@@
 \NormalTok{beepr}\SpecialCharTok{::}\FunctionTok{beep}\NormalTok{()}
+\FunctionTok{Sys.sleep}\NormalTok{(}\DecValTok{1}\NormalTok{)}
 \end{Highlighting}

### 2020-12-09 paper/paper.Rmd
final

@@
 footnotelist      : no
-linenumbers       : yes 
+linenumbers       : no
 mask              : no
@@
 As well as the fairness of the current electoral laws, how they are implemented, and the degree to which there is an independent judiciary.
-Political Participation is evaluated on four criterion, the right to form parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
+Political Participation is evaluated on four criterion, the right to form political parties, realistic opposition to current power, political choice free from military, religious powers, economic oligarchies, or any other unaccountable body, and various minority groups having full political rights.
 Functioning government measures the level of autonomy of the current heads of government when determining policies, safeguards against corruption, and transparency of government operations.
@@
 This will serve as a reasonable measure of political freedom around the world.
-Additionally, measuring political freedom is done in the same way as measuring physical properties such as weight, velocity, or temperature.
+Additionally, measuring political freedom is not done in the same way as measuring physical properties such as weight, velocity, or temperature.
 Often metrics such as political freedom are made based on scholarly judgment subject to the biases of the people measuring this.
@@
 These data came in separate sets so we downloaded them individually, cleaned and combined them together using R [@R-base] and the Tidyverse Package [@R-tidyverse].
-We included all the code in the appendix.
 This resulted in a data set with all 196 countries from years 1950 to 2030 (data after 2019 were projections).
@@
 This subset of countries has much more complete data.
-Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018.
+Therefore, we removed data from countries that are not members of the OECD and selected only the years 2000 through 2018 as data is more complete within this time frame.
 Removing all countries outside of the OECD puts an additional constraint on interpretation.
@@
   longtable = TRUE,
- caption = "Descriptive Statistics")
+ caption = "")
 ```
@@
 The model with six degrees of freedom contains **Internet Users** with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
-A coefficient that small has us suspecting that the relation that does not seem practically significant.
+A coefficient that small has us suspecting that relation is not practically significant.
 Also, given the violation of assumptions it seems reasonable to exclude it from the model.
@@
   stat_qq() +
-  stat_qq_line(color = "#3C989E", size = 2) + 
+  stat_qq_line(color = "#3C989E", size = 1) + 
 scale_x_continuous(limits = c(-4,4)) + 
@@
 
-\newpage
-# Appendix: All code for this report
-
-```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
-```
-
 ```{r include=FALSE}

### 2020-12-09 paper/paper.tex
final

@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 \keywords{keyword\newline\indent Word count: X}
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 These data came in separate sets so we downloaded them individually, cleaned and combined them together using R (R Core Team, 2020) and the Tidyverse Package (Wickham et al., 2019).
-We included all the code in the appendix.
 This resulted in a data set with all 196 countries from years 1950 to 2030 (data after 2019 were projections).
@@
 \begin{longtable}[t]{lrrrrrr}
-\caption{\label{tab:unnamed-chunk-2}Descriptive Statistics}\\
+\caption{\label{tab:unnamed-chunk-2}}\\
 \toprule
@@
 The model with six degrees of freedom contains \textbf{Internet Users} with coefficient 0.003, which is statistically significant, however, a one percent increase in the percentage of people using the internet is associated with a 0.003 increase in political freedom is not politically significant.
-A coefficient that small has us suspecting that the relation that does not seem practically significant.
+A coefficient that small has us suspecting that relation is not practically significant.
 Also, given the violation of assumptions it seems reasonable to exclude it from the model.
@@
 
-\newpage
-
-\hypertarget{appendix-all-code-for-this-report}{%
-\section{Appendix: All code for this report}\label{appendix-all-code-for-this-report}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(tidyverse)}
-\FunctionTok{library}\NormalTok{(kableExtra)}
-\FunctionTok{library}\NormalTok{(stargazer)}
-\FunctionTok{library}\NormalTok{(patchwork)}
-\FunctionTok{library}\NormalTok{(}\StringTok{"papaja"}\NormalTok{)}
-\NormalTok{size }\OtherTok{\textless{}{-}} \DecValTok{30}
-\FunctionTok{r\_refs}\NormalTok{(}\StringTok{"r{-}references.bib"}\NormalTok{)}
-\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{echo =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{warning=}\ConstantTok{FALSE}\NormalTok{, }\AttributeTok{message =} \ConstantTok{FALSE}\NormalTok{, }
-                      \AttributeTok{fig.width =} \DecValTok{12}\NormalTok{, }\AttributeTok{fig.height =} \DecValTok{8}\NormalTok{) }
-\CommentTok{\# Read and Clean {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{files }\OtherTok{\textless{}{-}} \FunctionTok{list.files}\NormalTok{(}\AttributeTok{path =}\NormalTok{ here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"raw\_data"}\NormalTok{), }\AttributeTok{pattern =} \StringTok{".csv"}\NormalTok{)}
-\NormalTok{cleaning }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(df)\{}
-\NormalTok{  df }\OtherTok{\textless{}{-}} \FunctionTok{pivot\_longer}\NormalTok{(df, }\AttributeTok{cols =} \SpecialCharTok{{-}}\NormalTok{country, }\AttributeTok{names\_to =} \StringTok{"year"}\NormalTok{)}
-\NormalTok{\}}
-\NormalTok{data }\OtherTok{\textless{}{-}}\NormalTok{ files }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) }\FunctionTok{read\_csv}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(}\StringTok{"raw\_data/"}\NormalTok{, x))) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{setNames}\NormalTok{(}\FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.csv$"}\NormalTok{, }\StringTok{""}\NormalTok{, files)) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{map}\NormalTok{(cleaning) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"id"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ id)}
-\CommentTok{\# Filtering {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{countries }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"countries.RDS"}\NormalTok{))}
-\NormalTok{data }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{year =} \FunctionTok{as.numeric}\NormalTok{(year)) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{filter}\NormalTok{(year }\SpecialCharTok{\textgreater{}=} \DecValTok{2000}\NormalTok{, year }\SpecialCharTok{\textless{}} \DecValTok{2019}\NormalTok{, country }\SpecialCharTok{\%in\%}\NormalTok{ countries) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(country) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{country),}\FunctionTok{list}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\FunctionTok{ifelse}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(.), }\FunctionTok{median}\NormalTok{(., }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{), .))) }\SpecialCharTok{\%\textgreater{}\%}
-\CommentTok{\# Iceland spent 0 so I needed to manually recode that}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{military\_spending\_pct\_of\_gdp =} \FunctionTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{),}
-         \AttributeTok{murder\_per\_mil\_people =} \FunctionTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\SpecialCharTok{==} \StringTok{"Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
-         \AttributeTok{murder\_per\_mil\_people =} \FunctionTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\SpecialCharTok{==} \StringTok{"Chile"}\NormalTok{, }\FloatTok{4.4}\NormalTok{),}
-         \AttributeTok{murder\_per\_mil\_people =} \FunctionTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\SpecialCharTok{==} \StringTok{"Colombia"}\NormalTok{, }\FloatTok{25.34}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{relocate}\NormalTok{(polrights\_fh) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{polrights\_fh =}\NormalTok{ (}\DecValTok{8} \SpecialCharTok{{-}}\NormalTok{ polrights\_fh),}
- \AttributeTok{military\_spending\_pct\_of\_gdp =}\NormalTok{ military\_spending\_pct\_of\_gdp }\SpecialCharTok{*} \DecValTok{100}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (}\DecValTok{100} \SpecialCharTok{{-}}\NormalTok{ corruption\_perception\_index\_cpi)) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{ungroup}\NormalTok{()}
-\CommentTok{\# Best Subset Selection {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{vars }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{country, }\SpecialCharTok{{-}}\NormalTok{year, }\SpecialCharTok{{-}}\FunctionTok{ends\_with}\NormalTok{(}\StringTok{"\_fh"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{names}\NormalTok{()}
-\NormalTok{models }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(vars)) \{}
-\NormalTok{  vc }\OtherTok{\textless{}{-}} \FunctionTok{combn}\NormalTok{(vars,i)}
-  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{ncol}\NormalTok{(vc)) \{}
-\NormalTok{    model }\OtherTok{\textless{}{-}} \FunctionTok{as.formula}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(}\StringTok{"polrights\_fh"}\NormalTok{, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\FunctionTok{paste0}\NormalTok{(vc[,j], }\AttributeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
-\NormalTok{    models }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(models, model)}
-\NormalTok{    \}}
-\NormalTok{  \}}
-\NormalTok{subsets }\OtherTok{\textless{}{-}} \FunctionTok{map}\NormalTok{(models, }\ControlFlowTok{function}\NormalTok{(x) }\FunctionTok{lm}\NormalTok{(x, data)) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{map}\NormalTok{(broom}\SpecialCharTok{::}\NormalTok{glance) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{setNames}\NormalTok{(models) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"id"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{rename}\NormalTok{(}\AttributeTok{model =}\NormalTok{ id) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Model =} \FunctionTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
-         \AttributeTok{Model =} \FunctionTok{str\_replace}\NormalTok{(Model, }\StringTok{"\textasciitilde{}"}\NormalTok{, }\StringTok{"="}\NormalTok{), }
-         \AttributeTok{Model =} \FunctionTok{str\_to\_title}\NormalTok{(Model))}
-\NormalTok{model\_df6\_formula }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(df }\SpecialCharTok{==} \DecValTok{6}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(adj.r.squared)) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(model) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{as.character}\NormalTok{() }
-\NormalTok{fit\_df6 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(model\_df6\_formula, data)}
-\NormalTok{model\_df5\_formula }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(df }\SpecialCharTok{==} \DecValTok{5}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(adj.r.squared)) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(model) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{as.character}\NormalTok{()}
-\NormalTok{fit\_df5 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(model\_df5\_formula, data)}
-\NormalTok{model\_df4\_formula }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(df }\SpecialCharTok{==} \DecValTok{4}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(adj.r.squared)) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(model) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{as.character}\NormalTok{() }
-\NormalTok{fit\_df4 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(model\_df4\_formula, data)}
-\NormalTok{stat }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, }\AttributeTok{df =}\NormalTok{ data, }\AttributeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}
-\NormalTok{    x }\OtherTok{\textless{}{-}} \FunctionTok{enquo}\NormalTok{(x)}
-\NormalTok{    df }\SpecialCharTok{\%\textgreater{}\%}
-      \FunctionTok{summarise}\NormalTok{(}
-                       \AttributeTok{Mean  =} \FunctionTok{mean}\NormalTok{( }\SpecialCharTok{!!}\NormalTok{ x),}
-                     \AttributeTok{Median  =} \FunctionTok{median}\NormalTok{( }\SpecialCharTok{!!}\NormalTok{ x),}
-                         \AttributeTok{Std =} \FunctionTok{sd}\NormalTok{  ( }\SpecialCharTok{!!}\NormalTok{ x),}
-                         \AttributeTok{Min =} \FunctionTok{min}\NormalTok{ ( }\SpecialCharTok{!!}\NormalTok{ x),}
-                         \AttributeTok{Max =} \FunctionTok{max}\NormalTok{ ( }\SpecialCharTok{!!}\NormalTok{ x),}
-                       \AttributeTok{Range =} \FunctionTok{max}\NormalTok{(}\SpecialCharTok{!!}\NormalTok{ x) }\SpecialCharTok{{-}} \FunctionTok{min}\NormalTok{(}\SpecialCharTok{!!}\NormalTok{ x) ) }\SpecialCharTok{\%\textgreater{}\%}
-      \FunctionTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
-\NormalTok{\}}
-\NormalTok{data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{country) }\SpecialCharTok{\%\textgreater{}\%} 
-\FunctionTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{stat}\NormalTok{(x)\}) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{bind\_rows}\NormalTok{(}\AttributeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Variable =} \FunctionTok{replace}\NormalTok{(Variable, }
-                            \AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{"Political Rights"}\NormalTok{, }\StringTok{"Year"}\NormalTok{, }
-                                       \StringTok{"Corruption Perception"}\NormalTok{, }
-                                       \StringTok{"Education Expenditure"}\NormalTok{, }
-                                       \StringTok{"Electricity Use"}\NormalTok{, }
-                                       \StringTok{"Gini"}\NormalTok{, }
-                                       \StringTok{"Internet Users"}\NormalTok{,}
-                                       \StringTok{"Life Expectancy"}\NormalTok{, }
-                                       \StringTok{"Labor Force Participation"}\NormalTok{, }
-                                       \StringTok{"Military Spending"}\NormalTok{, }
-                                       \StringTok{"Murders rate"}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%} 
-\FunctionTok{kable}\NormalTok{(}
-  \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
-  \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
-  \AttributeTok{escape =} \ConstantTok{FALSE}\NormalTok{,}
-  \AttributeTok{longtable =} \ConstantTok{TRUE}\NormalTok{,}
- \AttributeTok{caption =} \StringTok{"Descriptive Statistics"}\NormalTok{)}
-\NormalTok{r }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{group\_by}\NormalTok{(df) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{adj =} \FunctionTok{max}\NormalTok{(adj.r.squared, }\AttributeTok{na.rm =}\NormalTok{ T))}
-
-\NormalTok{subsets }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ df, }\AttributeTok{y =}\NormalTok{ adj.r.squared)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{data =}\NormalTok{ r, }\FunctionTok{aes}\NormalTok{(df, adj), }
-              \AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{span =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{""}\NormalTok{, }\AttributeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Adjusted R Squared"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{9}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{theme\_test}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Best Subset Selection"}\NormalTok{)}
-
-\NormalTok{r }\OtherTok{\textless{}{-}}\NormalTok{ subsets }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{group\_by}\NormalTok{(df) }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{AIC =} \FunctionTok{max}\NormalTok{(AIC, }\AttributeTok{na.rm =}\NormalTok{ T))}
-
-\NormalTok{subsets }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ df, }\AttributeTok{y =}\NormalTok{ AIC)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{data =}\NormalTok{ r, }\FunctionTok{aes}\NormalTok{(df, AIC), }
-              \AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{span =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{""}\NormalTok{, }\AttributeTok{x =} \StringTok{"Parameters"}\NormalTok{, }\AttributeTok{y =} \StringTok{"AIC"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{9}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{theme\_test}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }
-\FunctionTok{stargazer}\NormalTok{(fit\_df6, fit\_df5, fit\_df4, }
-                     \AttributeTok{type =} \StringTok{"latex"}\NormalTok{, }
-                     \AttributeTok{title =} \StringTok{"Regression Results"}\NormalTok{, }
-                     \AttributeTok{covariate.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Corruption Perception"}\NormalTok{, }
-                                          \StringTok{"Education Expendature"}\NormalTok{,}
-                                          \StringTok{"Internet Users"}\NormalTok{, }
-                                          \StringTok{"Life Expectancy"}\NormalTok{,}
-                                          \StringTok{"Military Spending"}\NormalTok{, }
-                                          \StringTok{"Murder Rate"}\NormalTok{, }
-                                          \StringTok{"Intercept"}\NormalTok{),}
-                     \AttributeTok{dep.var.caption =} \StringTok{"Political Rights Index"}\NormalTok{,}
-                     \AttributeTok{dep.var.labels =} \ConstantTok{NULL}\NormalTok{,}
-                     \AttributeTok{dep.var.labels.include =} \ConstantTok{FALSE}\NormalTok{, }
-                     \AttributeTok{model.names =} \ConstantTok{FALSE}\NormalTok{,}
-                     \AttributeTok{model.numbers =} \ConstantTok{FALSE}\NormalTok{,}
-                     \AttributeTok{df =} \ConstantTok{FALSE}\NormalTok{, }
-                     \AttributeTok{header =} \ConstantTok{FALSE}\NormalTok{,}
-                     \AttributeTok{column.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"DF = 6"}\NormalTok{, }\StringTok{"DF = 5"}\NormalTok{, }\StringTok{"DF = 4"}\NormalTok{),}
-                     \AttributeTok{no.space =} \ConstantTok{TRUE}\NormalTok{, }
-                     \AttributeTok{notes.label =} \StringTok{"Note: Standard Errors are in Prentices"}\NormalTok{)}
-\NormalTok{size }\OtherTok{\textless{}{-}} \DecValTok{18}
-\NormalTok{a }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ corruption\_perception\_index\_cpi, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Corruption Perception"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Political Rights"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Response Term on Convariates"}\NormalTok{)}
-
-\NormalTok{b }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ edu\_exp\_gdp\_per\_person, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{,}\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Education Expendature"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
-
-\NormalTok{c }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ life\_expectancy\_years, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{()}\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
-    \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Life Expectacy"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
-
-\NormalTok{d }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ military\_spending\_pct\_of\_gdp, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{()}\SpecialCharTok{+} 
-  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Military Spending"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{)}\SpecialCharTok{+} \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
-
-\NormalTok{e }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ murder\_per\_mil\_people, }\AttributeTok{y =}\NormalTok{ polrights\_fh)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Murder Rate"}\NormalTok{, }\AttributeTok{y =} \StringTok{""}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size)}
-
-\NormalTok{(a }\SpecialCharTok{+}\NormalTok{ b) }\SpecialCharTok{/}\NormalTok{ (c }\SpecialCharTok{+}\NormalTok{ d }\SpecialCharTok{+}\NormalTok{ e) }
-\NormalTok{fit\_df5 }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  broom}\SpecialCharTok{::}\FunctionTok{augment}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(.resid)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{75}\NormalTok{, }\AttributeTok{fill =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{y =} \StringTok{"Density"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Residual"}\NormalTok{, }\AttributeTok{title =} \StringTok{"Histogram of Residuals"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size }\SpecialCharTok{+} \DecValTok{10}\NormalTok{)}
-
-\NormalTok{fit\_df5 }\SpecialCharTok{\%\textgreater{}\%} 
-\NormalTok{  broom}\SpecialCharTok{::}\FunctionTok{augment}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{sample =}\NormalTok{ .resid)) }\SpecialCharTok{+} 
-  \FunctionTok{stat\_qq}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{stat\_qq\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"\#3C989E"}\NormalTok{, }\AttributeTok{size =} \DecValTok{2}\NormalTok{) }\SpecialCharTok{+} 
-\FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+} 
-\FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{)) }\SpecialCharTok{+} 
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"QQ Plot of Residuals "}\NormalTok{, }\AttributeTok{x =} \StringTok{"Residual"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Expected"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_light}\NormalTok{(}\AttributeTok{base\_size =}\NormalTok{ size }\SpecialCharTok{+} \DecValTok{10}\NormalTok{)}
-\NormalTok{beepr}\SpecialCharTok{::}\FunctionTok{beep}\NormalTok{()}
-\FunctionTok{Sys.sleep}\NormalTok{(}\DecValTok{1}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
 \end{document}
